### 2024-02-03 index.qmd
mastofeed

---
title: "Tom Stafford, Professor of Cognitive Science"
format: html
editor: visual
---

I study learning and decision making. Much of my research looks at risk and bias, and their management, in decision making. I am also interested in skill learning, using measures of behaviour informed by work done in computational theory and neuroscience. More recently a strand of my research looks at complex decisions, and the psychology of reason, argument and persuasion.

## Updates on <mastodon.online/@tomstafford>

<iframe allowfullscreen sandbox="allow-top-navigation allow-scripts allow-popups allow-popups-to-escape-sandbox" width="500" height="800" src="https://mastofeed.com/apiv2/feed?userurl=https%3A%2F%2Fmastodon.online%2Fusers%2Ftomstafford&theme=light&size=100&header=true&replies=false&boosts=false"></iframe>

Colophon

Website made with [Quarto](https://quarto.org), hosted on github pages. Styles taken from <https://ddimmery.com/posts/quarto-website/>

### 2024-02-04 about.qmd

---
title: "About"
---

I am Professor of Cognitive Science in the [Department of Psychology, University of Sheffield](https://www.sheffield.ac.uk/psychology) and Senior Research Fellow at the [Research on Research Institute](https://researchonresearch.org/).

### Research Interests

- Decision Making, Bias
- Reasoning
- Metaresearch
- Data Science
- Experimental Design

### Education

::: {.d-flex .justify-content-between}
::: {}
**New York University**  
PhD in clevrness
Not really
:::
::: {.text-end}
New York, NY  
Granted May 2016
:::
:::
- Some texthere

### 2024-02-04 about.qmd
wip
add css

@@
 ---
+
+::: {.html}
+<style>
+  iframe {
+    width: 100%;
+    aspect-ratio: 500 / 800;
+    max-width: 500px; /* Optional */
+  }
+</style>
+:::
 
@@
 - Some texthere
+
+### Mastodon
+
+<iframe allowfullscreen sandbox="allow-top-navigation allow-scripts allow-popups allow-popups-to-escape-sandbox" src="https://mastofeed.com/apiv2/feed?userurl=https%3A%2F%2Fmastodon.online%2Fusers%2Ftomstafford&theme=light&size=100&header=true&replies=false&boosts=false"></iframe>

### 2024-02-04 index.qmd
come on now
new
new2
wip

@@
 format: html
-editor: visual
+page-layout: full
+image: /tom_2020.jpg
 ---
+
+::: {.html}
+<style>
+  iframe {
+    width: 100%;
+    aspect-ratio: 500 / 800;
+    max-width: 500px; /* Optional */
+  }
+</style>
+:::
 
@@
 
+HI
+
 ## Updates on <mastodon.online/@tomstafford>
 
-<iframe allowfullscreen sandbox="allow-top-navigation allow-scripts allow-popups allow-popups-to-escape-sandbox" width="500" height="800" src="https://mastofeed.com/apiv2/feed?userurl=https%3A%2F%2Fmastodon.online%2Fusers%2Ftomstafford&theme=light&size=100&header=true&replies=false&boosts=false"></iframe>
-
+<iframe allowfullscreen sandbox="allow-top-navigation allow-scripts allow-popups allow-popups-to-escape-sandbox" src="https://mastofeed.com/apiv2/feed?userurl=https%3A%2F%2Fmastodon.online%2Fusers%2Ftomstafford&theme=light&size=100&header=true&replies=true&boosts=false"></iframe>
 Colophon
 
-Website made with [Quarto](https://quarto.org), hosted on github pages. Styles taken from <https://ddimmery.com/posts/quarto-website/>
+Website made with [Quarto](https://quarto.org), hosted on [github](https://github.com/tomstafford/tomstafford.github.io). Styles taken from <https://ddimmery.com/posts/quarto-website/>

### 2024-02-04 index.qmd
wip

@@
 
-<iframe allowfullscreen sandbox="allow-top-navigation allow-scripts allow-popups allow-popups-to-escape-sandbox" src="https://mastofeed.com/apiv2/feed?userurl=https%3A%2F%2Fmastodon.online%2Fusers%2Ftomstafford&theme=light&size=100&header=true&replies=true&boosts=false"></iframe>
+<iframe allowfullscreen sandbox="allow-top-navigation allow-scripts allow-popups allow-popups-to-escape-sandbox" src="https://mastofeed.com/apiv2/feed?userurl=https%3A%2F%2Fmastodon.online%2Fusers%2Ftomstafford&theme=light&size=100&header=false&replies=false&boosts=false"></iframe>
 Colophon

### 2024-02-04 index.qmd
icons

--- 2024-02-04 index.qmd
@@
 
-::: {.html}
-<style>
-  iframe {
-    width: 100%;
-    aspect-ratio: 500 / 800;
-    max-width: 500px; /* Optional */
-  }
-</style>
-:::
-
+::: {.column-page-inset}
+::: {.column-page-inset-left}
 I study learning and decision making.
@@
 More recently a strand of my research looks at complex decisions, and the psychology of reason, argument and persuasion.
+:::
 
-HI
+<div class="column-margin column-container">
+![](tom_2020.jpg){.rounded}
+</div>
+:::
 
-## Updates on <mastodon.online/@tomstafford>
+{{< pagebreak >}}
 
-<iframe allowfullscreen sandbox="allow-top-navigation allow-scripts allow-popups allow-popups-to-escape-sandbox" src="https://mastofeed.com/apiv2/feed?userurl=https%3A%2F%2Fmastodon.online%2Fusers%2Ftomstafford&theme=light&size=100&header=true&replies=true&boosts=false"></iframe>
-Colophon
+::: {.column-page-inset .text-center}
+```{=html}
+<a class="btn btn-outline-dark", href="https://tomstafford.substack.com" target="_blank" rel="noopener noreferrer">
+    <i class="bi bi-substack" role='img' aria-label='Substack'></i>
+</a>
 
-Website made with [Quarto](https://quarto.org), hosted on [github](https://github.com/tomstafford/tomstafford.github.io). Styles taken from <https://ddimmery.com/posts/quarto-website/>
+<a class="btn btn-outline-dark", href="https://mastodon.online/@tomstafford" target="_blank" rel="noopener noreferrer">
+    <i class="bi bi-mastodon" role='img' aria-label='Mastodon'></i>
+</a>
+
+<a class="btn btn-outline-dark", href="https://github.com/tomstafford" target="_blank" rel="noopener noreferrer">
+    <i class="bi bi-github" role='img' aria-label='Github'></i>
+</a>
+
+<a class="btn btn-outline-dark", href="https://www.linkedin.com/in/tom-stafford-81a737262/" target="_blank" rel="noopener noreferrer">
+    <i class="bi bi-linkedin" role='img' aria-label='LinkedIn'></i>
+</a>
+
+<a class="btn btn-outline-dark", href="https://scholar.google.co.uk/citations?user=bMEna2UAAAAJ&hl=en&oi=ao" target="_blank" rel="noopener noreferrer">
+    <i class="ai ai-google-scholar" role='img' aria-label='Google Scholar'></i>
+</a>
+
+<a class="btn btn-outline-dark", href="mailto:t.stafford@sheffield.ac.uk" target="_blank" rel="noopener noreferrer">
+    <i class="ai bi-envelope" role='img' aria-label='email'></i>
+</a>
+```
+:::
+
+{{< pagebreak >}}
+
+## Colophon
+
+Website made with [Quarto](https://quarto.org), hosted on [github](https://github.com/tomstafford/tomstafford.github.io).
+Site style & structure from [Drew Dimmery](https://ddimmery.com/posts/quarto-website/).

### 2024-02-04 news.qmd
icons

---
title: "News"
editor: source
---

::: html
```{=html}
<style>
  iframe {
    width: 100%;
    aspect-ratio: 500 / 800;
    max-width: 500px; /* Optional */
  }
</style>
```
:::

## Updates from <mastodon.online/@tomstafford>

<iframe allowfullscreen sandbox="allow-top-navigation allow-scripts allow-popups allow-popups-to-escape-sandbox" src="https://mastofeed.com/apiv2/feed?userurl=https%3A%2F%2Fmastodon.online%2Fusers%2Ftomstafford&theme=light&size=100&header=false&replies=false&boosts=false"></iframe>
Colophon

### 2024-02-04 done.qmd
Parking

---
title: "Done"
---

Recording things i've done which don't go under [Publications](https://tomstafford.sites.sheffield.ac.uk/outputs/scholarly-publications), 
[Talks](https://tomstafford.sites.sheffield.ac.uk/outputs/talks) or Newsletter: <https://tomstafford.substack.com/>. Most of these posted to [Mastodon](https://mastodon.online/@tomstafford) too.

## 2023

December 2023 : joined the PsyArXiv Scientific Advisory Board and approved as chair of the public engagement subcommittee. <https://osf.io/preprints/psyarxiv>

2023-11-10; Worked with Lingyu-Meng on a novel visualisation of how group discussion shifts people's opinions : <a href="Dynamics of group discussion in agreement-error space">https://lingyu-meng.github.io/convergence-valence_space/</a>

2023-11-07-: elected Chair of UKRN Institutional Leads group

Sept 2022 - Sept 2023 Coordinator for UKRN [Open Research programme](https://www.ukrn.org/open-research-programme/), [workstream 1: training](https://www.ukrn.org/ws1-training/)

2023 August made <https://tomstafford.github.io/imdb/>, showing change in crowdsourced ratings of summer movies:

<img src="https://tomstafford.github.io/imdb/plots/average_ratings_ordered.png" height=400>

2023 July Consulted on [University of Sheffield Guidelines on Generative AI](https://sheffield.libguides.com/genai/)

2023-05-23 Analysis of Open Editors data: <https://tomstafford.github.io/editors/>

<img src="https://tomstafford.github.io/editors/figs/gpa_vs_eds.png" height = 400>

2023-05-18 Chaired UKRN/RoRI panel on [The Future of Peer Review](https://www.ukrn.org/event/future-of-peer-review-may2023/). ([Recording](https://youtu.be/BMeSh6esehE), [Slides](https://osf.io/ce3ts/))

2023-05-05 Co-author on UKRN working paper on [Open Research Training Resources and Priorities](https://osf.io/s2f6k/), ([news item](https://www.ukrn.org/2023/05/05/ukrn-first-working-paper-on-training-priorities-and-resources/))

2023-05-10 Cited in Science, Innovation and Technology Committee report on [Reproducibility and research integrity](https://publications.parliament.uk/pa/cm5803/cmselect/cmsctech/101/summary.html). Written evidence:[Commercial involvement in academic publishing is key to research reliability and should face greater public scrutiny](https://osf.io/preprints/metaarxiv/rjmvh)

2023-04-15 Chaired [Straight to the Facts: Can we save public debate? A dialogue with Will Moy](https://www.eventbrite.co.uk/e/straight-to-the-facts-can-we-save-public-debate-a-dialogue-with-will-moy-tickets-546336496167)

2023-02-19 Updated my minimal working example of RMarkdown + papaja + tenzing for APA formatted manuscript preparation, to include a rights retention statement : <https://github.com/tomstafford/rmarkdown_apa>

2023-02-06 Teaching my MSc course in Data Management and Visualisation. Materials, all CC-BY, and containing many links and resources on all things research project management, data wrangling and #dataviz  here <https://tomstafford.github.io/psy6422/>

2023-02-01 and forever: taking part in [UCU strike action](https://mastodon.online/@tomstafford/109788334770383538)

2023-01-24 Attended launch of [N8 Research Partnership stands up for researchers with new Rights Retention statement](https://www.n8research.org.uk/n8-research-partnership-rights-retention-statement/)

2023-01-17 Celebrating [University of Sheffield announcing rights retention policy](https://www.researchprofessional.com/0/rr/news/uk/universities/2023/1/University-of-Sheffield-approves-policies-to-bolster-open-research.html)

2023-01-16 Retired the [Choice Engine](https://tomstafford.github.io/choice-engine-text/) bot

2023-01-09 Graduation for Psychological Research Method with Data Science MSc [class of 2021](https://mastodon.online/@tomstafford/109659193946308768)

2023-01-06 Updated: Experiment Design Checklist <https://tomstafford.github.io/psy-checklist/>

2023-01-05 [Christmas message 2022](https://tomstafford.sites.sheffield.ac.uk/news/christmas-message-2022)

2023-01-01 [Archive of tweets 2008-2022](https://idiolect.org.uk/tweets/)

# 2020

Led development and adoption of the [University of Sheffield statement on Open Research](https://www.sheffield.ac.uk/openresearch/university-statement-open-research)

# Earlier

2017 Organised [Mind Matters](https://tomstafford.sites.sheffield.ac.uk/sub-sites/mind-matters) 'a series of events based on various psychological research to bring knowledge to the general public and showcase Sheffield as a hub for psychology!'

2012 - 2017 Wrote a column for [BBC Future](https://www.bbc.com/future/columns/neurohacks)

2012-09 I wrote some of the code in LongArm, [a robot which draws labrynthine patterns](https://www.youtube.com/watch?v=lSuvSsDrEAw), by Matthias Jones

### 2024-02-04 about.qmd
wip
Parking
intro text

--- 2024-02-04 about.qmd
@@
 
-I am Professor of Cognitive Science in the [Department of Psychology, University of Sheffield](https://www.sheffield.ac.uk/psychology) and Senior Research Fellow at the [Research on Research Institute](https://researchonresearch.org/).
+::: {.column-page-inset-left}
+I study learning and decision making.
+Much of my research looks at risk and bias, and their management, in decision making.
+I am also interested in skill learning, using measures of behaviour informed by work done in computational theory and neuroscience.
+More recently a strand of my research looks at complex decisions, and the psychology of reason, argument and persuasion.
+:::
 
@@
 - Experimental Design
-
-### Education
-
-::: {.d-flex .justify-content-between}
-::: {}
-**New York University**  
-PhD in clevrness
-Not really
-:::
-::: {.text-end}
-New York, NY  
-Granted May 2016
-:::
-:::
-- Some texthere

### 2024-02-04 index.qmd
Parking
intro text

@@
 ---
-title: "Tom Stafford, Professor of Cognitive Science"
+title: "Tom Stafford"
 format: html
@@
 ---
+::: {.column-page-inset}
 
-::: {.column-page-inset}
-::: {.column-page-inset-left}
-I study learning and decision making.
-Much of my research looks at risk and bias, and their management, in decision making.
-I am also interested in skill learning, using measures of behaviour informed by work done in computational theory and neuroscience.
-More recently a strand of my research looks at complex decisions, and the psychology of reason, argument and persuasion.
+![](tom_2020.jpg){width="20%"}
+
+I teach and research in the [Department of Psychology](https://www.sheffield.ac.uk/psychology) at the University of Sheffield as Professor of Cognitive Science.
+My research and teaching focuses on applying insights from neuroscience, experimental design and data science to the topics of learning, decision making, reasoning and bias.
+
+I Direct the MSc programmes in Psychological Research Methods, and set up the MSc in Psychological Research Methods with Data Science.
+I teach a module on [Data Management and Visualisation](https://tomstafford.github.io/psy6422/).
+
+At the University I hold the position of Research Practice Lead, an institution-wide role with a remit to encourage practices which support robust and trusted research.
+As Research Practice Lead, I represent the University of Sheffield as Institutional Lead for the UK Reproducibility Network, and chair of the national UKRN Institutional Leads group.
+
+As Senior Fellow at the [Research on Research Institute](https://researchonresearch.org/), I lead the programme [AFIRE: Accelerator For Innovation &amp; Research Funding Experimentation](https://researchonresearch.org/project/a-f-i-r-e/).
+
+I am on the [PsyArXiv](https://osf.io/preprints/psyarxiv) Scientific Advisory Board as chair of the Public Engagement Subcommittee.
+
+For non-specialist audiences, I have written a [best-selling book](https://mindhacks.com/book/), an [award winning blog](https://mindhacks.com/) and columns for venues including BBC, New Scientist, The Guardian and The Conversation.
+I have also written some mediocre selling books, some widely ignored blogs and tweeted jokes which I thought were hilarious at the time but which received precisely zero likes and zero retweets.
+
 :::
 
-<div class="column-margin column-container">
-![](tom_2020.jpg){.rounded}
-</div>
-:::
+This page is a test. Most current material is at [tomstafford.sites.sheffield.ac.uk](https://tomstafford.sites.sheffield.ac.uk/)
+
+Or you can find traces on these other platforms:
 

### 2024-02-05 index.qmd
wip

@@
 
-![](tom_2020.jpg){width="20%"}
+![](tom_2020.jpg){width="25%"}
 
@@
 At the University I hold the position of Research Practice Lead, an institution-wide role with a remit to encourage practices which support robust and trusted research.
-As Research Practice Lead, I represent the University of Sheffield as Institutional Lead for the UK Reproducibility Network, and chair of the national UKRN Institutional Leads group.
+As Research Practice Lead, I represent the University of Sheffield on the UK Reproducibility Network, and chair the national UKRN Institutional Leads group.
 
 As Senior Fellow at the [Research on Research Institute](https://researchonresearch.org/), I lead the programme [AFIRE: Accelerator For Innovation &amp; Research Funding Experimentation](https://researchonresearch.org/project/a-f-i-r-e/).
+We seek to catalyse the generation and use of high quality evidence on research processes ("Metaresearch").
 
@@
 
-This page is a test. Most current material is at [tomstafford.sites.sheffield.ac.uk](https://tomstafford.sites.sheffield.ac.uk/)
+These pages are intended to replace [tomstafford.sites.sheffield.ac.uk](https://tomstafford.sites.sheffield.ac.uk/), and will reflect my professional activities.
+
+My non-professional activities are recorded on my personal blog at <https://idiolect.org.uk/notes/>
 

### 2024-05-11 index.qmd
smalls

@@
 
-I Direct the MSc programmes in Psychological Research Methods, and set up the MSc in Psychological Research Methods with Data Science.
+I direct the MSc programmes in Psychological Research Methods, and set up the MSc in Psychological Research Methods with Data Science.
 I teach a module on [Data Management and Visualisation](https://tomstafford.github.io/psy6422/).
@@
 At the University I hold the position of Research Practice Lead, an institution-wide role with a remit to encourage practices which support robust and trusted research.
-As Research Practice Lead, I represent the University of Sheffield on the UK Reproducibility Network, and chair the national UKRN Institutional Leads group.
+As Research Practice Lead, I represent the University of Sheffield on the [UK Reproducibility Network](https://www.ukrn.org/), for which I chair the national [UKRN Institutional Leads group](https://www.ukrn.org/institutional-leads/).
 

### 2024-05-12 publications.qmd
ipdates

---
title: "Publications"
---

[Google scholar profile](https://scholar.google.co.uk/citations?hl=en&user=bMEna2UAAAAJ&view_op=list_works&sortby=pubdate), ORCID ID : [0000-0002-8089-9479](http://orcid.org/0000-0002-8089-9479)

# Theme highlights

--------------------

## Data intensive psychology:

-   Panagiotidi, M., Zavlis, O., Jones, M., & Stafford, T. (2023). [The three-dimensional community structure of ADHD traits captured by the ASRS scale: An Exploratory Graph Analysis](http://doi.org/10.1002/mpr.1997). International Journal of Methods in Psychiatric Research.  http://doi.org/10.1002/mpr.1997

-   Stafford, T., and Vaci, N. (2022). [Maximizing the potential of digital games for understanding skill acquisition](https://doi.org/10.1177/09637214211057841). Current Directions in Psychological Science, 31(1), 49-55.  <https://doi.org/10.1177/09637214211057841> [[web/mobile version](https://journals.sagepub.com/doi/full/10.1177/09637214211057841)]

-   Bannard, C., Leriche, M., Bandmann, O., Brown, C., Ferracane, E., Sánchez-Ferro, A., Obeso, J., Redgrave, P. and Stafford, T. (2019). [Reduced habit-driven errors in Parkinson's Disease](https://www.nature.com/articles/s41598-019-39294-z). Nature Scientific Reports 9(1), 3423. ([pre-print](https://psyarxiv.com/b25tf/))

## Metaresearch

-   Jones, A., Stafford, T., & Petrovskaya, E. (under review). [Exploring the multiverse of analysis options for the Addiction Stroop](https://psyarxiv.com/prfu2/).

-   Stafford T, Rombach I, Hind D et al. (2023) [Where next for partial randomisation of research funding? The feasibility of RCTs and alternatives](https://wellcomeopenresearch.org/articles/8-309/v1) Wellcome Open Res 2023, 8:309 (https://doi.org/10.12688/wellcomeopenres.19565.1)

-   Bendiscioli, Sandra; Firpo, Teo; Bravo-Biosca, Albert; Czibor, Eszter; Garfinkel, Michele; Stafford, Tom; et al. (2022): [The Experimental Research Funder's Handbook](https://rori.figshare.com/articles/report/The_experimental_research_funder_s_handbook_final_version_/19459328) (Revised edition, June 2022, ISBN 978-1-7397102-0-0). Research on Research Institute. Report. https://doi.org/10.6084/m9.figshare.19459328.v2

-   Silberzahn, R. et al (2018). [Many analysts, one dataset: Making transparent how variations in analytical choices affect results](http://journals.sagepub.com/doi/full/10.1177/2515245917747646). Advances in Methods and Practices in Psychological Science, 1(3), 337-356.

    -   See also : '[Science isn't broken](https://fivethirtyeight.com/features/science-isnt-broken/)' and the [interactive visualisation by Mat Evans which allowed us to find an important confound in the source data](https://github.com/mathewzilla/redcard/blob/master/Crowdstorming_visualisation.ipynb).

    -   Ploner, S., & Stafford, T. (2021). [How analysis strategy affects analysis results: Assessing results space and structure of Silberzahn et al. (2018) through model specification](https://osf.io/preprints/psyarxiv/nzskm). Retrieved from osf.io/preprints/psyarxiv/b2hm7

## Decision making & reasoning

-   Stafford, T., Pirrone, A., Croucher, M., and Krystalli, A. (2020). [Quantifying the benefits of using decision models with response time and accuracy data](https://link.springer.com/article/10.3758/s13428-020-01372-w). Behaviour Research Methods, 52, 2142--2155. [doi.org/10.3758/s13428-020-01372-w](https://doi.org/10.3758/s13428-020-01372-w) (pre-print, [web/mobile version](https://idiolect.org.uk/papers/stafford2020/))

-   Brand, C. O., Brady, D., & Stafford, T. (2023, June 27). [The Ideological Turing Test: a behavioural measure of open-mindedness and perspective-taking](https://psyarxiv.com/2e9wn). https://doi.org/10.31234/osf.io/2e9wn

-   Karadzhov, G., Stafford, T., and Vlachos, A. (2023). [DeliData: A dataset for deliberation in multi-party problem solving](https://dl.acm.org/doi/10.1145/3610056). Proceedings of the ACM on Human-Computer Interaction, CSCW. https://doi.org/10.1145/3610056 [[arXiv](https://arxiv.org/abs/2108.05271)]

-   Karadzhov, G., Stafford, T., and Vlachos, A. (2022). [What makes you change your mind? An empirical investigation in online group decision-making conversations](https://www.delibot.xyz/publications/). arXiv preprint [arXiv:2207.12035](https://arxiv.org/abs/2207.12035)

    -   -   See also: [delibot.xyz](https://www.delibot.xyz/)

-   de Kock, C., Stafford, T., & Vlachos, A. (2022). [How to disagree well: Investigating the dispute tactics used on Wikipedia](https://arxiv.org/abs/2212.08353). arXiv preprint arXiv:2212.08353.

### 2024-05-12 research.qmd
ipdates

---
title: "Research"
---

## Reasearch Leadership

As of May 2020, I am [Research Practice Lead for the University of Sheffield](https://sites.google.com/sheffield.ac.uk/orwg/research-practice). This role involves the responsibility of promoting open, transparent, robust and reproducible research at the University. Read more about [our work on open research on the Sheffield University website](https://www.sheffield.ac.uk/openresearch).

From September 2022 I am also a Senior Research Fellow of the [Research on Research Institute (RoRI)](https://researchonresearch.org/). The aim of the Institute, lead by James Wilsdon, is to “translate ideas and evidence into practical, real world solutions to improve research culture and systems”. I lead the programme [AFIRE: Accelerator For Innovation & Research Funding Experimentation](https://researchonresearch.org/project/a-f-i-r-e/).

## Research ambitions

Three core ambitions of my research are:

* Data Intensive Methods – robust, scalable, reproducible experiments and analysis which are transparent, sharable and work with 400,000 data points as well as for 40.

* Interdisciplinarity – collaborating across all scholarly fields.

 * Public Engagement – listening to public interests, sharing research process and outcomes with non-specialists, giving back to the publics involved with research.

## Research Interests

- Decision Making, Bias
- Reasoning
- Metaresearch
- Data Science
- Experimental Design

## Research Grants

-   2023--2025: Research on Research Institute, [AFIRE: Accelerator For Innovation & Research Funding Experimentation](https://researchonresearch.org/project/a-f-i-r-e/) & [Distributed Peer Review Experiment](https://researchonresearch.org/volkswagen-distributed-peer-review/)

-   2022--2025: [Reinforcer-specific value-based decision-making in persistence of and recovery from alcohol use disorder](https://gtr.ukri.org/projects?ref=MR%2FW028476%2F1). [Matt Field](https://www.sheffield.ac.uk/psychology/people/academic/matt-field) (PI), Tom Stafford and Amber Copeland. MRC (£661, 617)

-   2021--2025: [Informing citizens? Effects of imprints on digital political advertising](https://tomstafford.sites.sheffield.ac.uk/news/phd-opportunity-informing-citizens).\
    White Rose Doctoral Training Partnership Collaborative Award, October 2020 to September 2024 (PhD studentship taken up by Hazel Gordon; primary supervisor, with Kate Dommett, and partnered with the [Electoral Reform Society](https://www.electoral-reform.org.uk/)).

-   2021--2026: [Growing and embedding open research in institutional practice and culture](https://www.sheffield.ac.uk/news/university-sheffield-spearhead-open-research-drive). Marcus Munafò (PI) and the UKRN. Research England Development Fund. £8,500,000 (£333,096 to Sheffield).

-   2021--2024: [Opening up minds: engaging dialogue generated from argument maps](https://tomstafford.sites.sheffield.ac.uk/news/engaging-dialogue-generated-from-argument-maps). Paul Piwek (PI), Tom Stafford, Andreas Vlachos, Svetlana Stonyanchev. EPSRC. £711,020 (£218,662 to Sheffield).

-   2020--2023: [Understanding online political advertising: perceptions, uses and regulation](https://tomstafford.sites.sheffield.ac.uk/news/understanding-online-political-advertising). Kate Dommett (PI), Tom Stafford, Nikos Aletras. Leverhulme Trust. (£390,215)

-   2019--2021: Plastics: redefining single-use. Anthony Ryan (PI) and many others. UKRI (Creative Circular Economy Approaches to Eliminate Plastics Waste). (£1,010,896).

-   2019--2020: EEG analysis of errors during skilled typing. Experimental Psychology Society Small Grant Scheme. Tom Stafford (PI), Cigir Kalfaoglu. (£3,500).

-   2018--2019: Assessing functional ability in older adults. Claudia von Bastian (PI). White Rose Collaboration Fund (£9,619).

-   2017--2018: C[yberselves: How Immersive Technologies will Impact our Future Selves](https://gtr.ukri.org/projects?ref=AH%2FR004811%2F1). Tony Prescott (PI), Tom Stafford, Michael Szollosy. AHRC (£78,494).

-   2014--2015: [Neuroimaging as a marker of Attention Deficit Hyperactivity Disorder (ADHD)](https://tomstafford.sites.sheffield.ac.uk/news/neuroimaging-as-a-marker-of-attention-deficit-hyperactivity-disorder-adhd)  Tom Stafford (PI), Paul Overton, Maria Panagiotidi (Sheffield), Tony Morland, Alex Wade (York), Jac Billington, Jean-Francois Delvenne (Leeds). White Rose Collaboration Fund 2014, (£10,996).

-   2014--2015:  [Reduced habitual intrusions : an early marker for Parkinson's Disease?](https://tomstafford.sites.sheffield.ac.uk/news/new-grant-reduced-habitual-intrusions-an-early-marker-for-parkinsons)  Tom Stafford (PI), with Jose Obeso, Peter Redgrave, Colin Bannard. Michael J Fox Foundation ($100,000).

-   2014--2015: [Cyberselves in Immersive Technologies\
    ](http://www.scentro.ac.uk/node/26)Tony Prescott (PI), Tom Stafford, Stuart Wilson (Department of Psychology, Sheffield), Adam Piette, Michael Szollosy (School of English, Sheffield), Julian Savulescu, Hannah Maslen (Philosophy, Oxford). AHRC, (£64,118).

-   2014--2016: [Bias and Blame: Do moral interactions modulate the expression of implicit bias?](https://tomstafford.sites.sheffield.ac.uk/news/new-project-bias-and-blame)  A Leverhulme Trust grant to the University of Nottingham, with Jules Holroyd (PI) and Tom Stafford. (£220,608).

-   2013--2016: Decision making under uncertainty: brains, swarms and markets\
    A studentship network for 3 PhDs at the University of Sheffield (led by Tom Stafford and with Kevin Gurney, James Marshall, Eleni Vasaliki, Jane Binner and Roderich Gross).

-   2012--2013:  Developing Haptics in Assistive Technology for the Visually-Impaired -- HATV-I.\
    Matt Carre (PI), Tom Stafford, Tony Prescott, Mark Hawley. UoS EPSRC Pump-priming fund (£46,000).

-   2013--2014:  'Collicular hyper-responsiveness in Attention Deficit Hyperactivity Disorder.\
    Overton, P.G., Chalhoub, N., Ennis, J., Stafford, T., Codina, C. Sheffield Children's Hospital Charity (£9,284).

-   2011--2012:  A wearable active sensing device using tactile displays\
    £50,000, EPSRC Proof of Concept Funding, via University of Sheffield

-   2009--2013: Intrinsically motivated cumulative learning versatile robots (Principal: Gianluca Baldassarre, ISTCCNR, Rome)\
    €5,900,000 (€771,190 to Sheffield), European Union FP7 grant.

-   2009--2010: Teaching Synthetic Psychology With Lego Robots (Principal: Tony Prescott, Sheffield) University of Sheffield Learning and Teaching Services grant,  (£6,720).

-   2009: [Does the tea really taste better if you put the milk in first?](https://tomstafford.sites.sheffield.ac.uk/sub-sites/tea-taste-test)' Scientific inquiry in public, CILASS Sheffield Undergraduate Research Experience Scheme: Summer studentship (£1,130).

-   2008--2011: White Rose Active Vision Network (Principal: Jim Austin, York)\
    £162,000 (£54,000 to Sheffield), White Rose Network studentship grant.

-   2008--2009: IBL at MSc level (Principal: Tom Stafford), CILASS Scholarship of Teaching grant, University of Sheffield (£2,720).

-   2005: 'The cognitive psychology of decision processing: How does intensity and size of choice-set affect response selection?' (Principal: Tom Stafford), Social Sciences Devolved Funds Grant, University of Sheffield (£3,000).

## Learned Societies

I am a fellow of the [British Psychological Society](https://www.bps.org.uk/) and the [Higher Education Academy](http://advance-he.ac.uk), and a member of the [Cognitive Science Society](https://cognitivesciencesociety.org/), the [Experimental Psychology Society](https://eps.ac.uk/) and the [Psychonomic Society](https://www.psychonomic.org/default.aspx).

### 2024-05-12 index.qmd
update

@@
 
-I teach and research in the [Department of Psychology](https://www.sheffield.ac.uk/psychology) at the University of Sheffield as Professor of Cognitive Science.
-My research and teaching focuses on applying insights from neuroscience, experimental design and data science to the topics of learning, decision making, reasoning and bias.
+As Professor of Cognitive Science, I teach and research in the [School of Psychology](https://www.sheffield.ac.uk/psychology) at the University of Sheffield.
+My work applies insights from neuroscience, experimental design and data science to the topics of learning, decision making, reasoning and bias.
 

### 2024-05-12 publications.qmd
update

@@
 -   de Kock, C., Stafford, T., & Vlachos, A. (2022). [How to disagree well: Investigating the dispute tactics used on Wikipedia](https://arxiv.org/abs/2212.08353). arXiv preprint arXiv:2212.08353.
+
+# Chronological
+
+## In press, and under review
+
+-   Adinugroho, I., Stafford, T., & Bentall, R.
+(2023, November 1).
+[The correlation between conspiracy mentality and vaccine intentions is moderated by social events: Evidence from longitudinal data during COVID-19 pandemic in the UK](https://osf.io/preprints/psyarxiv/5wcnz/).
+Retrieved from osf.io/preprints/psyarxiv/5wcnz
+
+-   Vardal, O., Karapanagiotidis, T., Stafford, T., Drachen, A.
+and Wade, A.
+(2023) [Unsupervised identification of internal perceptual states influencing psychomotor performance](https://www.biorxiv.org/content/10.1101/2023.09.08.556817v2).
+bioRxiv 2023.09.08.556817; doi: https://doi.org/10.1101/2023.09.08.556817
+
+-   Copeland, A., Stafford, T., & Field, M.
+(2023, August 23).
+[Value-based decision-making in regular alcohol consumers following experimental manipulation of alcohol value](https://osf.io/wcks6/).
+https://doi.org/10.31219/osf.io/wcks6
+
+-   Panagiotidi, M., Zavlis, O., Jones, M., & Stafford, T.
+(2023, July 14).
+[The three-dimensional community structure of ADHD traits captured by the ASRS scale: An Exploratory Graph Analysis](https://psyarxiv.com/sakn9).
+Retrieved from psyarxiv.com/sakn9
+
+-   Brand, C.
+O., Brady, D., & Stafford, T.
+(2023, June 27).
+[The Ideological Turing Test: a behavioural measure of open-mindedness and perspective-taking](https://psyarxiv.com/2e9wn).
+https://doi.org/10.31234/osf.io/2e9wn
+
+-   Zhu, J., Dommett, K., & Stafford, T.
+(2023).
+[What makes online political ads unacceptable?
+Interrogating public attitudes to inform regulatory responses](https://preprints.apsanet.org/engage/apsa/article-details/6462be37f2112b41e99fe9bf).
+APSA Preprints.
+doi:10.33774/apsa-2023-rxw1q This content is a preprint and has not been peer-reviewed.
+
+-   Jones, A., Stafford, T., & Petrovskaya, E. (2022). [Exploring the multiverse of analysis options for the Addiction Stroop](https://psyarxiv.com/prfu2/).
+
+-   Panagiotidi, M., Stafford, T., and Overton, P. (submitted). The relationship between cognitive control and task switching and problematic phone use. [Email for document]
+
+-   Karadzhov, G., Stafford, T., and Vlachos, A.
+(2022).
+[What makes you change your mind?
+An empirical investigation in online group decision-making conversations](https://www.delibot.xyz/publications/).
+arXiv preprint [arXiv:2207.12035](https://arxiv.org/abs/2207.12035)
+
+    -   -   See also: [delibot.xyz](https://www.delibot.xyz/)
+
+-   de Kock, C., Stafford, T., & Vlachos, A. (2022). [How to disagree well: Investigating the dispute tactics used on Wikipedia](https://arxiv.org/abs/2212.08353). arXiv preprint arXiv:2212.08353.
+
+## 2023
+
+-   Karadzhov, G., Stafford, T., and Vlachos, A.
+(2023).
+[DeliData: A dataset for deliberation in multi-party problem solving](https://dl.acm.org/doi/10.1145/3610056).
+Proceedings of the ACM on Human-Computer Interaction, CSCW.
+https://doi.org/10.1145/3610056 [[arXiv](https://arxiv.org/abs/2108.05271)]
+
+-   Stafford T, Rombach I, Hind D et al.
+(2023) [Where next for partial randomisation of research funding?
+The feasibility of RCTs and alternatives](https://wellcomeopenresearch.org/articles/8-309/v1) Wellcome Open Res 2023, 8:309 (https://doi.org/10.12688/wellcomeopenres.19565.1)
+
+-   Farag, Y., Brand, C.
+O., Amidei, J., Piwek, P., Stafford, T., Stoyanchev, S., & Vlachos, A.
+(2023).
+Opening up Minds with Argumentative Dialogues.
+SiCON 2023 (co-located with ACL 2023) [[preprint]](https://arxiv.org/abs/2301.06400)
+
+-   Dommett, K., Mensah, S.
+A., Zhu, J., Stafford, T., & Aletras, N.
+(2023).
+[Is There a Permanent Campaign for Online Political Advertising?
+Investigating Partisan and Non-Party Campaign Activity in the UK between 2018--2021](https://www.tandfonline.com/doi/full/10.1080/15377857.2023.2175102).
+Journal of Political Marketing, 1-19.
+
+-   Varbanov V., Overton, P., and Stafford, T.
+(2023).
+[ADHD and ASD traits are indirectly associated with sensory changes through anxiety](https://link.springer.com/article/10.1007/s12144-022-04217-1) Curr Psychol (2023).
+<https://doi.org/10.1007/s12144-022-04217-1> [[preprint](https://psyarxiv.com/dchbs)].
+
+## 2022
+
+-   Vardal, O., Bonometti, V., Drachen, A., Wade, A., & Stafford, T.
+(2022).
+[Mind the gap: Distributed practice enhances performance in a MOBA game](https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0275843).
+Plos one, 17(10), e0275843.
+
+-   Brand, C.
+O., & Stafford, T.
+(2022).
+[Using dialogues to increase positive attitudes towards COVID-19 vaccines in a vaccine-hesitant UK population](https://royalsocietypublishing.org/doi/full/10.1098/rsos.220366).
+Royal Society Open Science, 9(10), 220366.
+
+-   Copeland, A., Stafford, T., Acuff, S.F., Murphy, J.G.
+and Field, M.
+(in press).
+[Behavioral economic and value-based decision-making constructs that discriminate current heavy drinkers versus people who reduced their drinking without treatment](https://psyarxiv.com/5jhdg/).
+Psychology of Addictive Behaviors.
+
+-   Bendiscioli, Sandra; Firpo, Teo; Bravo-Biosca, Albert; Czibor, Eszter; Garfinkel, Michele; Stafford, Tom; et al.
+(2022): [The Experimental Research Funder's Handbook](https://rori.figshare.com/articles/report/The_experimental_research_funder_s_handbook_final_version_/19459328) (Revised edition, June 2022, ISBN 978-1-7397102-0-0).
+Research on Research Institute.
+Report.
+https://doi.org/10.6084/m9.figshare.19459328.v2
+
+-   Copeland et al (in press).
+Methodological issues with value-based decision-making (VBDM) tasks: the effect of trial wording on evidence accumulation outputs from the EZ drift-diffusion model.
+Cogent.
+
+-   Stafford, T. (in press). [Evidence for the rationalisation phenomenon is exaggerated](https://psyarxiv.com/aygh6/). Behavioural and Brain Sciences (commentary)
+
+-   Stafford, T., and Vaci, N.
+(2022).
+[Maximizing the potential of digital games for understanding skill acquisition](https://doi.org/10.1177/09637214211057841).
+Current Directions in Psychological Science, 31(1), 49-55.
+<https://doi.org/10.1177/09637214211057841> [[web/mobile  version](https://journals.sagepub.com/doi/full/10.1177/09637214211057841)]
+
+-   Pirrone, A., Reina, A, Stafford, T., Marshall, J.A.R., and Gobet, F.
+(2022).
+[Magnitude-sensitivity: Rethinking decision-making](https://www.sciencedirect.com/science/article/pii/S1364661321002618?casa_token=W5lKMgVueasAAAAA:GDwwQu4GBq4QtdbTWvjt7Y6-OY9kr7tgT0nGjQ1nu8a74laE5TCtmRotkpw5vQO6nQ8q14gH).
+Trends in Cognitive Sciences, 26(1), 66-80 [[OA version here](https://www.giovannireina.com/pdf/pirrone-TiCS2022.pdf)]
+
+## 2021
+
+-   Stafford, T.
+and Brand, C.O.
+(2021).
+[Commercial involvement in academic publishing is key to research reliability and should face greater public scrutiny](https://osf.io/preprints/metaarxiv/rjmvh).
+Evidence submitted to the House of Common Science and Technology Committee inquiry on reproducibility and research integrity.
+
+-   Copeland, A., Stafford, T., and Field, M.
+(2021).
+Recovery from addiction: A synthesis of perspectives from behavioral economics, psychology, and decision modeling.
+In The Handbook of Alcohol Use (pp.
+563-579).
+Academic Press.
+
+-   Brand, C.
+O.
+and Stafford, T.
+(2021).
+Review 1: "Information Delivered by a Chatbot Has a Positive Impact on COVID-19 Vaccines Attitudes and Intentions." Rapid Reviews COVID-19.
+<https://doi.org/10.1162/2e3983f5.237d4808>
+
+-   Ploner, S., & Stafford, T.
+(2021).
+[How analysis strategy affects analysis results: Assessing results space and structure of Silberzahn et al.
+(2018) through model specification](https://osf.io/preprints/psyarxiv/b2hm7).
+Retrieved from osf.io/preprints/psyarxiv/b2hm7
+
+## 2020
+
+-   Stafford, T., Pirrone, A., Croucher, M., and Krystalli, A.
+(2020).
+[Quantifying the benefits of using decision models with response time and accuracy data](https://link.springer.com/article/10.3758/s13428-020-01372-w).
+Behaviour Research Methods, 52, 2142--2155.
+[doi.org/10.3758/s13428-020-01372-w](https://doi.org/10.3758/s13428-020-01372-w) (pre-print, [web/mobile version](https://idiolect.org.uk/papers/stafford2020/))
+
+    -   See also the interactive data explorer: sheffield-[university.shinyapps.io/decision_power](https://sheffield-university.shinyapps.io/decision_power/)
+
+-   Dhir, N., Edman, M., Sanchez Ferro, A., Stafford, T., and Bannard, C.
+(2020).
+[Identifying robust markers of Parkinson's Disease in typing behaviour using a CNN-LSTM network](https://www.aclweb.org/anthology/2020.conll-1.47/).
+In Proceedings of Conference on Computational Natural Language Learning (CoNLL 2020).
+
+-   Panagiotidi, M., Overton, P.
+and Stafford, T.
+(2020).
+[The relationship between sensory processing sensitivity and Attention Deficit Hyperactivity Disorder traits: a spectrum approach](https://www.sciencedirect.com/science/article/pii/S0165178120331383).
+Psychiatry Research, 293, 113477.
+
+-   Scaife, R., Stafford, T., Bunge, A., and Holroyd, J.
+(2020).
+[To blame?
+The effects of moralized feedback on implicit racial bias](https://www.collabra.org/article/10.1525/collabra.251/).
+Collabra: Psychology, 6(1), 30.
+DOI: http://doi.org/10.1525/collabra.251
+
+-   Pirrone, A., Illin, J., Stafford, T., Milne, E.
+(2020).
+[A diffusion model decomposition of orientation discrimination in children with Autism Spectrum Disorder](https://www.tandfonline.com/eprint/VIIZBcGgYpItKcCGw27I/full).
+European Journal of Developmental Psychology, 17, 2, 213-230.
+
+-   Williams, L., Butler, J., Thirkettle, M., Stafford, T., Quinlivan, B., MacGovern, E., ...
+and Hutchinson, M.
+(2020).
+[Slowed luminance reaction times in cervical dystonia: disordered superior colliculus processin](https://onlinelibrary.wiley.com/doi/full/10.1002/mds.27975)g.
+Movement Disorders, 35(5), 877-880.
+
+-   Field, M., Heather, N., Murphy, J.
+G., Stafford, T., Tucker, J.
+A., & Witkiewitz, K.
+(2020).
+[Recovery from addiction: Behavioral economics and value-based decision making](https://psyarxiv.com/rfjwu/).
+Psychology of Addictive Behaviors, 34(1), 182--193.
+https://doi.org/10.1037/adb0000518
+
+-   Gyurkovics, M., Stafford, T., Levita, L.
+(2020).
+[Cognitive control across adolescence: Dynamic adjustments and mind-wandering](https://www.ncbi.nlm.nih.gov/pubmed/31599622).
+Journal of Experimental Psychology: General, 149(6), 1017--1031.
+
+-   Tierney, W., Hardy III, J.
+H., Ebersole, C.
+R., Leavitt, K., Viganola, D., Clemente, E.
+G., ...
+& Hiring Decisions Forecasting Collaboration.
+(2020).
+[Creative destruction in science](https://www.sciencedirect.com/science/article/pii/S0749597820303678).
+Organizational Behavior and Human Decision Processes, 161, 291-309.
+
+## 2019
+
+-   Hampsey, E., Overton, P.G., Stafford, T.
+(2019).
+[Microsaccade rate as a measure of drug response](https://bop.unibe.ch/JEMR/article/view/JEMR.12.6.12).
+Journal of Eye Movement Research, 12(6).
+https://doi.org/10.16910/jemr.12.6.12   Open data/analysis scripts/etc: <https://osf.io/je8hf/>
+
+-   Bannard, C., Leriche, M., Bandmann, O., Brown, C., Ferracane, E., Sánchez-Ferro, A., Obeso, J., Redgrave, P.
+and Stafford, T.
+(2019).
+[Reduced habit-driven errors in Parkinson's Disease](https://www.nature.com/articles/s41598-019-39294-z).
+Nature Scientific Reports 9(1), 3423.
+([pre-print](https://psyarxiv.com/b25tf/))
+
+-   Holroyd, J., Scaife, R., Stafford, T. (in press). [What is implicit bias](http://onlinelibrary.wiley.com/doi/10.1111/phc3.12437/full)? Philosophy Compass, 12(10), e12437.
+
+-   Holroyd, J., Scaife, R., Stafford, T. (in press). [Responsibility for Implicit Bias](http://onlinelibrary.wiley.com/doi/10.1111/phc3.12410/abstract). Philosophy Compass, 12(3), e12410.
+
+-   Thirkettle, M., Thyoka, M., Fernandes, N., Gopalan, P., Stafford, T.
+Offiah, A.C.
+(2019).
+[Internet-based measurement of visual assessment skill of trainee radiologists: developing a sensitive tool](https://www.birpublications.org/doi/abs/10.1259/bjr.20180958).
+British Journal of Radiology, 92(1097), 20180958.
+
+## 2018
+
+-   Silberzahn, R.
+et al (2018).
+[Many analysts, one dataset: Making transparent how variations in analytical choices affect results](http://journals.sagepub.com/doi/full/10.1177/2515245917747646).
+Advances in Methods and Practices in Psychological Science, 1(3), 337-356.
+See also : '[Science isn't broken](https://fivethirtyeight.com/features/science-isnt-broken/)' and the [interactive visualisation by Mat Evans which allowed us to find an important confound in the source data](https://github.com/mathewzilla/redcard/blob/master/Crowdstorming_visualisation.ipynb).
+
+-   Stafford, T., Holroyd, J., and Scaife, R.
+(2018).
+[Confronting bias in judging: A framework for addressing psychological biases in decision making](https://psyarxiv.com/nzskm).
+https://doi.org/10.31234/osf.io/nzskm
+
+    -   See also: [Judiciary.uk: Biases in decision making](https://www.judiciary.uk/wp-content/uploads/2018/02/stafford-biases-in-decision-making-winter-2017.pdf).
+
+-   Stafford, T. (2018). [Female chess players outperform expectations when playing men](http://journals.sagepub.com/doi/10.1177/0956797617736887). Psychological Science, 29(3), 429-436. (Preprint).
+
+-   Pirrone, A., Azab, H., Hayden, B.
+Y., Stafford, T., and Marshall, J.
+A.
+R.
+(2018).
+[Evidence for the speed--value trade-off: Human and monkey decision making is magnitude sensitive](http://eprints.whiterose.ac.uk/109297/).
+Decision, 5(2), 129-142.
+
+-   Panagiotidi, M., Overton, P.G., Stafford, T.
+(2018).
+[The relationship between ADHD traits and sensory sensitivity in the general population](https://www.sciencedirect.com/science/article/pii/S0010440X17302365).
+Comprehensive Psychiatry, 80, 179-185.
+
+-   Kalfaoğlu, Ç., Stafford, T.
+and Milne, E.
+(2018).
+[Frontal theta band oscillations predict error correction and post error slowing in typing](https://www.ncbi.nlm.nih.gov/pubmed/28447844).
+Journal of Experimental Psychology: Human Perception and Performance, 44(1), 69-88.
+
+## 2017
+
+-   Stafford, T., Devlin, S., Sifa, R., and Drachen, A.
+(2017).
+[Exploration and skill acquisition in a major online game](https://mindmodeling.org/cogsci2017/papers/0615/paper0615.pdf).
+In Proceedings of The 39th Annual Meeting of the Cognitive Science Society.
+
+-   Panagiotidi, M., Overton, P.G., Stafford, T.
+(2017).
+[Multisensory integration and ADHD-like traits: Evidence for an abnormal temporal integration window in ADHD](http://www.sciencedirect.com/science/article/pii/S000169181630302X).
+Acta Psychologica, 181, 10--17.
+
+-   Panagiotidi, M., Overton, P.G., Stafford, T. (2017). [Co-occurrence of ASD and ADHD traits in the general population](http://eprints.staffs.ac.uk/3487/). Journal of Attentional Disorders.
+
+-   Panagiotidi, M., Overton, P.G., Stafford, T.
+(2017).
+[Increased microsaccade rate in individuals with ADHD traits](https://bop.unibe.ch/index.php/JEMR/article/view/2963).
+Journal of Eye Movement Research.
+10, 1.
+
+-   Pirrone, A., Dickinson, A., Gomez, R., Stafford, T.
+and Milne, E.
+(2017).
+[Understanding perceptual judgement in autism spectrum disorder using the drift diffusion model](http://eprints.whiterose.ac.uk/107355/1/Perceptual%20Judgment%20in%20ASD%20final%20copy.pdf).
+Neuropsychology, 31 (2), 173--180.
+
+-   Pirrone, A., Marshall, J.
+A., and Stafford, T.
+(2017).
+[A drift diffusion model account of the semantic congruity effect in a classification paradigm](https://jnc.psychopen.eu/article/view/79).
+Journal of Numerical Cognition, 3(1), 77--96.
+
+-   Stafford, T.
+and Haasnoot, E.
+(2017).
+[Testing sleep consolidation in skill learning: a field study using an online game](http://onlinelibrary.wiley.com/wol1/doi/10.1111/tops.12232/abstract).
+Topics in Cognitive Science.
+9(2), 485--496.
+([data + code](https://osf.io/fckq8/))
+
+-   Panagiotidi, M., Overton, P.G., Stafford, T.
+(2017).
+[Attention Deficit Hyperactivity Disorder-like traits and distractibility in the visual periphery](http://pec.sagepub.com/content/early/2016/11/28/0301006616681313.abstract).
+Perception, 46 (6), 665--678.
+
+## 2016
+
+-   Bednark J., Reynolds J., Stafford T., Redgrave P.
+and Franz E.
+(2016).
+[Action experience and action discovery in medicated individuals with Parkinson's disease](http://journal.frontiersin.org/article/10.3389/fnhum.2016.00427).
+Frontiers in Human Neuroscience, 10, 427.
+DOI 10.3389/fnhum.2016.00427.
+
+-   Bertram, C., and Stafford, T.
+(2016).
+[Improving training for sensory augmentation using the science of expertise](http://www.sciencedirect.com/science/article/pii/S0149763415300634).
+Neuroscience & Biobehavioral Reviews, 68, 234--244.
+
+-   Lu, Y., Stafford, T., and Fox, C. (2016). [Maximum saliency bias in binocular fusion](http://www.tandfonline.com/doi/abs/10.1080/09540091.2016.1159181). Connection Science, 28(3),258-269.
+
+## 2015
+
+-   Thirkettle, M., Stafford, T., and Offiah, A. (2015). Internet Based Measurement of Visual Expertise in Radiological Skill. Perception, 44, 44-45.
+
+## 2014
+
+-   Stafford, T.
+and Dewar, M.
+(2014).
+[Tracing the trajectory of skill learning with a very large sample of online game players](http://pss.sagepub.com/content/25/2/511).
+Psychological Science, 25(2) 511--518.
+See also: [Data and analysis code](https://github.com/tomstafford/axongame).
+
+-   Baldassarre, G., Stafford, T., Mirolli, M., Redgrave, P., Ryan, R.
+M., and Barto, A.
+(2014).
+[Intrinsic motivations and open-ended development in animals, humans, and robots: an overview](http://journal.frontiersin.org/Journal/10.3389/fpsyg.2014.00985/full).
+Frontiers in Psychology, 5(985).
+doi: 10.3389/fpsyg.2014.00985 (introduction to Special Topic we edited).
+
+-   Kalfaoğlu, Ç & Stafford, T.
+(2014).
+[Performance breakdown effects dissociate from error detection effects in typing](http://www.tandfonline.com/eprint/neYR97ser5C3sFI8pcuT/full).
+The Quarterly Journal of Experimental Psychology, 67(3), 508--524.
+
+-   Stafford, T.
+(2014).
+[The perspectival shift: how experiments on unconscious processing don't justify the claims made for them](http://journal.frontiersin.org/Journal/10.3389/fpsyg.2014.01067/full).
+Frontiers in Psychology, 5, 1067.
+doi:10.3389/fpsyg.2014.01067.
+
+-   Stafford, T., Elgueta, H., Cameron, H.
+(2014).[ Students' engagement with a collaborative wiki tool predicts enhanced written exam performance](http://www.researchinlearningtechnology.net/index.php/rlt/article/view/22797).
+Research in Learning Technology, 22, 22797.
+doi:[10.3402/rlt.v22.22797](http://dx.doi.org/10.3402/rlt.v22.22797).
+
+-   Pirrone, A., Stafford, T., and Marshall, J.
+A.
+R.
+(2014).
+[When natural selection should optimise speed-accuracy trade-offs](http://www.frontiersin.org/decision%20neuroscience/10.3389/fnins.2014.00073/full).
+Frontiers in Neuroscience, 8(73).
+doi: 10.3389/fnins.2014.00073.
+
+-   Redgrave, P., Vautrelle, N., and Stafford, T.
+(2014).
+[Interpretive conundrums when practice doesn't always make perfect](http://www.ncbi.nlm.nih.gov/pubmed/24167063).
+Movement Disorders: Official Journal of the Movement Disorder Society, 29(1), 7-10.
+doi:10.1002/mds.25726.
+
+-   Kerdegari, H., Kim, Y., Stafford, T., and Prescott, T.
+J.
+(2014, June).
+[Centralizing bias and the vibrotactile funnelling illusion on the forehead](https://eprints.whiterose.ac.uk/100435/1/Eurohaptic-final%20version-HK.pdf).
+In International Conference on Human Haptic Sensing and Touch Enabled Computer Applications (pp.
+55-62).
+Springer, Berlin, Heidelberg.
+
+## 2013
+
+-   Bertram, C., Evans, M.
+H., Javaid, M., Stafford, T., and Prescott, T.
+(2013).
+Sensory augmentation with distal touch: the tactile helmet project.
+In Biomimetic and Biohybrid Systems (pp.
+24-35).
+Springer Berlin Heidelberg.
+
+-   Thirkettle, M., Walton, T., Redgrave, P., Gurney, K., and Stafford, T.
+(2013).
+[No learning where to go without first knowing where you're coming from: action discovery is trajectory, not endpoint based](http://www.frontiersin.org/cognitive_science/10.3389/fpsyg.2013.00638/abstract).
+Frontiers in Cognitive Science, 4:, 638.
+doi:10.3389/fpsyg.2013.00638.
+
+-   Walton, T., Thirkettle, M., Redgrave, P., Gurney, K.
+N., and Stafford, T.
+(2013).
+[The discovery of novel actions is affected by very brief reinforcement delays and reinforcement modality](http://www.tandfonline.com/doi/full/10.1080/00222895.2013.806108).
+Journal of Motor Behavior, 45(4), 351--360.
+
+-   Bednark, J.
+G., Reynolds, J.
+N.
+J., Stafford, T., Redgrave, P., and Franz, E.
+A.
+(2013).
+[Creating a movement heuristic for voluntary action: Electrophysiological correlates of movement-outcome learning](http://www.sciencedirect.com/science/article/pii/S0010945211003224).
+Cortex, 49(3), 771-780.
+doi:10.1016/j.cortex.2011.12.005.
+
+-   Thirkettle, M., Walton, T., Shah, A., Gurney, K., Redgrave, P., and Stafford, T.
+(2013).
+[The path to learning: Action acquisition is impaired when visual reinforcement signals must first access cortex](http://www.sciencedirect.com/science/article/pii/S0166432813000429).
+Behavioural Brain Research, 243, 267--272.
+doi:10.1016/j.bbr.2013.01.023.
+
+## 2012
+
+-   Stafford, T., Thirkettle, M., Walton, T., Vautrelle, N., Hetherington, L., Port, M., Gurney, K.N., Redgrave, P.
+(2012), [A novel task for the investigation of action acquisition](http://www.plosone.org/article/info%3Adoi%2F10.1371%2Fjournal.pone.0037749), PLoS One, 7(6), e37749.
+
+-   Stafford, T.
+and Grimes, A.
+(2012).
+[Memory enhances the mere exposure effect](https://drive.google.com/file/d/1XuHvFVk3rbWHmuEHclPxFGSXSi8_Rp88/view?usp=sharing).
+(PDF, 626KB) Psychology & Marketing, 29, 12, 995--1003.
+
+-   Stafford, T., and Bell, V.
+(2012).
+[Brain network: social media and the cognitive scientist](https://drive.google.com/file/d/1ouB70muf-9-XN_7RbeN86QQIU1tEn8lZ/view?usp=sharing).
+(PDF, 108KB) Trends in Cognitive Sciences, 16(10), 489--490.
+doi:10.1016/j.tics.2012.08.001.
+
+## 2011
+
+-   Stafford, T., & Gurney, K.
+N.
+(2011).
+[Additive factors do not imply discrete processing stages: a worked example using models of the Stroop Task](http://www.frontiersin.org/Cognitive_Science/10.3389/fpsyg.2011.00287/abstract).
+Frontiers in Psychology, 2.
+doi:10.3389/fpsyg.2011.00287.
+
+-   Stafford, T., Ingram, L.
+and Gurney, K.N.
+(2011), [Pieron's Law holds during Stroop conflict: insights into the architecture of decision making](https://drive.google.com/file/d/19v6Bi6x01YBs5InJj8ALNNfhUP1ZrV6H/view?usp=sharing).
+(PDF, 374KB)  Cognitive Science 35, 1553--1566.
+
+-   Yates, D.J.
+and Stafford, T.
+(2011), [Insights into the function and mechanism of saccadic decision making from targets scaled by an estimate of the cortical magnification factor](http://www.abrg.group.shef.ac.uk/!DATA/attachment/0102.Yates2011a.pdf), Cognitive Computation, 3, 89--93.
+
+## Earlier key publications
+
+-   Stafford, T.
+(2010).
+[How do we use computational models of cognitive processes?](https://drive.google.com/file/d/1U3JZPaUb_J-L-tj9t8CpevsvUTAcOyvr/view?usp=sharing) (PDF, 118KB) In Connectionist Models Of Neurocognition And Emergent Behaviour: From Theory to Applications.
+Proceedings of the 12th Neural Computation and Psychology Workshop, Birkbeck, University of London, 8-10 April 2010.
+World Scientific (pp.
+326--342).
+
+-   Stafford, T.
+(2009), [What use are computational models of cognitive processes?](https://drive.google.com/file/d/1KTWXcmsH9TWwVVagAfysf0ch-IQjzIDW/view?usp=sharing) (PDF, 56KB) In Mayor, J., Ruh, N.,  Plunkett, K.
+Connectionist Models of Behaviour and Cognition II: Proceedings of the 11th Neural Computation and Psychology Workshop.
+World Scientific.
+
+-   Eiser, J.
+R., Stafford, T., Henneberry, J., and Catney, P.
+(2009).
+"Trust me, I'm a Scientist (Not a Developer)": [Perceived expertise and motives as predictors of trust in assessment of risk from contaminated land](https://drive.google.com/file/d/1mBtjfzW89lcLCWogK9ZYhIm3EJNFqCJq/view?usp=sharing).
+(PDF, 260KB)  Risk Analysis, 29(2), 288--297.
+
+    -   see also [Why don't we trust the experts? (2016)](https://tomstafford.sites.sheffield.ac.uk/news/why-dont-we-trust-the-experts)
+
+-   Stafford, T.
+and Gurney, K.N.
+(2007), [Biologically constrained action selection improves cognitive control in a model of the Stroop task](http://www.abrg.group.shef.ac.uk/!DATA/attachment/0046.stafford07.pdf), (External PDF) Philosophical Transactions of the Royal Society B: Biological Sciences, 362 (1485), 1671--1684.
+
+-   Stafford, T.
+and Wilson, S.
+P.
+(2007), [Self-organisation can generate the discontinuities in the somatosensory map](https://drive.google.com/file/d/1IblZNhCxsEbgnL4K5x25qahwsXT5so4G/view?usp=sharing).
+(PDF, 347KB)  Neurocomputing, 70(10-12), 1932--1937.
+
+-   Stafford, T.
+and Gurney, K.
+N.
+(2004), [The role of response mechanisms in determining reaction time performance: Pieron's Law revisited](https://drive.google.com/file/d/1173WABpGb9jbDOwU-i99X9zrU5szzlmL/view?usp=sharing).
+(PDF, 231KB)  Psychonomic Bulletin & Review, 11, 975--987.
+
+-   Eiser, J.
+R., Fazio, R.
+H., Stafford, T.
+and Prescott, T.
+J.
+(2003), [Connectionist simulation of attitude learning: Asymmetries in the acquisition of positive and negative evaluations](https://drive.google.com/file/d/1bULXLeeUMv3wgq7g47JgLAZYfD_0ailg/view?usp=sharing).
+(PDF, 505KB)  Personality and Social Psychology Bulletin, 29, 1221--1235.

### 2024-05-12 research.qmd
update

@@
 
-* Data Intensive Methods – robust, scalable, reproducible experiments and analysis which are transparent, sharable and work with 400,000 data points as well as for 40.
+* Data Intensive Methods – robust, scalable, reproducible experiments and analysis; methods which are transparent, shareable and work with 400,000 data points as well as for 40.
 
-* Interdisciplinarity – collaborating across all scholarly fields.
+* Interdisciplinarity – pathfinding, cross-fertilising and collaborating across scholarly fields.
 

### 2024-05-12 updatepages.sh

@@ -1,0 +1,5 @@
+#!/bin/bash
+
+git add -A
+git commit -m "update"
+git push origin master

### 2024-05-12 updatepages.sh
update

@@ -2,4 +2,4 @@
 
 git add -A
 git commit -m "update"
-git push origin master
+git push origin main

### 2024-05-12 publications.qmd
update

@@
 (PDF, 505KB)  Personality and Social Psychology Bulletin, 29, 1221--1235.
+
+# Conference papers and posters
+
+-   **Ambient rubbish: examining the attitudinal impact of incidental exposure to brand litter.** Grimes A, Stafford T and Roper S (2016), Academy of Marketing's 11th Global Brand Conference, Bradford University, UK
+
+-   [**Linking total movement history to action learning**](http://www.google.com/url?q=http%3A%2F%2Ffigshare.com%2Farticles%2FLinking_total_movement_history_to_action_learning%2F892378&sa=D&sntz=1&usg=AOvVaw3ExoQVhh4BcI8upQL-gmdc).
+Stafford and Thirkettle.
+Poster presented at Reinforcement Learning and Decision Making 2013, 24--26 October, Princeton, USA
+
+-   [**Testing theories of skill learning using a very large sample of online game players**](http://www.google.com/url?q=http%3A%2F%2Fmindmodeling.org%2Fcogsci2013%2F&sa=D&sntz=1&usg=AOvVaw25DG89Sfh2NZ8l9IK1qroA).
+Stafford & Dewar.
+Talk at the 35th Annual Meeting of the Cognitive Science Society, Berlin, Germany, 31 July 31 --3 August 2013
+
+-   **The effect of acquisition of an internal forward model on an exploration task**.
+M.
+Dagioglou, J.
+M.Bugella, T.
+Walton, T.
+Stafford, P.
+Redgrave, R.C.
+Miall.
+Poster presented at the 22nd Annual Meeting of the Society for the Neural Control of Movement, 23--29 April 2012, Venice, Italy
+
+-   [**Typing errors lead to increase in power and synchronization of theta oscillations**](https://drive.google.com/file/d/1Wu2oCkV5wyFZd_RjB33leGZI4R7drPMg/view?usp=sharing).
+(PNG, 923KB) Cigir Kalfaoglu, Tom Stafford and Elizabeth Milne.
+Poster presentation (by Kalfaoglu) in the British Association of Cognitive Neuroscience in Newcastle, UK on Wednesday the 11 April, 2012.
+
+-   **Instruction to relax enhances visual search performance by altering eye movements.** David Yates and Tom Stafford.
+Oral Presentation (by Yates) at 34th European Conference on Visual Perception which will be held in Toulouse, France from Sunday 28th August to Thursday 1st September, 2011.
+
+-   [**Visual search performance can be enhanced by instructions that alter eye movements**](https://drive.google.com/file/d/1dT4pXbJT-C1sBv5ORKyH623_ip-oqygg/view?usp=sharing).(PDF, 962KB)  David Yates and Tom Stafford.
+Poster Presentation (by Yates) at 16th European Conference on Eye Movements which will be held in Marseille, France from 21 --25 August 2011.
+
+-   **Learning the long way round: action learning based on visual signals unavailable to the superior colliculus is impaired.** Martin Thirkettle, Tom Walton, Kevin Gurney, Peter Redgrave and Tom Stafford.
+Oral presentation (by Thirkettle) at 34th European Conference on Visual Perception which will be held in Toulouse, France from Sunday 28th August to Thursday 1st September 2011.
+
+-   **What mistakes reveal about skilled performance: a study of touch-typing**.
+Cigir Kalfaoglu, Tom Stafford and Elizabeth Milne.
+Poster presentation (by Kalfaoglu) in the Experimental Psychologists Society Meeting in Oxford, UK from Wednesday the 13th to Friday the 15th of April, 2011.
+
+-   [**Integrating** ](https://drive.google.com/file/d/1gakIKmUFR3HqYLjn2FnVGKkHJVcbYzzA/view?usp=sharing)[**a**](https://drive.google.com/file/d/1gakIKmUFR3HqYLjn2FnVGKkHJVcbYzzA/view?usp=sharing)[**ugmented** ](https://drive.google.com/file/d/1gakIKmUFR3HqYLjn2FnVGKkHJVcbYzzA/view?usp=sharing)[**s**](https://drive.google.com/file/d/1gakIKmUFR3HqYLjn2FnVGKkHJVcbYzzA/view?usp=sharing)[**enses into active perception: a framework**](https://drive.google.com/file/d/1gakIKmUFR3HqYLjn2FnVGKkHJVcbYzzA/view?usp=sharing)**.**  Stafford, T., Javaid, M, Mitchinson, B., Galloway, A.M.J., Prescott, T.J.
+(2011).
+Poster presented at Royal Society meeting on Active Touch Sensing at the Kavli Royal Society International Centre, 31 January -- 02 February, 2011
+
+-   **Tracking the learning of actions:** **a****n evaluation of the frontal P3a component**.
+J.G.
+Bednark, E.A.
+Franz, T.
+Stafford, P.
+Redgrave, J.N.J.
+Reynolds.
+Society for Neuroscience Annual Meeting, 17-21 October 2009, Chicago.
+
+-   [**Saccadic latency versus eccentricity for targets scaled by an estimate of the cortical magnification factor**](https://drive.google.com/file/d/1wipQkEDOefWmKfhq7_jIM-_ZRa49DRUt/view?usp=sharing).
+(PNG, 1.8MB)  Yates, D.J.; Stafford, T.
+15th European Conference on Eye Movements, Southampton, 23--27 August, 2009.
+
+-   [**The** ](https://drive.google.com/file/d/1mYVVhmBOA2PhNn4fJcaAsRlClDRy1lhj/view?usp=sharing)[**n**](https://drive.google.com/file/d/1mYVVhmBOA2PhNn4fJcaAsRlClDRy1lhj/view?usp=sharing)[**onconscious mere** ](https://drive.google.com/file/d/1mYVVhmBOA2PhNn4fJcaAsRlClDRy1lhj/view?usp=sharing)[**e**](https://drive.google.com/file/d/1mYVVhmBOA2PhNn4fJcaAsRlClDRy1lhj/view?usp=sharing)[**xposure effect with brand** ](https://drive.google.com/file/d/1mYVVhmBOA2PhNn4fJcaAsRlClDRy1lhj/view?usp=sharing)[**l**](https://drive.google.com/file/d/1mYVVhmBOA2PhNn4fJcaAsRlClDRy1lhj/view?usp=sharing)[**ogos: real but** ](https://drive.google.com/file/d/1mYVVhmBOA2PhNn4fJcaAsRlClDRy1lhj/view?usp=sharing)[**e**](https://drive.google.com/file/d/1mYVVhmBOA2PhNn4fJcaAsRlClDRy1lhj/view?usp=sharing)[**lusive**](https://drive.google.com/file/d/1mYVVhmBOA2PhNn4fJcaAsRlClDRy1lhj/view?usp=sharing).
+(PDF, 2.6MB) Stafford, T; Grimes, A., Perkins, C.
+The 21st Annual Convention of the Association for Psychological Science, 22-24 May 2009, San Francisco, CA.
+
+-   **What use are computational models of cognitive processes?**  Stafford, T. 11th Neural Computation and Psychology Workshop, Oxford, 16-18 July, 2008.
+
+-   [**Self-organisation explains discontinuities in the somatosensory map**](https://drive.google.com/file/d/1LioNtU36rUpLpIXWa6P0ik02h6droGpw/view?usp=sharing).
+(PDF, 1MB)  Stafford, T.
+and Wilson, S.P.
+Fifteenth Annual Computational Neuroscience Meeting CNS.
+2006, 16--20 July 2006.
+
+-   [**The neural circuitry necessary for decision making by evidence accumulation**](https://drive.google.com/file/d/1MSAuCBqVtHuqE-kJdtEjLfqDLgud5AAM/view?usp=sharing).
+Tom Stafford, Mark D.
+Humphries, Jonathan M.
+Chambers.
+Poster presented at the Computational Cognitive Neuroscience conference in Washington, DC, 11 October 2005.
+
+-   **The basal ganglia as the selection mechanism in a cognitive task**.
+Stafford, T.
+and Gurney, K.
+(2005).
+In J.
+J.
+Bryson, T.
+J.
+Prescott and A.
+Seth (Eds.) Modelling natural action selection (pp.
+77-83).
+AISB Press.
+
+-   [**The basal ganglia as the selection mechanism in a cognitive task**](https://drive.google.com/file/d/11mUBgognVLh-1cS8XIoXYQLwWRwsCv5t/view?usp=sharing).
+(PNG, 1.4MB) Stafford, T.
+and Gurney, K.
+(2005).
+Poster presented at Modelling Natural Action Selection workshop in Edinburgh, July 2005.
+
+-   **Learning under uncertainty: Manipulating and simulating the role of expectations.**  Eiser, Richard, Stafford, Tom, Shook, Natalie and Fazio, Russell.
+Paper presented at the 14th General Meeting of the European Association fo Experimental Social Psychology, Wurzburg, 19-23 July 2005.
+
+-   **Acid tar lagoons: risks and sustainable remediation in an urban context.**  Catney, P., Lawson, N., Palaseanu-Lovejoy, M., Shaw, S., Smith, C., Stafford, T., Talbot, S., Hao, X.
+(2005, 1st of March 2005).
+Paper presented at the SUBR:IM conference, Natural History Museum, London.
+
+-   **The Basal Ganglia provides an appropriate model for response selection in the Stroop task.**  Stafford, T.
+and Gurney, K.N.
+Poster presented at the Annual Conference of the BPS Cognitive Psychology Section at Essex, September 6th-8th, 2000.
+
+[Back to top](https://tomstafford.sites.sheffield.ac.uk/outputs/conference-papers)
+
+# Other publications
+
+-   Yates, D., and Stafford, T.
+(2017, October 1).
+[**'Cognitive strategy' in visual search: how it works and when it generalises**](https://www.google.com/url?q=https%3A%2F%2Fpsyarxiv.com%2F5dup8%2F&sa=D&sntz=1&usg=AOvVaw11ViqM96Lr3hnLbFR4Ppb3).
+https://doi.org/10.31234/osf.io/5dup8.
+
+-   Stafford, T.
+(2009).
+[**Lessons from the campaign against Elsevier: "We won, but how did we win?"**](https://drive.google.com/file/d/1TK60znv37xBB0r-5LJhxY0IUeGKCHT6e/view?usp=sharing)[.](https://drive.google.com/file/d/1TK60znv37xBB0r-5LJhxY0IUeGKCHT6e/view?usp=sharing) (PDF, 168KB) *ACME: An International E-Journal for Critical Geographies*, 8(3), 494--504.
+
+-   Stafford, T.
+(2008).
+[**Teaching questions rather than answers: inquiry-based learning on an MSc course**](https://drive.google.com/file/d/1ygxtidGmBfM-i0DJwBcqRf_GNL6yH32M/view?usp=sharing)**.** (PDF, 58KB) *HEA Psychology Network Newsletter*, Issue 46, January 2008.
+Available at: [http://www.psychology.heacademy.ac.uk/html/newsletter.asp](http://www.google.com/url?q=http%3A%2F%2Fwww.psychology.heacademy.ac.uk%2Fhtml%2Fnewsletter.asp&sa=D&sntz=1&usg=AOvVaw3ucom4XsicuL9yKSHQnXa6)
+
+-   Stafford, T.
+and Martin, C.J.
+(2007).
+[**How to do a neuroscience lab class with 120 students**](https://drive.google.com/file/d/1N88oBScVw4zTZIx9xneIjCnHL0xRY0Ua/view?usp=sharing).
+(PDF, 62KB) *HEA Psychology Network Newsletter*, Issue 45, November 2007.
+Available at: [http://www.psychology.heacademy.ac.uk/html/newsletter.asp](http://www.google.com/url?q=http%3A%2F%2Fwww.psychology.heacademy.ac.uk%2Fhtml%2Fnewsletter.asp&sa=D&sntz=1&usg=AOvVaw3ucom4XsicuL9yKSHQnXa6)
+
+-   Stafford, T.
+(2007).
+[Isn't it all just obvious?](http://www.google.com/url?q=http%3A%2F%2Fwww.bps.org.uk%2Fpublications%2Fthepsychologist%2Fsearch-the-psychologist-online.cfm%3Ffuseaction%3Dinc_psychologistdet%26ID%3D1145%26Publication_ID%3D1&sa=D&sntz=1&usg=AOvVaw2x3vJi_32e8EIdPmGIQeRW) *The Psychologist*, 20, 2, 94--95.
+
+-   **The neural circuitry necessary for decision making by evidence accumulation**\
+    Mark D. Humphries, Tom Stafford, Jonathan M. Chambers and Kevin N. Gurney\
+    ABRG Technical Report number 5, May 2006. Department of Psychology, University of Sheffield, UK
+
+-   Stafford, T.
+and Webb, M.
+(2006) **'What Is a Wiki (and How to Use One for Your Projects)'**.
+O'Reilly Network, 7 July 2006.
+Available at [http://www.oreillynet.com/pub/a/network/2006/07/07/what-is-a-wiki.html](http://www.google.com/url?q=http%3A%2F%2Fwww.oreillynet.com%2Fpub%2Fa%2Fnetwork%2F2006%2F07%2F07%2Fwhat-is-a-wiki.html&sa=D&sntz=1&usg=AOvVaw3Ra8vUj8t-t_0eMjG381sr)
+
+-   Stafford, T.
+and Gurney, K.
+(2005).
+**The basal ganglia as the selection mechanism in a cognitive task**.
+In *J.
+J.
+Bryson, T.
+J.
+Prescott and A.
+Seth (Eds.) Modeling Natural Action Selection* (pp.
+77--83).
+AISB Press.
+
+-   Webb, M.
+and Stafford, T.(2004) **'Paying Attention (or Not) to the Flickr Daily Zeitgeist'.** O'Reilly Network, 6 December 2004.
+Available at [http://www.oreillynet.com/pub/a/network/2004/12/06/mndhcks_1.html](http://www.google.com/url?q=http%3A%2F%2Fwww.oreillynet.com%2Fpub%2Fa%2Fnetwork%2F2004%2F12%2F06%2Fmndhcks_1.html&sa=D&sntz=1&usg=AOvVaw0lsrLHn5iUCFWTFi8RMust)
+
+-   Stafford, T.
+(2003).
+[**Integrating psychological and neuroscientific constraints in models of Stroop processing and action selection**](https://drive.google.com/file/d/1bPGdOXC6453IkNEJOhvwigpintO_c9eG/view?usp=sharing)**.** (PDF, 1MB) PhD Thesis, University of Sheffield.\
+    [Abstract and contents only](https://drive.google.com/file/d/1CCKBfx3MqMcat2gUKaxL4At58-l_h3_S/view?usp=sharing) (PDF, 169KB)
+
+-   Stafford, T.
+(2003).
+[**Psychology in the coffee shop**](http://www.google.com/url?q=http%3A%2F%2Fwww.idiolect.org.uk%2Fdocs%2Fjan04%2Fcoffee.pdf&sa=D&sntz=1&usg=AOvVaw31tI9HJmF3R-nIRUVcsaX2)**.** *The Psychologist*, 16(7), 358--359.
+
+-   Stafford, T.
+(2000).
+[**Stroop interference: methodological problems and contrary data**](http://www.google.com/url?q=http%3A%2F%2Fpsycprints.ecs.soton.ac.uk%2Farchive%2F00000110%2F&sa=D&sntz=1&usg=AOvVaw25AMB1sxZcqBDAARA21Zu1)**,** *Psycoloquy*, 11, #110.

### 2024-05-12 done.qmd
update

@@
 
-Recording things i've done which don't go under [Publications](https://tomstafford.sites.sheffield.ac.uk/outputs/scholarly-publications), 
-[Talks](https://tomstafford.sites.sheffield.ac.uk/outputs/talks) or Newsletter: <https://tomstafford.substack.com/>. Most of these posted to [Mastodon](https://mastodon.online/@tomstafford) too.
+Recording things i've done which don't go under  [Papers](papers.html), 
+[Talks](https://tomstafford.sites.sheffield.ac.uk/outputs/talks) or Newsletter: <https://tomstafford.substack.com/>. For current preoccupations, see [here](news.html).
 
@@
 
+# 2021
+
+2021: [The Experiment Design Checklist](https://tomstafford.github.io/psy-checklist/)
+
 # 2020
@@
 Led development and adoption of the [University of Sheffield statement on Open Research](https://www.sheffield.ac.uk/openresearch/university-statement-open-research)
+
+2020: [The Letters of Pope Gregory VII - pilot project](https://figshare.com/articles/dataset/The_Letters_of_Pope_Gregory_VII_-_pilot_project/12781049) (with Charles West and George Litchfield)
+
+# 2019
+
+[Animated Itinerary of King John,](https://sites.google.com/d/1nQb4g6jqk7M0gwaD4Bvw7QKtBg0nkQRV/p/120fMmXEkjhEwEnsgf8fx5v1XKQrf3MdZ/edit)  [Mapping The Itinerary of King Edward I](https://figshare.com/articles/dataset/Mapping_The_Itinerary_of_King_Edward_I/8948699), [Mapping Papal Letters](https://tomstafford.github.io/PapalCorrespondence/) (with Charles West)
+
+# 2018
+
+2018: [@ChoiceEngine - an interactive essay about the psychology of free will](https://github.com/tomstafford/choice-engine-text)
 
@@
 2012-09 I wrote some of the code in LongArm, [a robot which draws labrynthine patterns](https://www.youtube.com/watch?v=lSuvSsDrEAw), by Matthias Jones
+
+2012: [The Cognitive Science Safari](https://sites.google.com/d/1nQb4g6jqk7M0gwaD4Bvw7QKtBg0nkQRV/p/1Q0M0b1kRUveC9w0Li7Je0A1f1E8PzzYB/edit) was a street-tour of classic social psychology experiments, in Berlin as part of the BMW Guggenheim Lab.
+
+2011: [The Tea Taste Test](https://sites.google.com/d/1nQb4g6jqk7M0gwaD4Bvw7QKtBg0nkQRV/p/1O7uZnZPiKBL7C6JiR0DLSgGCqVw86uYX/edit) -- explaining why statistics are important to psychology, using a controversy of how to make a cup of tea.

### 2024-05-12 papers.qmd
update

--- 2024-05-12 publications.qmd
@@
 ---
-title: "Publications"
+title: "Papers"
 ---
@@
 
-[Back to top](https://tomstafford.sites.sheffield.ac.uk/outputs/conference-papers)
-
 # Other publications
@@
 [**Stroop interference: methodological problems and contrary data**](http://www.google.com/url?q=http%3A%2F%2Fpsycprints.ecs.soton.ac.uk%2Farchive%2F00000110%2F&sa=D&sntz=1&usg=AOvVaw25AMB1sxZcqBDAARA21Zu1)**,** *Psycoloquy*, 11, #110.
+
+# Books and chapters
+
+-   Stafford, T.
+(2011).
+[How do we use computational models of cognitive processes?](https://drive.google.com/file/d/1aXmvysI3PVNXGEdsMpAXunptvwUuez6h/view?usp=sharing) (PDF, 289KB) In E.
+Davelaar (eds) Connectionist Models Of Neurocognition And Emergent Behavior: Proceedings of the 12th Neural Computation and Psychology Workshop, 326--342.
+World Scientific.
+
+-   Stafford, T. (2010).[ The Narrative Escape](http://mindhacks.com/2010/10/21/the-narrative-escape/), 40kbooks, Milan.
+
+-   Moore, G & Stafford, T. (2010). [The Rough Guide Book of Brain Training](http://idiolect.org.uk/braintrain/).
+
+-   Stafford, T. (2009) Hacking our tools for thought in Nold, C. (ed) Emotional Cartography: Technologies of the Self, 88-96. [emotionalcartography.net](http://emotionalcartography.net/)
+
+-   Stafford, T.
+(2009).
+[What use are computational models of cognitive processes?](https://drive.google.com/file/d/19ZS4cAaAIlHcC0kTqOtJHAfox-4GRQlB/view?usp=sharing) (PDF, 132KB) In J.
+Mayor, N.
+Ruh and K.
+Plunkett (eds.) Connectionist Models of Behavior and Cognition II: Proceedings of the 11th Neural Computation and Psychology Workshop, 265--274.
+World Scientific.
+
+-   Catney, P., Eiser, J.R., Henneberry, J.
+and Stafford, T.
+(2007) Democracy, Trust and Risk Related to Contaminated Sites in the UK, in: T.
+Dixon, M.
+Raco, P.
+Catney & D.N.
+Lerner (Eds.) Sustainable Brownfield Regeneration: Liveable Places from Problem Spaces.
+Oxford: Blackwells.
+
+-   Stafford, T.
+and Gurney, K.N.
+(2006).
+Computational Models of Cognition.
+In An Introduction to Cognitive Psychology: Processes and Disorders.
+Second Edition.
+Ed.
+David Groome.
+Hove, UK: Psychology Press.
+
+Stafford, T. and Webb, M. (2004). [Mind Hacks: Tips and Tricks for using your brain](http://www.mindhacks.com/). Sebastapol, CA: O'Reilly.

### 2024-05-12 writing.qmd
update

---
title: "writing"
---

For non-specialist audiences

# Mindhacks

![](images/mindhacks.jpeg){width="25%"}

[The DIY book for cognitive science](http://mindhacks.com/book). 100 things you can try at home which will teach you how the mind works.

"The authors have compiled a fascinating "collection of probes into the moment-by-moment works of the brain" ... Mind Hacks allows you to test the theories of neuroscience on your own grey matter. If you've always wanted to get closer to your cerebellum but never plucked up the courage to take that DIY neurosurgery course, this is the book for you." --- The Guardian

"A wonderful annotated bibliography, with a light touch and hackish humour that inspires further reading." --- New Scientist

# For argument's sake: evidence that reason can change minds

![](images/fas_small.jpg){width="25%"}

Are we irrational creatures, swayed by emotion and entrenched biases? Modern psychology and neuroscience are often reported as showing that we can't overcome our prejudices and selfish motivations. In this long essay (short ebook) I challenge this view. Re-analysing classic experiments on persuasion, as well as summarising more recent research into how arguments change minds, I show that the evidence is that persuasion by reason alone can be a powerful force.

Buy the book: [Amazon](http://www.amazon.com/dp/B010O1Z018), [books2read](https://books2read.com/u/boXz59) (indie)

## mindhacks.com

I helped run the [mindhacks.com](http://mindhacks.com/) blog. It was active from roughly 2004 to 2020, and dedicated to psychology and neuroscience news and views.

"Mindhacks.com...surely the best popular psychology content anywhere, not just on the net" [Ben Goldacre](http://www.badscience.net/2009/02/the-evidence-aric-sigman-ignored/)

"Riveting" [Scientific American](http://mindhacks.com/2005/10/05/scientific-american-web-awards/)

## BBC Future column

I wrote a [regular column](http://www.bbc.com/future/columns/neurohacks) for the BBC, exploring the psychology behind some everyday phenomena.

## The Conversation

My column at [The Conversation](https://theconversation.com/columns/tom-stafford-91781) consisted of critical reviews of neuroscience and psychology stories in the news.

# Other writing

I also wrote the essays which intersperse the [Rough Guide Book of Brain Training](http://www.amazon.co.uk/Rough-Guide-Brain-Training-Guides/dp/1848365187) (2010). You can read about this [Rough Guide on mindhacks.com](http://mindhacks.com/2010/01/14/the-rough-guide-to-brain-training-moore-stafford-2010/), and there is [one of the cut chapters](http://mindhacks.com/2010/01/28/better-thinking-through-chemistry/).

I have written an ebook on psychology, morality and the nature of stories: [The Narrative Escape](http://idiolect.org.uk/notes/?p=1201) (2010). I have published two free ebooks [Explore Your Blind Spot](http://www.smashwords.com/books/view/110777) and [Control Your Dreams](http://www.smashwords.com/books/view/118271) (both December 2011).

I have written magazine articles, including an article on confabulation and creativity for Prospect magazine: [Tall Stories](http://idiolect.org.uk/notes/?p=894); this on [creativity and games](http://mindhacks.com/2011/10/12/games-of-invention/) for Rattle; and one on small world theory and social networks for Now Then magazine (available here). I come top of a google search for "psychology + coffee" because of this article [Psychology in the Coffee Shop](http://www.idiolect.org.uk/docs/jan04/coffee.pdf), published in the Psychologist magazine.

I wrote a chapter for Christian Nold's [Emotional Cartography](http://emotionalcartography.net/), and I gave a talk at the book launch which started '[There is a saying that those who want to enjoy laws and sausages should not find out how they are made. I think the same is true about facts](http://idiolect.org.uk/notes/?p=796)'.

### 2024-05-12 talks.qmd
update

---
title: "talks"
---

# Coming up

# Past talks

## 2024

-   17th April 2024, [Improving The Research Funding Lottery](https://docs.google.com/presentation/d/1W1RmcaYGKjsRHFLZ-zC0S0PN_UWV_oCto78z62I1bc8/edit?usp=sharing) at School of Architecture, University of Sheffield.

    -   Researchers spend hours and hours writing funding proposals and in the end bad ideas get funded and good ideas get missed. Everyone has the suspicion that the funding process is biased against people in the wrong fields, from the wrong institutions or with the wrong backgrounds. Can research funding be improved, and what does the evidence say? Tom will talk about work from the Research on Research Institute, and about projects on innovations in how research funding is awarded.[  https://researchonresearch.org/](https://researchonresearch.org/)

-   10th April 2024, [Research on Research](https://docs.google.com/presentation/d/1htwqAwrvKtLONwIP1szg7QNMDMQoEJBvuGRTmfrqX20/edit?usp=sharing) at School of Psychology Research Day, University of Sheffield.

-   9th February 2024, [Adventures in the Multiverse](https://docs.google.com/presentation/d/1ZIdTon4KVqZrwkoQMR_Seu4plM5oTQf3hzgk6lZqveY/edit?usp=sharing) at [TARG](https://www.bristol.ac.uk/psychology/research/brain/targ/), University of Bristol

    -   Complex data and complex methods mean multiple statistical analyses are potentially legitimate. Multiverse analysis offers a tool to interrogate the stability of results under different analysis choices. After introducing the general history and rationale of multiverse analysis, I will talk about two multiverse projects I have been involved in, both in my research area of bias and decision making, and what we have learned from them

    -   Slides: "[Adventures in the Multiverse](https://docs.google.com/presentation/d/1ZIdTon4KVqZrwkoQMR_Seu4plM5oTQf3hzgk6lZqveY/edit?usp=sharing)" ([PDF](https://drive.google.com/file/d/1il0clUWLZCSlj4s8L_5ftZaSAABH4e0o/view?usp=sharing))

-   19th January 2024 6pm UK time, Google IQ Research Talk: [When people are wrong on the internet - reasons to be optimistic](https://docs.google.com/presentation/d/1snNtURuMiiXBkrt-kg2cF3E_g0pfwn9as3e_Tz3p30I/edit?usp=sharing) (host Mevan Babakar)

    -   Human reasoning in the digital age has a terrible reputation. People are often portrayed as hopelessly biased, polarised and resistant to good sense, while - strangely - also being easily manipulated by malevolent forces and bizarre fads. From the trenches of psychological science, I bring you good news! I will discuss two strands of work. In the first, we show that even minimal deliberation allows online groups to select away from intuitive but wrong answers (and that there are prospects for language-model based dialogue agents to support good group reasoning). More at [delibot.xyz](https://www.delibot.xyz/). In the second strand of research we show that, across polarising topics, UK partisans are surprisingly good at representing the views of the ideological opponents, and that the better people are at this the more likely they are to view people they disagree with as moral, informed and rational. More in [Brand, Brady & Stafford (2023)](https://osf.io/preprints/psyarxiv/2e9wn).

    -   [Slides](https://docs.google.com/presentation/d/1snNtURuMiiXBkrt-kg2cF3E_g0pfwn9as3e_Tz3p30I/edit?usp=sharing), [PDF](https://drive.google.com/file/d/1wDGAZkwTgy0x0JH-kB_LamFBSdyzj75c/view?usp=drive_link)

## 2023

-   7.30pm 18th of September 2023 for the [Consciousness Perspectives Forum](https://scientificandmedical.net/consciousness-perspectives-forum/) of the [Scientific and Medical Network](https://scientificandmedical.net/) [online, £]

    -   "[Free thought in a world of influences](https://docs.google.com/presentation/d/1m2haWkkQJ1Gul6iuPZ_0wryob4ZfrvplIxVTxn-pl0I/edit?usp=sharing)" ([PDF](https://drive.google.com/file/d/1XGA3qfhxREMn5iXmEfikMBiKmWcjSk_R/view?usp=sharing))

-   2pm, 6th Sept 2023:. [The Possibility Studies Network](https://www.possibilitystudies.net/) [online, free]

    -   "[Human reason and the expanding circle](https://docs.google.com/presentation/d/1blnmTTW8Ew_6CDK0mQ30BHuZbUjVPvx3uomGxRkACdg/edit?usp=sharing)" ([PDF](https://drive.google.com/file/d/1IJTVHA_XhdTxdJEXh9jdgk1MeHAPdt-D/view?usp=drive_link))

-   30 June 2023 [RoRI's Experimental Research Funder's Forum](https://docs.google.com/presentation/d/1jfJ5KFeJzCQSlx75-0tXyv0CAKGzZvQ3hulHIdRjl9A/edit?usp=sharing) at workshop on [The Funding of Science and Innovation](https://www.som.polimi.it/the-funding-of-science-and-innovation/), Milan, 29-30 June 2023 ([PDF](https://drive.google.com/file/d/1AGAeUKPJSt6tNgWZYvSIW02l_g1tJkII/view?usp=drive_link))

-   6th June 2023 [Research on Research: Introducing Metascience](https://docs.google.com/presentation/d/1_3nOAEb_o_6Ykk3_IUQRfLDVz_QHiDck7W8B7FxE4Vo/edit?usp=sharing) at the Scharr Research Away Day, University of Sheffield.

-   24th May 2023 "[The UKRN's Open Research programme. WP1: Training](https://docs.google.com/presentation/d/13SISHdIdITEjPbIyI-RxSfp0w_pca_0RkY8SqWXZI0M/edit?usp=sharing)" at [Keele Open Research week](https://www.keele.ac.uk/openresearchweek/) conference

-   5th of May 2023 Keynote at [EACL2023](https://2023.eacl.org/program/main/), [Sixth Workshop on Fact Extraction and VERification](https://fever.ai/workshop.html):

    -   "[Faith in Reason: Prospects for fact checking in a world of bias](https://docs.google.com/presentation/d/1duYeukxv282OPQRI2-2OnoFnZiVCAHZ_C5696rNF0iA/edit?usp=sharing)" ([PDF](https://drive.google.com/file/d/1cCxjUNP9A_Gx5ZTGBZolqOLziWU8YCck/view?usp=share_link))

-   2nd March 2023 - "[Maximizing the potential of digital games for understanding skill acquisition](https://docs.google.com/presentation/d/1Fdp7plowlCYcr42dXfZP_-mJV9idwoDcgqegD7l9QgU/edit?usp=sharing)", Invited Speaker, Center for Educational Neuroscience, UCL

    -   [recording](https://www.youtube.com/watch?v=En1lBcGTpo0)

-   2nd Feb 2023 - talks and panel discussion [INTERFACE: Art/Technology/Collaboration](https://www.sitegallery.org/event/interface-art-technology-collaboration/)

    -   [slides](https://docs.google.com/presentation/d/1m_UgWRuEbzfgG5wZg7ufvi2_iP-wAp5w1quX31b2PNw/edit?usp=sharing)

    -   newsletter on this [Microarguments and macrodecisions](https://tomstafford.substack.com/p/microarguments-and-macrodecisions)

## 2022

-   9th December 2022 - [Wide Open?](https://docs.google.com/presentation/d/1uikndHgd6V6VJS3sGfbRDVjQOoGvL8Niil47jgjv2qU/edit?usp=sharing) Inaugural annual Open Research lecture, University of Sheffield.

    -   [Tickets](https://www.eventbrite.co.uk/e/university-of-sheffield-inaugural-annual-open-research-lecture-tickets-440984976937)

-   7th Dec 2022 -[ Faculty doctoral training on research professionalism & integrity ](https://docs.google.com/presentation/d/1fbkF-nd2jbOxg9akluIpwyEj6L0xaXqyiNGMT-htTSw/edit?usp=sharing)(DDP Module code: FCP611)

-   8th November 2022 - "[How arguments work: The Delibot Project](https://docs.google.com/presentation/d/1qQ9HSqnShq3cYOF-L9FrDqg_5GPSPXrlJZm7_FytBq0/edit?usp=sharing)", Department of Psychology research day

    -   See also [delibot.xyz](https://www.delibot.xyz/)

-   4 November 2022 - Invited Speaker, [School of Collective Intelligence](https://sci.um6p.ma/), Mohammed VI Polytechnic University, Morocco: "[How Arguments Work](https://docs.google.com/presentation/d/1SqZRKwwju2tK47tQrvLQsgBQjmfR4P0LiDjy2vpRH64/edit?usp=sharing)"

-   2 September 2022 - Plenary Lecture, How the research on Research Institute (RoRI) is aiming to improve how research is funded, practiced, communicated, and evaluated. Meeting of the [NeuroLeman Network and Doctoral Schools (NLN)](https://www.neuroleman.ch/) 2022, Les Diablerets, Switzerland

    -   -   [Google slides](https://docs.google.com/presentation/d/1KiAqZXl5LBzA6O0Fc2nEFzlNYPD46CORc3dbyZdnPx0/edit#slide=id.g132c935b892_0_114)

        -   [Presentation slides](https://drive.google.com/file/d/1S4TsFmREC5_7OH-ACKqg64XUJcImvKuk/view?usp=sharing) (PDF, 5.1MB)

-   7--9 September 2022 - Keynote, [BPS Cognitive Psychology Section Conference 2022](https://www.cogsec2022.com/), University of Sussex

    -   -   [Google slides](https://docs.google.com/presentation/d/11CesdSn8oUvyGwHhOvtvDGxowy-OMwhxRl6XKEdvFS4/edit?usp=sharing)

        -   [Presentation slides](https://drive.google.com/file/d/1HPAg4-nKHgR67lChLPPkgat52cAe_boS/view?usp=sharing) (PDF, 4.8MB)

-   20 April 2022 - Maximizing the potential of digital games for understanding skill acquisition. Part of Digital Creativity Speaker series @ University of York.

    -   -   [Google slides](https://docs.google.com/presentation/d/19Djw0nBYGR0Yjd9jEKdBlaE8nLh1xBkZHl96T3UC9tQ/edit?usp=sharing)

        -   [Presentation slides](https://drive.google.com/file/d/1DCefMe5cON3VH729gvsK9ss_AmB-KQhh/view?usp=sharing) (PDF, 3.2MB)

-   6 April 2022 - Research Improvement at TUOS

    -   -   [Google slides](https://docs.google.com/presentation/d/12BthkJitruyL_LY4cH7lvnMR2OGSQUPUbbPkRU6WG48/edit?usp=sharing) (requires University login to view)

These slides form the basis for events run in the:

-   -   -   Department of Urban Studies & Planning (2022-04-26)

        -   Department of Economics (2022-05-04)

        -   The Social Research Institutes (2022-05-13)

        -   School of Architecture (2022-05-19)

        -   School of Education (2022-05-25)

        -   School of Clinical Dentistry (2022-05-26), Centre for Care (2022-06-07)

        -   Department of Sociology and Social Care (2022-06-07)

        -   Department of Politics (2022-06-07)

        -   Department of Architecture (2022-06-29)

        -   Department of Landscape Architecture (2022-07-06) and others.

-   23 March and 14 April 2022 - Understanding the brain through the eyes\
    What we see and how we see can be used to help us understand how the brain works. Illusions are not just visual tricks, but illustrate the deep principles which our brains use to construct reality. In this talk, with the use of many examples, I will show how the study of illusions provides important lessons for psychologists trying to understand all aspects of mind, brain and behaviour

    -   -   [Google slides](https://docs.google.com/presentation/d/1F-AnQEURCFRWY1W99S75dY5mUkykBQZj_xhhSdidlGo/edit?usp=sharing)

        -   [Presentation](https://drive.google.com/file/d/1lH6tx_kE2zvolV3lQDShwyqMlw5HpUyw/view?usp=sharing) (PDF, 3.2MB)

-   23 Feb 2022 - Open Research at the DDRI Network meeting

    -   -   [Google slides](https://docs.google.com/presentation/d/16_sO5H1mvbEMVu12eyT4uARw9h1BRF3i8nyGbI0nCcs/edit?usp=sharing)

## 2021

-   7 December 2021 - Faculty doctoral training on research professionalism and integrity (DDP Module code: FCP6101)

    -   -   [Google slides](https://docs.google.com/presentation/d/1fbkF-nd2jbOxg9akluIpwyEj6L0xaXqyiNGMT-htTSw/edit?usp=sharing)

-   25 November 2021 - SuperVisionaries: Open Research for Supervisors

    -   -   [Google slides](https://docs.google.com/presentation/d/1cxZY-VV9n9Eq2JT7iGV4a7l2sJnQ_zpM-OC-AjaUVoI/edit?usp=sharing)

-   17 November 2021 - Open Research Conversations: "Open Source Licensing", with Bob Turner

    -   -   [Google slides](https://docs.google.com/presentation/d/1xtLJXckiCb7lW-syhtCTtkJsXTFDhpfe5gF8zkRoey8/edit?usp=sharing)

-   27 October 2021 - Into the Multiverse, slides to support a Sheffield MetaNet discussion

    -   -   [Google slides](https://docs.google.com/presentation/d/1_Hzae2fCDby02BIdsbPQpuq353R09d5pSrYKoQ0ohG8/edit?usp=sharing)

-   30 June 2021 - The rise of on-line political advertising: A 'moral panic'?, with Dr Kate Dommett, a [Top Talk from the APG](https://www.apg.org.uk/).

    -   -   [Google slides](https://docs.google.com/presentation/d/1nwwqbRB2-t7IjmpUBnH47jDPfeJ6t5e8Yhi4l8sJNNU/edit?usp=sharing)

        -   [Presentation](https://drive.google.com/file/d/1dBrQmCp1W0NVz-UaWeJ-blJSlcRtvpR5/view?usp=sharing) (PDF, 2MB)

-   16 June 2021 - Why you should use decision models with your response time and accuracy data at [Centre for Cognition and Neuroscience](https://research.hud.ac.uk/institutes-centres/ccn/), University of Huddersfield (and online).

    Decision modelling is increasingly accessible and yields highly practical benefits to experimental psychologists. This talk will explain why and how you should apply decision models to your data.

    Response time and accuracy are fundamental measures of behavioural science, but discerning participants' underlying abilities can be masked by speed-accuracy trade-offs (SATOs). SATOs are often inadequately addressed in experiment analyses which focus on a single variable or which involve a suboptimal analytic correction. Models of decision making, such as the drift diffusion model (DDM), provide a principled account of the decision making process, allowing the recovery of SATO-unconfounded decision parameters from observed behavioural variables.

    I will show, using simulations and worked examples from experimental data, how decision models allow potentially massive increases in statistical power at the same time as helping you avoid mistaken inferences due to variations in participants' SATOs strategies. Because the modelling community has focussed on differences between different decision models, this has disguised the fact that there is now a consensus around the core mechanisms which define the family of plausible decision models, as well as increasing agreement on tools for fitting behavioural data with these decision models.

    Stafford, T., Pirrone, A., Croucher, M., and Krystalli, A. (2020). Quantifying the benefits of using decision models with response time and accuracy data. Behavioral Research Methods, 52, 2142-2155 [doi.org/10.3758/s13428-020-01372-w\
    ](https://doi.org/10.3758/s13428-020-01372-w)See also:

    -   -   the [interactive data explorer](https://sheffield-university.shinyapps.io/decision_power/):

        -   [Pre-print](https://tomstafford.sites.sheffield.ac.uk/sub-sites/decision-power)

        -   [Google slides](https://docs.google.com/presentation/d/1mQaDtmFk-Cj86EkVblvo7aeg4sfShrShMFhkBmcpaAk/edit?usp=sharing)

        -   [Presentation](https://drive.google.com/file/d/1fBdFHrUXQ9_DxahhWAJxh-_xZyC2pnOg/view?usp=sharing) (PDF, 1.3MB)

-   14 June 2021 - A researcher's perspective on reproducibility, University of Sheffield Medical School Research Meeting

    -   -   [Google slides](https://docs.google.com/presentation/d/1cpTzLxorxUqcwY6T2BtkD1wL3wBihozL9HdGTbN3xNA/edit?usp=sharing)

        -   [Presentation](https://drive.google.com/file/d/1FZorVFfdujqkcQyjYUaTngcQykaTPawD/view?usp=sharing) (PDF, 1.2MB)

-   3 March 2021 - Revolutions in Reproducibility, Sheffield Metascience Network Launch

    -   -   [Google slides](https://docs.google.com/presentation/d/1RMwO6jg3Y1V6L_UGIdBWhYGb1u9TDpjYDbAyCT3QwCQ/edit?usp=sharing)

        -   [Presentation](https://drive.google.com/file/d/1Jjbyuky0s3qRZbuGjTqMFndT5wiG8ZWK/view?usp=sharing) (PDF, 1.1MB)

-   18 Jan 2021 - Reproducibility in Practice - [Open Research Conversations](https://www.sheffield.ac.uk/library) at University of Sheffield. With Dr Anna Krystalli

-   [Google slides](https://docs.google.com/presentation/d/1qsv8IETDKxLwubWkWyD5mCDlWWfCHIRAqQpTe572fMk/edit?usp=sharing)

-   [Presentation](https://drive.google.com/file/d/1yMUs_XXQir7I8XQefWe10j2U6VdyNljj/view?usp=sharing) (PDF, 673KB)

-   [Talk recording](https://figshare.shef.ac.uk/articles/presentation/Open_Research_Conversation_Reproducibility_in_Practice/13516274)

## 2020

-   28 Jan 2020 - Bias and Blame - Department of Psychology, University of York.

    -   -   [Google slides](https://docs.google.com/presentation/d/1VddXVox1RZD5qZgAOazSDSGjHoBr2F-nFZSyFDI6ZmM/edit?usp=sharing)

        -   [Presentation](https://drive.google.com/file/d/1EWi2YwLIBlzywxELnyznL-forkLK2fpn/view?usp=sharing) (PDF, 2.3MB)

## 2019

-   12 Nov 2019 - Unconscious Bias - at [Ministry of Justice, Digital and Technology](https://mojdigital.blog.gov.uk/), Sheffield.

    -   -   [Google slides](https://docs.google.com/presentation/d/1GIqsGdtthkCG049OoJoqma_qXua-MnRyhQTrtWYvQ8s/edit?usp=sharing)

        -   [Presentation](https://drive.google.com/file/d/1YiXqUGHU656iAShcMery2yLyCMdTD3Ej/view?usp=sharing) (PDF, 2.2MB)

-   21 Oct 2019 - Analysing Big Data to Understand Learning - 15 minutes for SMI606, at the [Sheffield Methods Institute](https://www.sheffield.ac.uk/smi).

    -   -   [Google slides](https://docs.google.com/presentation/d/1ZI-DYc2ojDbT1BvgpSbIxe8fZLPlTB1nOUllkzh72E0/edit?usp=sharing)

        -   [Presentation](https://drive.google.com/file/d/1o9SZZmWxjQM1tAgAxz6hqkAvzAz1lBHq/view?usp=sharing) (PDF, 1.9MB)

-   5 Oct 2019 - Rational Choices About Who To Trust, [Truth and Trust Online](https://truthandtrustonline.com/).

    -   -   [Video](https://www.youtube.com/watch?v=3ermwFGVql4)

        -   [Talk slides and transcript](https://tomstafford.sites.sheffield.ac.uk/sub-sites/truth-and-trust)

        -   [Google slides](https://docs.google.com/presentation/d/1bbuO0rlX95iWQ2ndporRKpnDGfsuMBELyVeM0-3GGEc/edit?usp=sharing)

        -   [Presentation](https://drive.google.com/file/d/1c1nPWqluIR7E2av1dJh8_qvJW0BYZgj4/view?usp=sharing) (PDF, 1.6MB)

-   26 Sept 2019 - Bias, Skill and Decisions, Department of Computer Science, University of Sheffield ([Natural Language Processing Group](https://www.sheffield.ac.uk/dcs/research/groups/natural-language-processing)).

    -   -   [Google slides](https://docs.google.com/presentation/d/1jx6UEICeQXaHG7VPJzPQRtqS8k62BFPEI6jQCcr1UAI/edit?usp=sharing)

        -   [Presentation](https://drive.google.com/file/d/10a3uoYOJMd-w7uh0iKHhTPTdMBa0fhyD/view?usp=sharing) (PDF, 812KB)

-   8 April 2019 - Computation, Science and Reproducibility, [HPC at Sheffield](https://students.sheffield.ac.uk/it-services/research/hpc-facilities).

    -   -   [Google slides](https://docs.google.com/presentation/d/1dKJCeV9er0zVXblTd52GHZxZszXtGGXfpeZMLH3AD6A/edit?usp=sharing)

        -   [Presentation](https://drive.google.com/file/d/1DOuFusShxS66YtU33NNDmnM1NlOTywK2/view?usp=sharing) (PDF, 1.5KMB)

-   8 February 2019 - Confronting Bias,  [Disciplinary Conference](http://www.disciplinaryconference.com/).

    -   -   [Google slides](https://docs.google.com/presentation/d/1JQoAHhyIFkwlliiUcQtD-KyXsQpJScEQB_oy8IjZVp0/edit?usp=sharing)

        -   [Presentation](https://drive.google.com/file/d/1yGSsmE3sviNnBbDGZO6OoP-V1wnV42Da/view?usp=sharing) (PDF, 1.9MB)

        -   [Confronting Bias Project](http://confrontingbias.group.shef.ac.uk/)

        -   [Resources](http://confrontingbias.group.shef.ac.uk/resources/)

-   30 January 2019 - Research Blogging, A Bite Size Guide to Research in the 21st Century - Communicating Your Research.

    -   -   [Google slides](https://docs.google.com/presentation/d/1Ymo7ecKRAn-Cn3OblpV5Ry-9e5PrOKmIS0c5JRzznDM/edit?usp=sharing)

-   15 January 2019 - Reasons and Values, Remarks at "Re-energising the narrative: human rights in the digital age" at [Wilton Park](https://www.wiltonpark.org.uk/).

    -   -   [Blog post](https://tomstafford.sites.sheffield.ac.uk/news/remarks-at-re-energising-the-narrative-human-rights-in-the-digital-age)

        -   [Transcript](https://drive.google.com/file/d/1OwJUhPmPY1TTacJ_bR-_hN727FgAgqrk/view?usp=sharing) (PDF, 36KB)

## 2018

-   25 Sept 2018 - The Choice Engine at [Festival of the Mind](http://festivalofthemind.group.shef.ac.uk/)

    -   -   [Google slides](https://docs.google.com/presentation/d/1fK_Ven7ilQSXPv6dyLW7sBph1W7mTHo0vV8mwzTb7cM/edit?usp=sharing)

        -   [Presentation](https://drive.google.com/file/d/1G8Cb9fe22tkACNWi_Sj4VWBKhD6xm9ed/view?usp=sharing) (PDF, 2.5MB)

-   24 Sept 2018 - Defining Bias at [Empirically Informed Implicit Bias Training workshop](https://biasbestpractice.weebly.com/)

    -   -   [Google slides](https://docs.google.com/presentation/d/17dqAQ5GHNQBhYwLQZt1S8ECmbkmXY0SuL39_ANrQ_X0/edit?usp=sharing)

        -   [Presentation](https://drive.google.com/file/d/1DY9oinzNmciWdPIWVWOiUFW_X3V95m3z/view?usp=sharing) (PDF, 1.4MB)

-   2018 - Debating Sex Differences in Cognition: We Can Do Better

    -   -   [Annotated slide deck](https://tomstafford.sites.sheffield.ac.uk/sub-sites/delusions-of-gender)

        -   [Presentation](https://drive.google.com/file/d/19qNMqoVgLajvw-SpREx79Gppf0kyQPkK/view?usp=sharing) (PDF, 707KB)

        -   [Transcript](https://tomstafford.sites.sheffield.ac.uk/outputs/talks)

## 2017

-   9--12 July 2017 - Psychonomic Society Leading Edge Workshop: [Beyond the Lab: Using Big Data to Discover Principles of Cognition](https://www.psychonomic.org/page/2017workshop), Madison, Wisconsin, USA.

    -   -   [Google slides](https://docs.google.com/presentation/d/1P3IctB3SRer8HQgjXZthe87IHTdmjqu4ipKXUrnCdmc/edit?usp=sharing)

        -   [Presentation](https://drive.google.com/file/d/1-qWorkf1XjJzugnJR5Oe5Fhg--lZqh09/view?usp=sharing) (PDF 4.2MB)

-   16 May 2017 - Optimal Learning in Games @ Pint of Science, Sheffield

    -   -   [Video](https://www.youtube.com/watch?v=4W_QVrwDvMY)

        -   Screenshot from video:

![](images/pintofscience.png)

-   31 January 2017 - Experiments in Learning,  [Greenwich University](https://www.gre.ac.uk/) Open Lectures in Teaching and Learning.

    -   -   [Video](https://vimeo.com/album/3694974/video/202237782)

        -   [Presentation](https://drive.google.com/file/d/133NE1LVl4u7Q_Chv0GDATbpE0tYCFJV3/view?usp=sharing) (PDF 1.4MB)

-   19 January 2017 - Learning: new techniques for the old topic, [University of Dundee](https://www.dundee.ac.uk/), Department of Psychology.

    -   -   [Google slides](https://docs.google.com/presentation/d/1SyeTx-OVzicS6p5QOrR0HT2mz0D-R6-x_khylmRzfsw/edit?usp=sharing)

## 2016

-   7 June 2016 - Research Bloggin, [A Bite Size Guide to Research in the 21st Century](https://www.eventbrite.co.uk/e/a-bite-size-guide-to-research-in-the-21st-century-episode-two-tickets-24480920091)

    -   -   [Google slides](https://docs.google.com/presentation/d/1oE04e0y767qv97a2dag5wOnBSCjIw34Pg9jlmHOMVIE/edit?usp=sharing)

        -   [Presentation](https://drive.google.com/file/d/1jNQ4O0XoMD1ExfdGgk9Rh9by7odsQNWU/view?usp=sharing) (PDF, 1.4MB)

-   16 March 2016 - Factors influencing optimal skill learning: data from a simple online game, Network on Intrapersonal Research in Education (NIRE), York

    -   -   [Video](https://www.youtube.com/watch?time_continue=1&v=RY7Vj_XEnqo)

        -   [Presentation](https://drive.google.com/file/d/1HRiFjg1euV_jTY70xleqwX-SgypyJ7em/view?usp=sharing) (PDF, 3.1MB)

## 2012

-   July 2012 - A Berlin Cognitive Science Safari

    -   [Report](https://mindhacks.com/2012/07/16/berlin-cognitive-science-safari-report/)

    -   And I made the cover of the Wall Street Journal:

![](images/wsj.png)

## 2011 and earlier

-   [Beyond reinforcement learning in action acquisition](https://drive.google.com/file/d/1ff_6aAqGLejXUvOjRGLJ6Hc_88ln4DD9/view?usp=sharing), (OpenOffice, 3.7MB) 9 November 2011, Department of Psychological Sciences, Birkbeck University of London.

-   Inferring cognitive architectures from high-resolution behavioural data, 13 May 2011, [York Centre for Complex Systems Analysis](http://www.york.ac.uk/res/yccsa/), University of York.

-   A novel task for the investigation of action learning, 7 July 2010, Experimental Psychology Society, Manchester, 7-9 July 2010

-   An empirical test of some philosophies of science, 21 May 2010, Heng Seng Centre for Cognitive Studies, University of Sheffield

-   How do we use computational models of cognitive processes?, Neural Computation and Psychology Workshop, 8-10 April 2010, Birkbeck, London

-   [What use are computational models of cognitive processes?](https://docs.google.com/presentation/d/1GtuQOnCjySDTH6B0kUMueFq4vRD4Xr9V/edit?usp=sharing&ouid=106112927054309632662&rtpof=true&sd=true), (PowerPoint, 3.6MB) 19th of March 2010, Redwood Centre for Theoretical Neuroscience, UC Berkeley

-   [Using the psychophysics of choice behaviours to infer mental structure from reaction times](https://docs.google.com/presentation/d/1Vp6VgqAmIltnz9IWJtgFNlkqqa5GOHq4/edit?usp=sharing&ouid=106112927054309632662&rtpof=true&sd=true),(PowerPoint 2MB) 15th of January 2010, Department of Psychology, National University of Ireland, Galway

-   [Pieron's Law holds in conditions of response conflict](http://csjarchive.cogsci.rpi.edu/Proceedings/2009/papers/524/index.html), 1st August, presented at the 31st Annual Conference of the Cognitive Science Society. Amsterdam, The Netherlands.\
    [Presentation](https://docs.google.com/presentation/d/1FJcdBBXwTaZXS6inZMAOjK6FxKY1DZtU/edit?usp=sharing&ouid=106112927054309632662&rtpof=true&sd=true) (PowerPoint, 1.6MB)

-   The nonconscious mere exposure effect with brand logos: real but elusive, Department of Psychology, City College, Thessaloniki, 1/6/09

-   Email: the technology and psychology of continuous partial attention, UFI, Sheffield, 12 November 2008

-   [Things can be known : Teaching psychology through demonstrations](https://docs.google.com/presentation/d/1C6EYi_APHhpgWpidTf3cP2UQuVZxw47T/edit?usp=sharing&ouid=106112927054309632662&rtpof=true&sd=true) (PowerPoint, 7.4MB) Keynote at 26th Annual Conference of the Association for the Teaching of Psychology, University of Lincoln, 11th of July, 2008

-   How to make students talk in seminars, HEA Psychology 'Postgraduates who Teach' Network, University of Birmingham, 27 May 2008

-   The psychological foundations of privacy, Privacy in Law, Ethics and Genetic Data, 1st international workshop PRIVILEGED Project (EC FP6), 10 Jan 2008

-   Debates in Cognitive Neuroscience, Centre for Inquiry Based Learning in the Arts and Social Sciences, University of Sheffield, 30 May 2007

-   [Is there a science of advertising?](https://docs.google.com/presentation/d/1l4VwP6F2LxMsb73En7qs1g8K87wYglo9/edit?usp=sharing&ouid=106112927054309632662&rtpof=true&sd=true) (PowerPoint, 3.3MB) University of Hull, Management School, 27th of April 2007

-   Residents' perception of risk on contaminated sites, Environment Agency training day, Leeds, 20th of June, 2007

### 2024-05-12 supervision.qmd
update

---
title: "Supervision"
---

I am always enthusiastic to hear from potential PhD students. Please get in touch.

A PhD with me will involve using [robust](https://www.nature.com/articles/s41562-016-0021) and [open science](https://en.wikipedia.org/wiki/Open_science) methods to address theoretical ideas in cognitive science. Plus extensive mentoring on all aspects of the scholarly life, conducted in [Sheffield's best coffee shops](https://www.ourfaveplaces.co.uk/our-guides/top-10-coffee-shops/).

Specific projects I am currently seeking students for are [here](https://docs.google.com/document/d/1v9akVLjoYlR01V7SvGjYxUsDP2zCCbdvSXYB1NqoqcQ/edit?usp=sharing). Some advice about applying is [here](https://github.com/tomstafford/onboarding/).

# Current PhD and postdoc supervision

## Postdoc

-   [Amber Copeland](https://scholar.google.com/citations?user=JnNAldsAAAAJ&hl=en) (2018--2025) on "Reinforcer-specific value-based decision-making in persistence of and recovery from alcohol use disorder"

-   [Georgi Karadzhov](https://gkaradzhov.com/) (2024--2025) -- "DEliBots -- Deliberation Enhancing Bots" (at University of Cambridge)

## PhD

-   Indro Adinugroho (2021--2025) -- Investigating the Relation between Fundamentalism, Belief in Conspiracy Theories and Perceived Political Leadership toward Political Trust

-   Hazel Gordon (2021--2025) "[Informing citizens? Effects of imprints on digital political advertising](https://tomstafford.sites.sheffield.ac.uk/news/phd-opportunity-informing-citizens)"

-   Ioanna Spentza (2017--) -- Factors affecting Everyday Problem-Solving skills in Older Adults

### Second supervisor to...

-   Vesko Varbanov (2020-) ' Sensory processing in Autism Spectrum Conditions and Attention Deficit Hyperactivity Disorder'

# Previous supervision and examining

## As primary PhD supervisor

-   [Maria Panagiotidi](https://scholar.google.co.uk/citations?user=XcFf_6EAAAAJ&hl=en&oi=ao), PhD 2017 '[The Role of the Superior Colliculus in Attention Deficit Hyperactivity Disorder](https://etheses.whiterose.ac.uk/12124/)'

-   [Angelo Pirrone](https://scholar.google.co.uk/citations?user=UZzVps4AAAAJ&hl=en), PhD 2016 '[Decision modelling insights in cognition and adaptive decision making](http://etheses.whiterose.ac.uk/15841/)'

-   Despina Panagiotidou (co-supervised with Ana Vivas, City College, Thessaloniki), PhD 2015, 'Distractor, Temporal, and Inhibitory Variations of the Distractor Devaluation Effect of Visual Selective Attention'

-   [Tom Walton](http://www.abrg.group.shef.ac.uk/people/walton/), PhD 2012, '[The Discovery of Novel Actions](http://etheses.whiterose.ac.uk/2204/)'

-   David Yates, PhD 2012, 'Using eye-movements to elucidate architectures of object recognition and selection'

-   Cigir Kalfaoglu, PhD 2012, '[Errors and error-detection during skilled typing](http://etheses.whiterose.ac.uk/2924/)'

## As a secondary PhD supervisor

-   [Georgi Karadzhov](https://gkaradzhov.com/) (2019--2022) -- "DEliBots -- Deliberation Enhancing Bots" (at University of Cambridge)

-   Ozan Vardal (2018--2022) -- [Leveraging Big Data from eSports Games to Understand Human Skill Acquisition](http://iggi.org.uk/students/2018/ozan-vardal/) (At University of York)

-   [Elena Petrovskaya](https://www.elenapetrovskaya.com/) (2019--2023) -- Decision-making & e-sports (At University of York)

-   [Amber Copeland](https://scholar.google.com/citations?user=JnNAldsAAAAJ&hl=en) (2018--2022)  -- 'Value-based decision-making and self-control in alcohol-related behaviour change and recovery from addiction'

-   August Lindemer (2018-2022) 'Planetary Fever -- The Climate Change Communication of Health Professionals.'

-   Siham Albesisi (2018 - 2023) 'emotion regulation on ADHD children'

-   Stephanie Powell ' The relationship and effects of young children's use of technology'

-   [Máté Gyurkovics](https://scholar.google.hu/citations?user=XGk9OnEAAAAJ&hl=hu) --  'Affective factors in cognitive control: Behavioural and neural investigations in adults and adolescents'

-   Stephanie Armstrong 'Relation between the Executive Function development and the reading acquisition, from a neuropsychological view'

-   Andreas Bunge (Department of Philosophy, University of Sheffield), "The mental structure of prejudice", February 2018

-   Luana Nunes, "Ethological Decision Making with Non-Stationary Inputs Using MSPRT Based Mechanisms" May 2017

-   Alvin Pastore (Department of Computer Science), "Neuroeconomics, Reinforcement learning and the equity premium puzzle" January 2017

-   Stephanie Dunn (with Elizabeth Milne and Megan Freeth), PhD 2016 'Electrophysiological correlates of visual search in the autism spectrum'

-   [Hamideh Kerdegari](http://scholar.google.co.uk/citations?user=BZdPw4MAAAAJ&hl=en) (supervised with Tony Prescott), PhD 2016 'Head-mounted Sensory Augmentation System for Navigation in Low Visibility Environments'

-   Tom Bullock (supervised with Elizabeth Milne and Dick Eiser), 2012, 'Crossmodal Load and Selective Attention'

## Research Associate Supervision

-   Zarha Arjmandi Lari, 2022 - 2023

-   Dagmar Adamcová, 2017--2018: "Quit while you're ahead: a surprising interaction between game performance and motivation" ([Blog post](https://tomstafford.sites.sheffield.ac.uk/news/quit-while-youre-ahead), [Jupyter notebook](https://github.com/dagmaradamcova/axon-drop-out/blob/master/axon_drop_out.ipynb)). Erasmus exchange

## Post doctoral supervision

-   [Junyan Zhu](https://www.sheffield.ac.uk/politics/people/academic-staff/junyan-zhu) (2020--2023)

-   [Lotty Brand](https://lottybrand.wordpress.com/) (2020--2023)

-   Mariana Leriche, 2014--2016

-   Robin Scaife, 2013--2017

-   Jen Lewis, 2012--2013

-   Craig Bertram, 2012--2013

-   [Martin Thirkettle](https://www.shu.ac.uk/about-us/our-people/staff-profiles/martin-thirkettle), 2008--2012

# Examining

-   **Matthew Warburton, University of Leeds, 8 March 2024**

-   **Nick Simonsen, University of Nottingham, 18 October 2023**

-   Danielle Beaton, University of Sheffield, 23 November, 2022

-   **Emma Henderson, Kingston University London, 17 September 2021**

-   Stanislava Naneva, University of Sheffield, 11 November 2020

-   Andrea Caso, Birkbeck, University of London, 1 July 2019**

-   **Athanasios Kokkinakis, University of York, 12 March 2019**

-   Alejandro Jimenez Rodriguez, University of Sheffield, 15 February 2019

-   **Jim Lumsden, University of Bristol, 19 October 2018**

-   Conor Heapy, University of Sheffield, 4 May 2018

-   **Joe Thompson, Simon Fraser University, Canada, 30 April 2018**

-   Jonathan Glancy, University of Sheffield, 2 December 2016

-   Christian Beyle Sandoval, University of Sheffield, 9 October 2015

-   **Maria Dagioglou, University of Birmingham, 7 April 2014**

-   Jennifer Lewis, University of Sheffield, 2012

-   David Cameron, University of Sheffield, 2011

-   Alexander Cope, University of Sheffield, 2011

-   Mike Roberts, University of Sheffield, 21st October, 2010

### 2024-05-12 teaching.qmd
update

---
title: "Teaching"
---

# University of Sheffield

I am director for the MSc programmes in Psychological Research Methods with Data Science. I am founding director for MSc in Psychological Research Methods with Data Science. I teach a MSc module in [data management and visualisation](https://tomstafford.github.io/psy6422/).

In 2020 the Department of Psychology completed a redesign and overhaul of its undergraduate, based around a [programme level approach](https://staff.sheffield.ac.uk/teaching-guidance/curriculum/pla). I contributed to this as lead for one of the five core streams -- cognitive psychology.

I was stream lead for cognitive psychology on the undergraduate psychology BSc. Within that, I teach level 1 and 2 students the psychology of decision making, skill and reasoning.

Previously I have taught Synthetic Psychology, using [Lego robots](http://mindhacks.com/2010/06/23/the-scientific-method-lego-robots-edition/) and [Jupyter notebooks](https://github.com/tomstafford/emerge) to show how building models of behaviour can help us understand the nature of mind.

I taught a graduate seminar on contentious issues in cognitive neuroscience for several years, including dual process accounts, sex differences in the brain, and the reliability crisis in cognitive neuroscience. This module was based on the principles of inquiry-based learning and uses unresolved questions in the cognitive neurosciences to teach critical analysis of research literature and how to build a novel and interesting scientific arguments. I have published a paper and a short report on the design of the course:

-   Stafford, T. (2008), [A fire to be lighted: a case-study in enquiry-based learning](http://www.pestlhe.org.uk/index.php/pestlhe/article/view/39/160), Practice and Evidence of Scholarship of Teaching and Learning in Higher Education, Vol. 3, No. 1, April 2008, pp.20-42.

-   Stafford, T. (2008). [Teaching questions rather than answers: inquiry-based learning on an MSc course](https://drive.google.com/file/d/1ygxtidGmBfM-i0DJwBcqRf_GNL6yH32M/view?usp=sharing) (PDF, 58KB). HEA Psychology Network Newsletter, Issue 46, January 2008.

When I was module organiser for PSY241/3 Cognitive Psychology. I designed the course around the use of a [wiki](https://idiolect.org.uk/docs/wiki243/) -- an user editable webpage which allows writing practice, collaboration and encourages a critical approach to sources. Students who used the wiki more during the course scores higher on the exam:

-   Stafford, T., Elgueta, H., and Cameron, H. (2014). [Students' engagement with a collaborative wiki tool predicts enhanced written exam performance](https://journal.alt.ac.uk/index.php/rlt/article/view/1491). Research in Learning Technology, 22.

# Elsewhere

I am external examiner at the University of Manchester (2023 -  ) for their [MSc MSc Computational and Corpus Linguistics.](https://www.manchester.ac.uk/study/masters/courses/list/21198/msc-computational-and-corpus-linguistics/course-details/)

I am external examiner at the University of Glasgow (2022-2025) for their microcredential course in [Applied data skills for processing and presenting data](https://www.gla.ac.uk/coursecatalogue/course/?code=PSYCH2016).

I was invite to give a keynote at the University of Greenwich on how Cognitive Science inspires my teaching, in January 2017.

You may also enjoy this short list of [Cheap tricks for starting discussions in lectures](https://medium.com/@tomstafford/cheap-tricks-for-starting-discussions-in-lectures-c6baecd4a6c8).

# Disclaimer

This list is not comprehensive. I have teaching roles not mentioned here.

### 2024-05-15 done.qmd
update

@@
 [Talks](https://tomstafford.sites.sheffield.ac.uk/outputs/talks) or Newsletter: <https://tomstafford.substack.com/>. For current preoccupations, see [here](news.html).
+
+## 2024
+
+2024 onwards: member of University of Sheffield Research Culture Steering Board, which provides leadership and coordination for the development of institutional research culture.
+
+2021 to 2024: member of University of Sheffield Research Excellence Working group, which developed, consulted on and agreed a common definition and understanding of ‘excellence’ for use alongside the institutional research strategy.
 
@@
 
+2021 onwards: member, University of Sheffield Open Research Advsory Group, "providing strategic leadership in the ongoing development, promotion and implementation of the policies and practices supporting the University’s
+commitment to Open Research"
+
 2021: [The Experiment Design Checklist](https://tomstafford.github.io/psy-checklist/)
@@
 2020: [The Letters of Pope Gregory VII - pilot project](https://figshare.com/articles/dataset/The_Letters_of_Pope_Gregory_VII_-_pilot_project/12781049) (with Charles West and George Litchfield)
+
+2020 onwards: member, University Vice President for Research's Strategy Group (VPSG)
 
@@
 
+2017 to 2021: member, University of Sheffield Open Access Advisory Group, representing Faculty of Science, providing strategic overview of scholarly communication
+
 2017 Organised [Mind Matters](https://tomstafford.sites.sheffield.ac.uk/sub-sites/mind-matters) 'a series of events based on various psychological research to bring knowledge to the general public and showcase Sheffield as a hub for psychology!'

### 2024-05-16 done.qmd
update

@@
 ## 2024
-
-2024 onwards: member of University of Sheffield Research Culture Steering Board, which provides leadership and coordination for the development of institutional research culture.
-
-2021 to 2024: member of University of Sheffield Research Excellence Working group, which developed, consulted on and agreed a common definition and understanding of ‘excellence’ for use alongside the institutional research strategy.
 
@@
 <img src="https://tomstafford.github.io/editors/figs/gpa_vs_eds.png" height = 400>
+
+2023 onwards: member of University of Sheffield Research Culture Steering Board, which provides leadership and coordination for the development of institutional research culture.
 
@@
 
+2021 to 2024: member of University of Sheffield Research Excellence Working group, which developed, consulted on and agreed a common definition and understanding of ‘excellence’ for use alongside the institutional research strategy.
+
 2021: [The Experiment Design Checklist](https://tomstafford.github.io/psy-checklist/)

### 2024-05-22 talks.qmd
update

@@
 ---
-title: "talks"
+title: "Talks"
 ---
@@
 # Coming up
+
+- 22nd May 2024 [AFIRE Project, Research on Research Institute](https://docs.google.com/presentation/d/17Pod_cJ2b2xB1i5PCK2mi1LMpE0egH7O/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true) at [Seminar: Interventions for Funding Application Assessments](https://edicaucus.ac.uk/edica-seminar-series/) for [EDI Caucus](https://edicaucus.ac.uk/)
 

### 2024-06-04 done.qmd
update

@@
 ## 2024
+
+2024-01-03: BBC Future article [Tetris: How a US teenager achieved the 'impossible' and what his feat tells us about human capabilities](https://www.bbc.co.uk/future/article/20240103-tetris-how-a-us-teenager-achieved-the-impossible)
 
@@
 
+Led development and adoption of the [University of Sheffield statement on Open Research](https://www.sheffield.ac.uk/openresearch/university-statement-open-research)
+
 # 2020
-
-Led development and adoption of the [University of Sheffield statement on Open Research](https://www.sheffield.ac.uk/openresearch/university-statement-open-research)
 
@@
 
+2015 Data Scientist in Residence at [folksy.com](folksy.com). See [Folksy data analysis: buyer decision time](http://blog.folksy.com/2015/03/09/folksy-data-analysis-buyer-decision-time)
+
 2012 - 2017 Wrote a column for [BBC Future](https://www.bbc.com/future/columns/neurohacks)

### 2024-06-21 done.qmd
update

@@
 ## 2024
+
+2024-06-21: Research Matters magazine (with Shaun Leamon): [Experiments in research funding to reduce research](https://the-sra.org.uk/common/Uploaded%20files/Research%20Matters%20Magazine/sra-research-matters-june-2024-edition.pdf) bureaucracy
+
+2024-06-18: Early results from our project with Volkswagen Foundation: [Researchers optimistic about Distributed Peer Review](https://researchonresearch.org/dpr-volkswagen-foundation-first-results/)
+
+2024-06-17: Hosted [AI replication game](https://sites.google.com/sheffield.ac.uk/orwg/research-practice) at University of Sheffield with the [Institute for Replication](https://i4replication.org/)
+
+2024-05-23: Organised networking event for [University of Sheffield editors](https://sites.google.com/sheffield.ac.uk/orwg/research-practice)
+
+2024-06-21: [2024 Showcase for Data Analysis and Visualisation MSc Students](https://tomstafford.github.io/psy6422/class-of-2024.html)
 

### 2024-06-21 supervision.qmd
update

@@
 ## Postdoc
+
+- [Adam Partridge](https://orcid.org/0000-0002-0133-4155) (2022 -), as Open Research Training Lead for the University of Sheffield and part of the [UKRN Open Research Programme](https://www.ukrn.org/open-research-programme/)
 
@@
 
-# Examining
+# PhD Examining
 
@@
 
--   Andrea Caso, Birkbeck, University of London, 1 July 2019**
+-   **Andrea Caso, Birkbeck, University of London, 1 July 2019**
 

### 2024-07-03 news.qmd
update

@@
 <iframe allowfullscreen sandbox="allow-top-navigation allow-scripts allow-popups allow-popups-to-escape-sandbox" src="https://mastofeed.com/apiv2/feed?userurl=https%3A%2F%2Fmastodon.online%2Fusers%2Ftomstafford&theme=light&size=100&header=false&replies=false&boosts=false"></iframe>
-Colophon

### 2024-07-04 done.qmd
update

@@
 2024-06-21: [2024 Showcase for Data Analysis and Visualisation MSc Students](https://tomstafford.github.io/psy6422/class-of-2024.html)
+
+Febuary 2024: Oliver Bray shared his MSc project: Bray, O.
+J., & Stafford, T.
+(2024, February 5).
+[No Far-Transfer from Ten Years of Feedback on Task Length Estimation: A Case Study](https://osf.io/preprints/psyarxiv/fsr53).
+https://doi.org/10.31234/osf.io/fsr53.
+  - see also [Ollie's blog: Can Feedback Improve Your Productivity Estimates? Data from a 10-Year Case Study
+Ollie Bray](https://shinkai0202.github.io/PSY6009_Research_Project/)
 

### 2024-07-17 papers.qmd
update

@@
 -   Stafford T, Rombach I, Hind D et al.
-(2023) [Where next for partial randomisation of research funding?
-The feasibility of RCTs and alternatives](https://wellcomeopenresearch.org/articles/8-309/v1) Wellcome Open Res 2023, 8:309 (https://doi.org/10.12688/wellcomeopenres.19565.1)
+Where next for partial randomisation of research funding?
+The feasibility of RCTs and alternatives [version 2; peer review: 3 approved].
+Wellcome Open Res 2024, 8:309 (<https://doi.org/10.12688/wellcomeopenres.19565.2>)
 
@@
 ## In press, and under review
+
+- Boag, R.
+J., Innes, R.
+J., Stevenson, N., Bahg, G., Busemeyer, J.
+R., Cox, G.
+E., … Forstmann, B.
+(2024, July 2).
+[An expert guide to planning experimental tasks for evidence accumulation modelling](https://osf.io/preprints/psyarxiv/snqgp).
+https://doi.org/10.31234/osf.io/snqgp
 

### 2024-09-04 talks.qmd
update

@@
 
-- 22nd May 2024 [AFIRE Project, Research on Research Institute](https://docs.google.com/presentation/d/17Pod_cJ2b2xB1i5PCK2mi1LMpE0egH7O/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true) at [Seminar: Interventions for Funding Application Assessments](https://edicaucus.ac.uk/edica-seminar-series/) for [EDI Caucus](https://edicaucus.ac.uk/)
+- 8th September: "Research Culture in the UK". Keynote at [Pujiang Innovation Forum 2024](https://en.pujiangforum.cn/en/en_news_show.aspx?channel_id=20&cateid=175&id=119), Shanghai, China.
+
+  - Britain has a rich industrial and scientific heritage, with an established and diverse research culture anchored within a world-leading University sector.
+Successfully sustaining and building on the reputation of British research means addressing the challenges and criticisms of how research culture has developed in the 21st century.
+I will review some of these challenges - hypercompetition and excessive workload, employment precarity, perverse metrics, unfortunate publishing practices, lack of transparency, irreproducibility of findings and threats to international collaboration - and suggest ways forward.
+
+- 9th September: "Experiments with the funding of research". [Shanghai Institute for Science of Science](https://www.siss.sh.cn/eng/).
+
+  - Research funders share some common concerns: how do they know if they are allocating funding in the way that is most effective, fair and best balances risks versus possible rewards?
+Although a large variety of different funding systems exist, rigorous evidence on how funding can be designed to promote the best outcomes is not common.
+I will speak about the Research on Research Institute, and the programme on formal experiments that I lead there: AFIRE <https://researchonresearch.org/project/a-f-i-r-e> I will showcase good examples of strong evidence on aspects of funding systems, and talk about how funders might better use and generate evidence in the future
 
@@
 ## 2024
+
+- 22nd May 2024 [AFIRE Project, Research on Research Institute](https://docs.google.com/presentation/d/17Pod_cJ2b2xB1i5PCK2mi1LMpE0egH7O/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true) at [Seminar: Interventions for Funding Application Assessments](https://edicaucus.ac.uk/edica-seminar-series/) for [EDI Caucus](https://edicaucus.ac.uk/)
 

### 2024-09-15 talks.qmd
update

@@
 I will review some of these challenges - hypercompetition and excessive workload, employment precarity, perverse metrics, unfortunate publishing practices, lack of transparency, irreproducibility of findings and threats to international collaboration - and suggest ways forward.
+  - Slides: [PDF](shanghai2024-09-09-1.pdf)
 
@@
 I will speak about the Research on Research Institute, and the programme on formal experiments that I lead there: AFIRE <https://researchonresearch.org/project/a-f-i-r-e> I will showcase good examples of strong evidence on aspects of funding systems, and talk about how funders might better use and generate evidence in the future
+  - Slides: [PDF]<>, [transcript]<>
 

### 2024-09-15 talks.qmd
update

--- 2024-09-04 talks.qmd
@@
 
+- 16 December: "History of partial randomisation in research". At "Using partial randomisation to award research funding – a day of discussion", hosted by the British Academy, London.
+
+# Past talks
+
+## 2024
+
 - 8th September: "Research Culture in the UK". Keynote at [Pujiang Innovation Forum 2024](https://en.pujiangforum.cn/en/en_news_show.aspx?channel_id=20&cateid=175&id=119), Shanghai, China.
@@
 I will review some of these challenges - hypercompetition and excessive workload, employment precarity, perverse metrics, unfortunate publishing practices, lack of transparency, irreproducibility of findings and threats to international collaboration - and suggest ways forward.
+  - Slides: [PPT](https://docs.google.com/presentation/d/1YbnKHHsHI--njavxH7Kp_bdAzCU3UHQTkSEUzjZgfKc/edit?usp=sharing), [PDF](docs/shanghai2024-09-09.pdf)
 
@@
 I will speak about the Research on Research Institute, and the programme on formal experiments that I lead there: AFIRE <https://researchonresearch.org/project/a-f-i-r-e> I will showcase good examples of strong evidence on aspects of funding systems, and talk about how funders might better use and generate evidence in the future
-
-# Past talks
-
-## 2024
+  - Slides: [PPT](<https://docs.google.com/presentation/d/1vAzGbA68_M8uQHZ5rNJ5cVh-G5547Gat/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true), [PDF](pujiang2024-09-08.pdf), [transcript](shanghai_transcript2024-09-08.pdf)<>
 

### 2024-09-15 talks.qmd
update

@@
 I will speak about the Research on Research Institute, and the programme on formal experiments that I lead there: AFIRE <https://researchonresearch.org/project/a-f-i-r-e> I will showcase good examples of strong evidence on aspects of funding systems, and talk about how funders might better use and generate evidence in the future
-  - Slides: [PPT](<https://docs.google.com/presentation/d/1vAzGbA68_M8uQHZ5rNJ5cVh-G5547Gat/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true), [PDF](pujiang2024-09-08.pdf), [transcript](shanghai_transcript2024-09-08.pdf)<>
+  - Slides: [PPT](https://docs.google.com/presentation/d/1vAzGbA68_M8uQHZ5rNJ5cVh-G5547Gat/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true), [PDF](pujiang2024-09-08.pdf), [transcript](shanghai_transcript2024-09-08.pdf)<>
 

### 2024-09-15 talks.qmd
update

@@
 I will speak about the Research on Research Institute, and the programme on formal experiments that I lead there: AFIRE <https://researchonresearch.org/project/a-f-i-r-e> I will showcase good examples of strong evidence on aspects of funding systems, and talk about how funders might better use and generate evidence in the future
-  - Slides: [PPT](https://docs.google.com/presentation/d/1vAzGbA68_M8uQHZ5rNJ5cVh-G5547Gat/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true), [PDF](pujiang2024-09-08.pdf), [transcript](shanghai_transcript2024-09-08.pdf)<>
+  - Slides: [PPT](https://docs.google.com/presentation/d/1vAzGbA68_M8uQHZ5rNJ5cVh-G5547Gat/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true), [PDF](docs/pujiang2024-09-08.pdf), [transcript](docs/shanghai_transcript2024-09-08.pdf)
 

### 2024-09-20 papers.qmd
update

@@
 -    Panagiotidi, M., Zavlis, O., Jones, M., & Stafford, T.
-(2023).
-[The three-dimensional community structure of ADHD traits captured by the ASRS scale: An Exploratory Graph Analysis](http://doi.org/10.1002/mpr.1997).
-International Journal of Methods in Psychiatric Research.
-http://doi.org/10.1002/mpr.1997
+(2024).
+[The three-dimensional community structure of attention-deficit hyperactivity disorder (ADHD) traits captured by the Adult ADHD Self-Report Scale: An exploratory graph analysis](https://onlinelibrary.wiley.com/doi/full/10.1002/mpr.1997).
+International Journal of Methods in Psychiatric Research, e1997.
+<https://doi.org/10.1002/mpr.1997> - [[preprint](https://psyarxiv.com/sakn9)]
 
@@
 Nature Scientific Reports 9(1), 3423.
-([pre-print](https://psyarxiv.com/b25tf/))
+[[pre-print](https://psyarxiv.com/b25tf/)]
 
@@
 
--   Jones, A., Stafford, T., & Petrovskaya, E. (under review). [Exploring the multiverse of analysis options for the Addiction Stroop](https://psyarxiv.com/prfu2/).
+-   Jones, A., Petrovskaya, E., & Stafford, T.
+(2024).
+[Exploring the multiverse of analysis options for the alcohol Stroop](https://link.springer.com/article/10.3758/s13428-024-02377-5).
+Behavior Research Methods, 56(4), 3578-3588.
+[[preprint](https://psyarxiv.com/prfu2/)]
 
@@
 
+- Karadzhov, G., Vlachos, A., & Stafford, T. (2024). The effect of diversity on group decision-making. arXiv preprint [arXiv:2402.01427](https://arxiv.org/abs/2402.01427).
+
 - Boag, R.
@@
 [An expert guide to planning experimental tasks for evidence accumulation modelling](https://osf.io/preprints/psyarxiv/snqgp).
-https://doi.org/10.31234/osf.io/snqgp
-
--   Adinugroho, I., Stafford, T., & Bentall, R.
-(2023, November 1).
-[The correlation between conspiracy mentality and vaccine intentions is moderated by social events: Evidence from longitudinal data during COVID-19 pandemic in the UK](https://osf.io/preprints/psyarxiv/5wcnz/).
-Retrieved from osf.io/preprints/psyarxiv/5wcnz
 
@@
 bioRxiv 2023.09.08.556817; doi: https://doi.org/10.1101/2023.09.08.556817
-
--   Copeland, A., Stafford, T., & Field, M.
-(2023, August 23).
-[Value-based decision-making in regular alcohol consumers following experimental manipulation of alcohol value](https://osf.io/wcks6/).
-https://doi.org/10.31219/osf.io/wcks6
-
--   Panagiotidi, M., Zavlis, O., Jones, M., & Stafford, T.
-(2023, July 14).
-[The three-dimensional community structure of ADHD traits captured by the ASRS scale: An Exploratory Graph Analysis](https://psyarxiv.com/sakn9).
-Retrieved from psyarxiv.com/sakn9
 
@@
 
--   Jones, A., Stafford, T., & Petrovskaya, E. (2022). [Exploring the multiverse of analysis options for the Addiction Stroop](https://psyarxiv.com/prfu2/).
-
--   Panagiotidi, M., Stafford, T., and Overton, P. (submitted). The relationship between cognitive control and task switching and problematic phone use. [Email for document]
-
 -   Karadzhov, G., Stafford, T., and Vlachos, A.
@@
 
--   de Kock, C., Stafford, T., & Vlachos, A. (2022). [How to disagree well: Investigating the dispute tactics used on Wikipedia](https://arxiv.org/abs/2212.08353). arXiv preprint arXiv:2212.08353.
+## 2024
+
+-   Jones, A., Petrovskaya, E., & Stafford, T.
+(2024).
+[Exploring the multiverse of analysis options for the alcohol Stroop](https://link.springer.com/article/10.3758/s13428-024-02377-5).
+Behavior Research Methods, 56(4), 3578-3588.
+[[preprint](https://psyarxiv.com/prfu2/)]
+
+-  Stafford, T., Gordon, H., Zhu, J., & Dommett, K.
+(2024).
+[Online political adverts: The effect of disclosures and opportunities for clandestine campaigning](https://onlinelibrary.wiley.com/doi/10.1111/pops.13034).
+Political Psychology, 00, 1–27.
+<https://doi.org/10.1111/pops.13034>
+
+-    Panagiotidi, M., Zavlis, O., Jones, M., & Stafford, T.
+(2024).
+[The three-dimensional community structure of attention-deficit hyperactivity disorder (ADHD) traits captured by the Adult ADHD Self-Report Scale: An exploratory graph analysis](https://onlinelibrary.wiley.com/doi/full/10.1002/mpr.1997).
+International Journal of Methods in Psychiatric Research, e1997.
+<https://doi.org/10.1002/mpr.1997> [[preprint](https://psyarxiv.com/sakn9)]
+
+-   Adinugroho, I., Stafford, T., & Bentall, R.
+(2024).
+[The correlation between conspiracy mentality and vaccine intentions is moderated by social events: Evidence from longitudinal data during COVID-19 pandemic in the UK](https://www.sciencedirect.com/science/article/pii/S0264410X24005103).
+Vaccine, 42(16), 3607-3614.
+<https://doi.org/10.1016/j.vaccine.2024.04.071>  [[preprint](https://osf.io/preprints/psyarxiv/5wcnz/)]
+
+-   Copeland, A., Stafford, T., & Field, M.
+(2024).
+[Value-based decision-making in regular alcohol consumers following experimental manipulation of alcohol value](https://www.sciencedirect.com/science/article/pii/S0306460324001187).
+Addictive Behaviors, 156, 108069.
+<https://doi.org/10.1016/j.addbeh.2024.108069> [[preprint](https://osf.io/wcks6/)]
 

### 2024-10-16 supervision.qmd
update

@@
 
-Specific projects I am currently seeking students for are [here](https://docs.google.com/document/d/1v9akVLjoYlR01V7SvGjYxUsDP2zCCbdvSXYB1NqoqcQ/edit?usp=sharing).
-Some advice about applying is [here](https://github.com/tomstafford/onboarding/).
+I am not currently accepting applications for PhD places. My old advice page about applying is [here](https://github.com/tomstafford/onboarding/).
 

### 2024-10-18 papers.qmd
update

@@
 International Journal of Methods in Psychiatric Research, e1997.
-<https://doi.org/10.1002/mpr.1997> - [[preprint](https://psyarxiv.com/sakn9)]
+<https://doi.org/10.1002/mpr.1997> [[preprint](https://psyarxiv.com/sakn9)]
 
@@
 Proceedings of the ACM on Human-Computer Interaction, CSCW.
-https://doi.org/10.1145/3610056 [[arXiv](https://arxiv.org/abs/2108.05271)]
+<https://doi.org/10.1145/3610056> [[arXiv](https://arxiv.org/abs/2108.05271)]
 
@@
 ## 2024
+
+-   Dommett, K., Mensah, S.
+A., Zhu, J., & Stafford, T.
+(2024).
+[Understanding the communicative strategies used in online political advertising and how the public views them](https://doi.org/10.1177/13691481241287177).
+The British Journal of Politics and International Relations, 0(0).
+https://doi.org/10.1177/13691481241287177
 

### 2024-10-27 papers.qmd
update

@@
 
-- Karadzhov, G., Vlachos, A., & Stafford, T. (2024). The effect of diversity on group decision-making. arXiv preprint [arXiv:2402.01427](https://arxiv.org/abs/2402.01427).
+- Zhu, X., Zhang, C., Stafford, T., Collier, N., & Vlachos, A. (2024). Conformity in Large Language Models. arXiv preprint [arXiv::2410.12428](https://doi.org/10.48550/arXiv.2410.12428)
 
@@
 ## 2024
+
+- Karadzhov, G.
+M., Vlachos, A., & Stafford, T.
+(2024).
+The effect of diversity on group decision-making.
+Proceedings of the Annual Meeting of the Cognitive Science Society, 46(0).
+https://escholarship.org/uc/item/6685n22z.
+arXiv preprint [arXiv:2402.01427](https://arxiv.org/abs/2402.01427).
 
@@
 
--   Farag, Y., Brand, C.
-O., Amidei, J., Piwek, P., Stafford, T., Stoyanchev, S., & Vlachos, A.
-(2023).
+-   Farag, Y., Brand, C., Amidei, J., Piwek, P., Stafford, T., Stoyanchev, S., & Vlachos, A.
+(2022).
 Opening up Minds with Argumentative Dialogues.
-SiCON 2023 (co-located with ACL 2023) [[preprint]](https://arxiv.org/abs/2301.06400)
+In Y.
+Goldberg, Z.
+Kozareva, & Y.
+Zhang (Eds.), Findings of the Association for Computational Linguistics: EMNLP 2022 (pp.
+4569–4582).
+Association for Computational Linguistics.
+https://doi.org/10.18653/v1/2022.findings-emnlp.335
 
@@
 
--   Holroyd, J., Scaife, R., Stafford, T. (in press). [What is implicit bias](http://onlinelibrary.wiley.com/doi/10.1111/phc3.12437/full)? Philosophy Compass, 12(10), e12437.
-
--   Holroyd, J., Scaife, R., Stafford, T. (in press). [Responsibility for Implicit Bias](http://onlinelibrary.wiley.com/doi/10.1111/phc3.12410/abstract). Philosophy Compass, 12(3), e12410.
-
 -   Thirkettle, M., Thyoka, M., Fernandes, N., Gopalan, P., Stafford, T.
@@
 Perception, 46 (6), 665--678.
+
+-   Holroyd, J., Scaife, R., Stafford, T. (2017). [What is implicit bias](http://onlinelibrary.wiley.com/doi/10.1111/phc3.12437/full)? Philosophy Compass, 12(10), e12437.
+
+-   Holroyd, J., Scaife, R., Stafford, T. (2017). [Responsibility for Implicit Bias](http://onlinelibrary.wiley.com/doi/10.1111/phc3.12410/abstract). Philosophy Compass, 12(3), e12410.
 

### 2024-11-20 talks.qmd
update

@@
 
+- 20 November: (chair) AFIRE Funder's Forum - promoting experiments by research funders :  [slides](https://docs.google.com/presentation/d/1yuXXm398di67hA3NwgJf5pRZ39LVPWHg/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true)
+
 # Past talks
@@
 ## 2024
+
+- 23 October: (chair) AFIRE Funder's Forum - promoting experiments by research funders:  [slides](https://docs.google.com/presentation/d/19XrX5qCxNrBIfYrUIEd832eQ17nE6Ad5/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true)
 

### 2024-12-12 supervision.qmd
update

@@
 
--   Vesko Varbanov (2020-) ' Sensory processing in Autism Spectrum Conditions and Attention Deficit Hyperactivity Disorder'
+-   James Myers (2022-) 'Modelling cognitive decline in dementia patients: the impact of social isolation'
+
+-   Vesko Varbanov (2020-) 'Sensory processing in Autism Spectrum Conditions and Attention Deficit Hyperactivity Disorder'
 

### 2024-12-13 talks.qmd
update

@@
 
-- 16 December: "History of partial randomisation in research". At "Using partial randomisation to award research funding – a day of discussion", hosted by the British Academy, London.
+- 16 December: "History of partial randomisation in research".
+At "Using partial randomisation to award research funding – a day of discussion", hosted by the British Academy, London.
+[Slides](https://docs.google.com/presentation/d/115XGeezR0bSeVcZQBVMo5mzvLZ7_QLBj/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true)
 
-- 20 November: (chair) AFIRE Funder's Forum - promoting experiments by research funders :  [slides](https://docs.google.com/presentation/d/1yuXXm398di67hA3NwgJf5pRZ39LVPWHg/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true)
+- 18 December: (chair) AFIRE Funder's Forum - promoting experiments by research funders :  [slides](https://docs.google.com/presentation/d/1C_O_V7tzreRB_ws5tmMR-N4e2gxJ4G_U/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true)
 
@@
 ## 2024
+
+- 20 November: (chair) AFIRE Funder's Forum - promoting experiments by research funders :  [slides](https://docs.google.com/presentation/d/1yuXXm398di67hA3NwgJf5pRZ39LVPWHg/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true)
 

### 2025-01-06 done.qmd
update

@@
 ## 2024
+
+2024-12-23: Made a webscraping bot on mastodon: [https://mastodon.social/@PAXscraper](https://mastodon.social/@PAXscraper), which reports stats from PsyArXiv:
+
+<img src="images/PAXdec2024.png" height = 400>
+
+2024-11-28/29: Represented [UKRN](https://www.ukrn.org/) at the [Swiss National Science Foundation](https://www.snf.ch/en)'s Research on Research Conference, Bern.
+
+2024-10-23: Inaugural event of the [AFIRE Funder Forum](https://researchonresearch.org/afire-funders-forum/)
+
+2024-10-07: Nature editorial on our project with VolkswagenStiftung: [New peer-review trial lets grant applicants evaluate each other’s proposals](https://www.nature.com/articles/d41586-024-03106-w)
+
+2024-09: Trip to China. News story on this: [Navigating Research Culture and Funding Practices: Highlights from Shanghai](https://researchonresearch.org/shanghai-forum-tom-stafford-afire/)
+
+2024-08-30: Article in New Scientist with Kate Dommett: [Is digital technology really swaying voters and undermining democracy?](https://www.newscientist.com/article/mg26335062-800-is-digital-technology-really-swaying-voters-and-undermining-democracy/).
+My [newsletter on this](https://tomstafford.substack.com/p/the-truth-about-digital-propaganda)
 

### 2025-01-06 done/2012-06-06.qmd
update

---
title: "2012-06-06"
---

# Fundamentals of learning: the exploration-exploitation trade-off

*Originally published 2012-06-06*

The exploration-exploitation trade-off is a fundamental dilemma whenever you learn about the world by trying things out. The dilemma is between choosing what you know and getting something close to what you expect (‘exploitation’) and choosing something you aren’t sure about and possibly learning more (‘exploration’). For example, suppose you are in a restaurant and you look at the menu:

-   Fish and chips

-   Chole poori

-   Paneer uttappam

-   Khara dosa

Assuming for the sake of example that you’re not very good with Sri Lankan food, you’ve now got a choice. You can ‘exploit’ – go with the fish and chips, which will probably be alright – or you can ‘explore’ – try something you haven’t had before and see what you get. Obviously which you decide to do will depend on many things: how hungry you are, how good the restaurant reviews are, how adventurous you are, how often you reckon you’ll be coming back etc.

What’s important is that the study of the best way to make these kinds of choices – [called reinforcement learning](http://webdocs.cs.ualberta.ca/~sutton/book/the-book.html) – has shown that optimal learning requires that you to sometimes make some bad choices. This means that sometimes you have to choose to avoid the action you think will be most rewarding, and take an action which you think will be less rewarding.

The rationale is that these ‘sub-optimal’ actions are necessary for your long term benefit – you need to go off track sometimes to learn more about the environment. The exploration-exploitation dilemma is really a trade-off : enjoy more now vs learn more now and enjoy later. You can’t avoid it, all you can do is position yourself somewhere along the spectrum.

Because the trade-off is fundamental we would expect to be able to see it in all learning domains, not just restaurant food choices. In work just published, we’ve been using a new task to look at how actions are learnt.

Using a joystick we asked people to explore the space of all possible movements, giving them a signal when they made a particular target movement. This task – which we’re pretty keen on – gives us a lens to look at the relation between how people explore the possible movements they can make and which particular movements they learn to rely on to generate predictable outcomes (which we call ‘actions’).

Using data gathered from this task, it is possible to see the exploitation-exploration trade-off in action. With each target people get 10 attempts to try to identify the right movement to make. Obviously some successful movements will be more efficient than others, because it is possible to hit the target after going all “round the houses” first, adding lots of extraneous movements and taking longer than needed.

If you had a success like this you could repeat it exactly (‘exploit’), or try and cut out some of the extraneous movement and risk missing the target (‘explore’). Obviously this refinement of action through trial and error is of critical interest to anyone who cares about how we learn skilled movements.

I calculated an average performance score for the first 50% and second 50% of attempts (basically a measure of distance travelled before hitting the target – so lower scores mean better performance). I also calculated how variable these performance scores were in the first 50% and second 50%.

Normally we would expect people who perform best in the first half of a test to perform best in the second half (depressingly people who start out ahead usually stay there!). But this analysis showed up something interesting: a strong correlation between variability in the first half and performance in the second half. You can see this in the graph:

![](https://lh7-rt.googleusercontent.com/u/0/docs/AHkbwyKXyazJAed-8vKiBtFmh0zHAiHWmD3Z8Kz6zKkjJVgAiNrr84hz56SILsK7ZoQ5KSRz7_t7QILjHK3cLd8ohSkOWogjedRVBps9ziU4POHZdm0zy45VJ2Vg2rC3tKnd9sTtF_C6-w4HKRfpI0NlGlxeN7xT9khANvaUk5mLbWoBgTE15lWH5ZnujeQXhktiSnx6Xb5mol9NAcXJamZM0rmgDb2l41hTo1G5uxLH_FSBxOUwl5N9yFqHH-LhS0GzEyGhnBHwqCfwDlKnJLOw6H5stHLuZPTbkKvWQIJ9zRdXulvGx1KuPswYbJ9PUAVHDvMMd0K4u2yZS3BW7jAufJpTJYge56BISSfI-5lMJqwy0r46aHY-ToPyv__p7kmDC-7eqeIvyCCVXEF4plXNGJVdSRDtwkTxtklPIbKp9CQe684KATRjBs0FjjFW_EjdiLdOAhzgjRK3LAU_lFKbWcSvTbhk5X83-XEdtCgsjO4s_4qLtoDbTHjvZaklrMt2b05k4lNF9n1PUKzofRVOqP5Voi_Rz4XlgCGH4ZLp3YFwVI1MG6HTAQOpUD_k092WaZFTnKcNv6ZX0chtnUP7WVRJHr_sVIVu1vWD8C3Zwu36KOLZuV8bKsNhg4bjG3LpT0GrYsMoicxTn4EeFMJ1P1S7ltScHf5NhhReoXxVaXrEVTxBzywK9Rypt_JJEkG3pmw-LaLlTe2sbtNv8gPKiRpyHHRFjhq_nhp0RBgStI6yX8Nk3vubSMOkUzugcu76w3JiF5G21vmO0uHOhFLLQfAGSwk-zTT8_Tgmo-CknceRtFi0_XsWT_i2Vo5SLXvY4FYRim2b-Az1xKhEiiNzZ0TTGLq_Im4A9CUlCLUqxR2-Uy-8N7avVKmmaDaDy5fr3emqOaOrMo9y85WnHFkJgqHNhOsk0_k)

This shows that people who are most inconsistent when they start to learn perform best towards the end of learning. Usually inconsistency is a bad sign, so it is somewhat surprising that it predicts better performance later on. The obvious interpretation is in terms of the exploration-exploitation trade-off.

The inconsistent people are trying out more things at the beginning, learning more about what works and what doesn’t. This provides them with the foundation to perform well later on. This pattern holds when comparing across individuals, but it also holds for comparing across trials (so for the same individual, their later performance is better for targets on which they are most inconsistent on early in learning).

You can read about this, and more, in our new paper, which is open-access over at PLoS One [A novel task for the investigation of action acquisition](http://dx.plos.org/10.1371/journal.pone.0037749).

### 2025-01-06 done.qmd
update

@@
 <img src="images/PAXdec2024.png" height = 400>
+
+2024-12-19: Kate took this picture in [Elm](https://www.elmsheffield.co.uk/)
+
+<a href="images/tom_2024-12-19.jpg"><img src="images/tom_2024-12-19small.jpg" height = 400></a>
 
@@
 
+2012-06-06: [Fundamentals of learning: the exploration-exploitation trade-off](done/2012-06-12.html)
+
+2012-06-04: [New paper: A novel task for the investigation of action acquisition](done/2012-06-12.html)
+
 2012: [The Cognitive Science Safari](https://sites.google.com/d/1nQb4g6jqk7M0gwaD4Bvw7QKtBg0nkQRV/p/1Q0M0b1kRUveC9w0Li7Je0A1f1E8PzzYB/edit) was a street-tour of classic social psychology experiments, in Berlin as part of the BMW Guggenheim Lab.

### 2025-01-06 done/2012-06-04.qmd
update

---
title: "2012-06-04"
---

# New paper: A novel task for the investigation of action acquisition

*Originally published 2012-06-04*. \

Our new paper, [A novel task for the investigation of action acquisition](http://dx.plos.org/10.1371/journal.pone.0037749), has been published in PLoS One today. The paper describes a new paradigm we’ve been using to investigate how actions are learnt.

It’s a curious fact that although psychologists have thoroughly investigated how actions are valued (ie how you figure out how good or bad a thing is to do), and how actions are trained (ie shaped and refined over time), the same effort has not gone into investigating how a behaviour is first identified and stored as a part of our repertoire. We hope this task provides a useful tool for opening up this area for investigation.

As well as the basic description of the task, the paper also contains a section outlining how the form of learning the the task makes available for inspection is different from the forms of learning made available by other ‘action learning’ tasks (for example, operant conditioning tasks).

In addition to serving an under-investigated area of learning research, the task also has a number of practical benefits. It is scalable in difficulty, suitable for repeated measures designs (meaning you can do it again and again – it isn’t something you learn once and then can’t be tested on any more) as well being adaptable for different species (meaning you can test humans and non-human animals on the task).

The paper is based on work done as part of the EU robotics project I’m on ([‘I’M-CLeVeR‘](http://www.im-clever.eu/)) and on Tom Walton’s PhD thesis, [The Discovery of Novel Actions](http://etheses.whiterose.ac.uk/2204/).

### 2025-01-06 done/2012-06-06.qmd
update

@@
 
-![](https://lh7-rt.googleusercontent.com/u/0/docs/AHkbwyKXyazJAed-8vKiBtFmh0zHAiHWmD3Z8Kz6zKkjJVgAiNrr84hz56SILsK7ZoQ5KSRz7_t7QILjHK3cLd8ohSkOWogjedRVBps9ziU4POHZdm0zy45VJ2Vg2rC3tKnd9sTtF_C6-w4HKRfpI0NlGlxeN7xT9khANvaUk5mLbWoBgTE15lWH5ZnujeQXhktiSnx6Xb5mol9NAcXJamZM0rmgDb2l41hTo1G5uxLH_FSBxOUwl5N9yFqHH-LhS0GzEyGhnBHwqCfwDlKnJLOw6H5stHLuZPTbkKvWQIJ9zRdXulvGx1KuPswYbJ9PUAVHDvMMd0K4u2yZS3BW7jAufJpTJYge56BISSfI-5lMJqwy0r46aHY-ToPyv__p7kmDC-7eqeIvyCCVXEF4plXNGJVdSRDtwkTxtklPIbKp9CQe684KATRjBs0FjjFW_EjdiLdOAhzgjRK3LAU_lFKbWcSvTbhk5X83-XEdtCgsjO4s_4qLtoDbTHjvZaklrMt2b05k4lNF9n1PUKzofRVOqP5Voi_Rz4XlgCGH4ZLp3YFwVI1MG6HTAQOpUD_k092WaZFTnKcNv6ZX0chtnUP7WVRJHr_sVIVu1vWD8C3Zwu36KOLZuV8bKsNhg4bjG3LpT0GrYsMoicxTn4EeFMJ1P1S7ltScHf5NhhReoXxVaXrEVTxBzywK9Rypt_JJEkG3pmw-LaLlTe2sbtNv8gPKiRpyHHRFjhq_nhp0RBgStI6yX8Nk3vubSMOkUzugcu76w3JiF5G21vmO0uHOhFLLQfAGSwk-zTT8_Tgmo-CknceRtFi0_XsWT_i2Vo5SLXvY4FYRim2b-Az1xKhEiiNzZ0TTGLq_Im4A9CUlCLUqxR2-Uy-8N7avVKmmaDaDy5fr3emqOaOrMo9y85WnHFkJgqHNhOsk0_k)
+![](../images/2012-06-06.png)
 

### 2025-01-07 done.qmd
update

@@
 
+2012 September: [The Cognitive Science Safari](done/2012-09-06.html) was a street-tour of classic social psychology experiments, in Berlin as part of the BMW Guggenheim Lab.
+I was on the cover of the Wall Street Journal.
+
 2012-06-06: [Fundamentals of learning: the exploration-exploitation trade-off](done/2012-06-12.html)
@@
 
-2012: [The Cognitive Science Safari](https://sites.google.com/d/1nQb4g6jqk7M0gwaD4Bvw7QKtBg0nkQRV/p/1Q0M0b1kRUveC9w0Li7Je0A1f1E8PzzYB/edit) was a street-tour of classic social psychology experiments, in Berlin as part of the BMW Guggenheim Lab.
-
 2011: [The Tea Taste Test](https://sites.google.com/d/1nQb4g6jqk7M0gwaD4Bvw7QKtBg0nkQRV/p/1O7uZnZPiKBL7C6JiR0DLSgGCqVw86uYX/edit) -- explaining why statistics are important to psychology, using a controversy of how to make a cup of tea.

### 2025-02-04 talks.qmd
update

@@
 
-- 16 December: "History of partial randomisation in research".
-At "Using partial randomisation to award research funding – a day of discussion", hosted by the British Academy, London.
-[Slides](https://docs.google.com/presentation/d/115XGeezR0bSeVcZQBVMo5mzvLZ7_QLBj/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true)
-
-- 18 December: (chair) AFIRE Funder's Forum - promoting experiments by research funders :  [slides](https://docs.google.com/presentation/d/1C_O_V7tzreRB_ws5tmMR-N4e2gxJ4G_U/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true)
+- 4 February: "Do we truly understand those we disagree with, and how could we test this?
+The Ideological Turing test", Psychopathology Lab meeting, University of Sheffield (host: Richard Bentall) : [slides](https://docs.google.com/presentation/d/1cEsWXBo4uZFZ8TKJj_NuNGendjLpiC04Wd6DbgmaQP8/edit?usp=sharing)
 
@@
 ## 2024
+
+- 18 December: (chair) AFIRE Funder's Forum - promoting experiments by research funders :  [slides](https://docs.google.com/presentation/d/1C_O_V7tzreRB_ws5tmMR-N4e2gxJ4G_U/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true)
+
+- 16 December: "History of partial randomisation in research".
+At "Using partial randomisation to award research funding – a day of discussion", hosted by the British Academy, London.
+[Slides](https://docs.google.com/presentation/d/115XGeezR0bSeVcZQBVMo5mzvLZ7_QLBj/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true)
 

### 2025-02-22 teaching.qmd
update

@@
 
-I am external examiner at the University of Manchester (2023 -  ) for their [MSc MSc Computational and Corpus Linguistics.](https://www.manchester.ac.uk/study/masters/courses/list/21198/msc-computational-and-corpus-linguistics/course-details/)
+I was external examiner at the University of Glasgow (2022-2025) for their microcredential course in [Applied data skills for processing and presenting data](https://www.gla.ac.uk/coursecatalogue/course/?code=PSYCH2016).
 
-I am external examiner at the University of Glasgow (2022-2025) for their microcredential course in [Applied data skills for processing and presenting data](https://www.gla.ac.uk/coursecatalogue/course/?code=PSYCH2016).
+I was external examiner at the University of Manchester (2023) for their new [MSc MSc Computational and Corpus Linguistics.](https://www.manchester.ac.uk/study/masters/courses/list/21198/msc-computational-and-corpus-linguistics/course-details/)
 

### 2025-03-13 papers.qmd
update

@@
 
--   de Kock, C., Stafford, T., & Vlachos, A. (2022). [How to disagree well: Investigating the dispute tactics used on Wikipedia](https://arxiv.org/abs/2212.08353). arXiv preprint arXiv:2212.08353.
+-   De Kock, C., Stafford, T., & Vlachos, A.
+(2022).
+[How to disagree well: Investigating the dispute tactics used on Wikipedia](https://arxiv.org/abs/2212.08353).
+In Y.
+Goldberg, Z.
+Kozareva, & Y.
+Zhang (Eds.), Proceedings of the 2022 Conference on Empirical Methods in Natural Language Processing (pp.
+3824–3837).
+Association for Computational Linguistics.
+https://doi.org/10.18653/v1/2022.emnlp-main.252
 
@@
 ## In press, and under review
+
+- Lee, J., Zhu, X., Karadzhov, G., Stafford, T., Vlachos, A., & Lee, D.
+(2025).
+[Collaborative Evaluation of Deepfake Text with Deliberation-Enhancing Dialogue Systems](https://arxiv.org/abs/2503.04945).
+arXiv preprint arXiv:2503.04945.
 
@@
 <https://doi.org/10.1016/j.addbeh.2024.108069> [[preprint](https://osf.io/wcks6/)]
+
+- Stafford, T., Zhu, J., & Dommett, K.
+(2024, December 31).
+[Quantifying belief in the rationality of others: the Faith in Reason scale](https://doi.org/10.31234/osf.io/umwxj).
+Working paper.
+<https://doi.org/10.31234/osf.io/umwxj>
 
@@
 
-Stafford, T. and Webb, M. (2004). [Mind Hacks: Tips and Tricks for using your brain](http://www.mindhacks.com/). Sebastapol, CA: O'Reilly.
+-   Stafford, T. and Webb, M. (2004). [Mind Hacks: Tips and Tricks for using your brain](http://www.mindhacks.com/). Sebastapol, CA: O'Reilly.

### 2025-03-24 talks.qmd
update

@@
 
+- 25 March: The Accelerator For Innovation & Research Funding Experimentation - AFIRE @ The National Research Foundation
+and Research on Research Institute Partnership Meeting: [slides](https://docs.google.com/presentation/d/1DohQA6DPndxx_spfDuIe13N8XwYiGUna/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true)
+
+# Past talks
+
+## 2025
+
+- 19 February: (chair) AFIRE Funder's Forum - promoting experiments by research funders :  [slides](https://docs.google.com/presentation/d/1E_A9yS-zeZNSJ7M41t8g2l9U_5ObDcc3/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true)
+
 - 4 February: "Do we truly understand those we disagree with, and how could we test this?
 The Ideological Turing test", Psychopathology Lab meeting, University of Sheffield (host: Richard Bentall) : [slides](https://docs.google.com/presentation/d/1cEsWXBo4uZFZ8TKJj_NuNGendjLpiC04Wd6DbgmaQP8/edit?usp=sharing)
-
-# Past talks
 

### 2025-03-24 talks.qmd
update

--- 2025-02-04 talks.qmd
@@
 
+- 25 March: The Accelerator For Innovation & Research Funding Experimentation - AFIRE @ The National Research Foundation
+and Research on Research Institute Partnership Meeting: [slides](https://docs.google.com/presentation/d/1UkmQxS7nlKJA784B95NuNO_UoH6PlDl6/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true)
+
+# Past talks
+
+## 2025
+
+- 19 February: (chair) AFIRE Funder's Forum - promoting experiments by research funders :  [slides](https://docs.google.com/presentation/d/1E_A9yS-zeZNSJ7M41t8g2l9U_5ObDcc3/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true)
+
 - 4 February: "Do we truly understand those we disagree with, and how could we test this?
 The Ideological Turing test", Psychopathology Lab meeting, University of Sheffield (host: Richard Bentall) : [slides](https://docs.google.com/presentation/d/1cEsWXBo4uZFZ8TKJj_NuNGendjLpiC04Wd6DbgmaQP8/edit?usp=sharing)
-
-# Past talks
 

### 2025-03-31 papers.qmd
update

@@
 
+- Copeland, A., Dora, J., King, K., Stafford, T., & Field, M.
+(in press).
+Value-based decision-making in daily tobacco smokers following experimental manipulation of mood.
+*Experimental and Clinical Psychopharmacology* [preprint](https://osf.io/preprints/psyarxiv/5w4ap_v1)
+
 - Lee, J., Zhu, X., Karadzhov, G., Stafford, T., Vlachos, A., & Lee, D.
@@
     -   -   See also: [delibot.xyz](https://www.delibot.xyz/)
+
+## 2025
+
+- Vardal, O., Karapanagiotidis, T., Stafford, T., Drachen, A., & Wade, A.
+(2025).
+[Unsupervised identification of internal perceptual states influencing psychomotor performance](https://doi.org/10.1016/j.neuroimage.2025.121134).
+NeuroImage, 310, 121134.
+https://doi.org/10.1016/j.neuroimage.2025.121134
+[[preprint](https://www.biorxiv.org/content/10.1101/2023.09.08.556817v2.abstract)]
 

### 2025-05-12 talks.qmd
update

--- 2025-02-04 talks.qmd
@@
 
+- June 4. Evolution and Social Cognition lab,	Institut Jean Nicod, Paris.
+
+- Panel on Distributed Peer Review, International Conference on the Science of Science ([ICSSI](https://icssi.org/)), June 16 - 18, Copenhagen.
+
+- Evaluating Distributed Peer Review at the Volkswagen Foundation. Metascience 2025, June 30 - 2 July, London.
+
+- Can AI be used for better matching of proposals to reviewers? Feasibility and formal evaluation with the Metascience 2025 conference. Metascience 2025, June 30 - 2 July, London.
+
+# Past talks
+
+## 2025
+
+- 25 March: The Accelerator For Innovation & Research Funding Experimentation - AFIRE @ The National Research Foundation, South Africa; and Research on Research Institute Partnership Meeting: [slides](https://docs.google.com/presentation/d/1UkmQxS7nlKJA784B95NuNO_UoH6PlDl6/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true)
+
+- 19 February: (chair) AFIRE Funder's Forum - promoting experiments by research funders :  [slides](https://docs.google.com/presentation/d/1E_A9yS-zeZNSJ7M41t8g2l9U_5ObDcc3/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true)
+
 - 4 February: "Do we truly understand those we disagree with, and how could we test this?
 The Ideological Turing test", Psychopathology Lab meeting, University of Sheffield (host: Richard Bentall) : [slides](https://docs.google.com/presentation/d/1cEsWXBo4uZFZ8TKJj_NuNGendjLpiC04Wd6DbgmaQP8/edit?usp=sharing)
-
-# Past talks
 

### 2025-06-03 talks.qmd
update

@@
 
-- June 4. Evolution and Social Cognition lab,	Institut Jean Nicod, Paris.
+- June 4. ["Do we truly understand those we disagree with, and how could we test this?
+The Ideological Turing test"](https://docs.google.com/presentation/d/19QBDb20G9QWzebz7sgbxi80xDxisy_LDCaQGvHIcQxU/edit?usp=sharing), Evolution and Social Cognition lab,	Institut Jean Nicod, Paris.
 

### 2025-06-27 done.qmd
update

@@
 [Talks](https://tomstafford.sites.sheffield.ac.uk/outputs/talks) or Newsletter: <https://tomstafford.substack.com/>. For current preoccupations, see [here](news.html).
+
+## 2025
+
+June 16-18th: Panel DPR on DPR at International Conference on the Science of Science and Innovation ([ICSSI](https://icssi.org/)), Copenhagen
+
+June: Stafford, T., Pinfield, S., Butters, A., & Benson Marshall, M.
+(2025).
+RoRI Insights: Applicants as reviewers - a Guide to Distributed Peer Review (Version 1).
+Research on Research Institute.
+<https://doi.org/10.6084/m9.figshare.29270534.v1>
+
+May - June: Sprint on AI in grantmaking
 
@@
 2023-05-18 Chaired UKRN/RoRI panel on [The Future of Peer Review](https://www.ukrn.org/event/future-of-peer-review-may2023/).
-([Recording](https://youtu.be/BMeSh6esehE), [Slides](https://osf.io/ce3ts/))
+([Recording](https://youtu.be/BMeSh6esehE) and DOI:[10.52843/cassyni.50wy02](https://doi.org/10.52843/cassyni.50wy02), [Slides](https://osf.io/ce3ts/))
 

### 2025-06-27 papers.qmd
update

@@
 [[pre-print](https://psyarxiv.com/b25tf/)]
+
+- Vardal, O., Karapanagiotidis, T., Stafford, T., Drachen, A., & Wade, A.
+(2025).
+[Unsupervised identification of internal perceptual states influencing psychomotor performance](https://doi.org/10.1016/j.neuroimage.2025.121134).
+NeuroImage, 310, 121134.
+https://doi.org/10.1016/j.neuroimage.2025.121134
+[[preprint](https://www.biorxiv.org/content/10.1101/2023.09.08.556817v2.abstract)]
 
@@
 [doi.org/10.3758/s13428-020-01372-w](https://doi.org/10.3758/s13428-020-01372-w) (pre-print, [web/mobile version](https://idiolect.org.uk/papers/stafford2020/))
+
+- - Boag, R.
+J., Innes, R.
+J., Stevenson, N., Bahg, G., Busemeyer, J.
+R., Cox, G.
+E., … Forstmann, B.
+(2024, July 2).
+[An expert guide to planning experimental tasks for evidence accumulation modelling](https://osf.io/preprints/psyarxiv/snqgp).
 
@@
 
--   Vardal, O., Karapanagiotidis, T., Stafford, T., Drachen, A.
-and Wade, A.
-(2023) [Unsupervised identification of internal perceptual states influencing psychomotor performance](https://www.biorxiv.org/content/10.1101/2023.09.08.556817v2).
-bioRxiv 2023.09.08.556817; doi: https://doi.org/10.1101/2023.09.08.556817
-
 -   Brand, C.
@@
 https://doi.org/10.31234/osf.io/2e9wn
-
--   Zhu, J., Dommett, K., & Stafford, T.
-(2023).
-[What makes online political ads unacceptable?
-Interrogating public attitudes to inform regulatory responses](https://preprints.apsanet.org/engage/apsa/article-details/6462be37f2112b41e99fe9bf).
-APSA Preprints.
-doi:10.33774/apsa-2023-rxw1q This content is a preprint and has not been peer-reviewed.
 
@@
 ## 2025
+
+-   Zhu, J., Dommett, K., & Stafford, T.
+(2025).
+[What makes online political ads unacceptable?
+Interrogating public attitudes to inform regulatory responses](https://doi.org/10.1057/s41599-025-05114-1 ).
+Humanities and Social Sciences Communications, 12, 806.
+https://doi.org/10.1057/s41599-025-05114-1
 

### 2025-06-28 talks.qmd
update

@@
 
-- Can AI be used for better matching of proposals to reviewers? Feasibility and formal evaluation with the Metascience 2025 conference. Metascience 2025, June 30 - 2 July, London.
+- [Can AI be used for better matching of proposals to reviewers?
+Feasibility and formal evaluation with the Metascience 2025 conference](https://docs.google.com/presentation/d/12LqFL4JlioIgYgUxUCOiDUvTwERgT5Y3/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true).
+Metascience 2025, June 30 - 2 July, London.
 

### 2025-07-15 done.qmd
update

@@
 
+2025-07-01 Science runs a story on our work on Distributed Peer Review: [Should grant applicants judge competitors’ proposals?
+Unorthodox approach gets two real-world tests](https://www.science.org/content/article/should-grant-applicants-judge-competitors-proposals-unorthodox-approach-gets-two-real) doi: 10.1126/science.zap69fh
+
+2025-07-01 Quoted in Nature for this story on Distributed Peer Review: [How to speed up peer review: make applicants mark one another](https://www.nature.com/articles/d41586-025-02090-z).
+Nature 643, 313-314 (2025) doi: https://doi.org/10.1038/d41586-025-02090-z
+
+June 29th: Helped organise and run ECR Metascientst Happy Hour, a networking event before Metascience 2025 hosted by the UKRN.
+Report: [How to make a career in Metascience: Advice from Experts](https://www.ukrn.org/2025/07/04/ecr-metascientist-happy-hour/)
+
 June 16-18th: Panel DPR on DPR at International Conference on the Science of Science and Innovation ([ICSSI](https://icssi.org/)), Copenhagen
@@
 
-May - June: Sprint on AI in grantmaking
+May : external advisor and auditor for UKRI's first trial of Distributed Peer Review (read about this in their report [A Year in Metascience](https://www.gov.uk/government/publications/a-year-in-metascience-2025), published 2025-06-30)
+
+May - June: [AFIRE Sprint on AI in grantmaking](https://researchonresearch.org/afire-ai-in-funding-sprint/)
+
+2025-03-04: Chaired the [UKRN](https://www.ukrn.org/) Institutional Leads retreat in Cardiff. Here we are:
+
+<img src="images/2025-03-04ukrn_ils.jpeg" height = 400>
+
+2025-01-14: republished on the LSE Impact Blog [Do Community Notes work?](https://blogs.lse.ac.uk/impactofsocialsciences/2025/01/14/do-community-notes-work/)
 
@@
 
-2024-06-21: Research Matters magazine (with Shaun Leamon): [Experiments in research funding to reduce research](https://the-sra.org.uk/common/Uploaded%20files/Research%20Matters%20Magazine/sra-research-matters-june-2024-edition.pdf) bureaucracy
+2024-06-21: Research Matters magazine (with Shaun Leamon): [Experiments in research funding to reduce research bureaucracy](https://the-sra.org.uk/common/Uploaded%20files/Research%20Matters%20Magazine/sra-research-matters-june-2024-edition.pdf)
 

### 2025-08-01 index.qmd
update

@@
 
-![](tom_2020.jpg){width="25%"}
+![](images/tom_2020.jpg){width="50%"}
 
@@
 
-I direct the MSc programmes in Psychological Research Methods, and set up the MSc in Psychological Research Methods with Data Science.
-I teach a module on [Data Management and Visualisation](https://tomstafford.github.io/psy6422/).
-
-At the University I hold the position of Research Practice Lead, an institution-wide role with a remit to encourage practices which support robust and trusted research.
-As Research Practice Lead, I represent the University of Sheffield on the [UK Reproducibility Network](https://www.ukrn.org/), for which I chair the national [UKRN Institutional Leads group](https://www.ukrn.org/institutional-leads/).
+::: {.callout-tip title="News!"}
+From 1st September 2025 - 31st August 2026 I am on leave from the University of Sheffield.
+During this time I will be on secondment to the [Research on Research Institute](https://researchonresearch.org/), as well as pursing writing projects.
+Subscribe for updates on [tomstafford.substack.com/](https://tomstafford.substack.com/).
+:::
 
@@
 I am on the [PsyArXiv](https://osf.io/preprints/psyarxiv) Scientific Advisory Board as chair of the Public Engagement Subcommittee.
+
+Previously, I was Director for the MSc programmes in Psychological Research Methods, and set up the MSc in Psychological Research Methods with Data Science.
+You can read more about the flagshiop module I designed and taught here: [PSY6422 Data Analysis and Visualisation](https://tomstafford.github.io/psy6422/).
+
+From 2020 to 2025 I held the Research Practice Lead for the University of Sheffield, an institution-wide role with a remit to encourage practices which support robust and trusted research.
+As Research Practice Lead, I represented the University of Sheffield in the [UK Reproducibility Network](https://www.ukrn.org/), for which I chaired the national [UKRN Institutional Leads group](https://www.ukrn.org/institutional-leads/) 2023 - 2025.
 
@@
 
+## More
+
+* [Research](research.html)
+* [Papers](papers.html)
+* [Writing](writing.html)
+* [Talks](talks.html)
+* [Teaching](teaching.html)
+* [Supervision](supervision.html)
+* [Done](done.html)
+* [News](news.html)
+
 ## Colophon

### 2025-08-01 research.qmd
update

@@
 
-As of May 2020, I am [Research Practice Lead for the University of Sheffield](https://sites.google.com/sheffield.ac.uk/orwg/research-practice).
-This role involves the responsibility of promoting open, transparent, robust and reproducible research at the University.
+From 2020 - 2025 I was [Research Practice Lead for the University of Sheffield](https://sites.google.com/sheffield.ac.uk/orwg/research-practice).
+This role involves promoting transparent, robust and reproducible research at the University.
 Read more about [our work on open research on the Sheffield University website](https://www.sheffield.ac.uk/openresearch).

### 2025-08-01 teaching.qmd
update

@@
 
-I am director for the MSc programmes in Psychological Research Methods with Data Science.
-I am founding director for MSc in Psychological Research Methods with Data Science.
-I teach a MSc module in [data management and visualisation](https://tomstafford.github.io/psy6422/).
+To 2025 I was Director for the MSc programmes in Psychological Research Methods with Data Science.
+I was founding director for MSc in Psychological Research Methods with Data Science.
+I designed and led an MSc module in [data management and visualisation](https://tomstafford.github.io/psy6422/).
 

### 2025-08-01 done.qmd
update

@@
 ## 2025
+
+2025-07-31 Published (late!) the [showcase for this year's class of PSY6422 Data Analysis and Visualisation](https://tomstafford.github.io/psy6422/class-of-2025.html) (check out previous year's showcases on [the course pages](https://tomstafford.github.io/psy6422))
 
@@
 
-June 16-18th: Panel DPR on DPR at International Conference on the Science of Science and Innovation ([ICSSI](https://icssi.org/)), Copenhagen
+June 16-18th: Panel DPR on DPR at International Conference on the Science of Science and Innovation ([ICSSI](https://icssi.org/)), Copenhagen. Here's me and Anders Smith from Villum Fonden
+
+<img src="images/icssi2025.jpg" height = 400>
 
@@
 May - June: [AFIRE Sprint on AI in grantmaking](https://researchonresearch.org/afire-ai-in-funding-sprint/)
+
+May 2025: Launch of the [Editors and Publishers Network](https://sheffield.ac.uk/openresearch/home/editors-and-publishers-network) at the University of Sheffield, following the event I convened in 2024.
+
+2025-05-21 Final of our 2024-25 [AFIRE Funder Forum](https://researchonresearch.org/afire-funders-forum/) series; showcasing experiments by research funders.
+Talk recordings are on the website, as well as the [RoRI YouTube channel](https://www.youtube.com/@researchonresearchinstitut6175).
+
+April 2025: Attended [Fostering Accountability for the Integrity of Research Studies (FAIRS)](https://www.sjcfairsmeeting.com/), St John's College, Oxford
 
@@
 
+# 2022
+
+Probably I did other things this year, but the only thing I can find a note of is
+
+2022-03-09 Released code for making your own ['hybrid images'](https://github.com/tomstafford/hybridimages).
+They look different from different distances (vision science people: it is about putting different image information into different spatial frequencies)
+
+<img src="images/2022-03-29hybrid.jpg" height = 400>
+
 # 2021

### 2025-08-01 supervision.qmd
update

@@
 
-- [Adam Partridge](https://orcid.org/0000-0002-0133-4155) (2022 -), as Open Research Training Lead for the University of Sheffield and part of the [UKRN Open Research Programme](https://www.ukrn.org/open-research-programme/)
+- [Anna Butters](https://scholar.google.com/citations?user=8mKDLWQAAAAJ&hl=en&oi=ao) (2024 -- 2026) on [Distributed Peer Review at the Volkswagen Foundation](https://researchonresearch.org/volkswagen-distributed-peer-review/)
 
 -   [Amber Copeland](https://scholar.google.com/citations?user=JnNAldsAAAAJ&hl=en) (2018--2025) on "Reinforcer-specific value-based decision-making in persistence of and recovery from alcohol use disorder"
-
--   [Georgi Karadzhov](https://gkaradzhov.com/) (2024--2025) -- "DEliBots -- Deliberation Enhancing Bots" (at University of Cambridge)
 
@@
 
-# Previous supervision and examining
+### External
+
+- [Olha Guley](http://www.institutnicod.org/membres/etudiant-e-s/doctorant-e-s/guley-olha/?lang=fr) (2023 - ) Institut Jean Nicod, CNRS, Paris.
+
+# Alumni! (Previous supervision and examining)
 
@@
 
+- [Adam Partridge](https://orcid.org/0000-0002-0133-4155) (2022 -), as Open Research Training Lead for the University of Sheffield and part of the [UKRN Open Research Programme](https://www.ukrn.org/open-research-programme/)
+
+-   [Georgi Karadzhov](https://gkaradzhov.com/) (2024--2025) -- "DEliBots -- Deliberation Enhancing Bots" (at University of Cambridge)
+
 -   [Junyan Zhu](https://www.sheffield.ac.uk/politics/people/academic-staff/junyan-zhu) (2020--2023)

### 2025-08-06 papers.qmd
update

@@
 
+- Stafford, T., Zhu, J., & Dommett, K. (2024, December 31). Quantifying belief in the rationality of others: the Faith in Reason scale. Working Paper. <https://doi.org/10.31234/osf.io/umwxj>
+
 -   Stafford, T., Pirrone, A., Croucher, M., and Krystalli, A.
@@
 
-- - Boag, R.
+- Boag, R.
 J., Innes, R.
@@
 R., Cox, G.
-E., … Forstmann, B.
-(2024, July 2).
-[An expert guide to planning experimental tasks for evidence accumulation modelling](https://osf.io/preprints/psyarxiv/snqgp).
+E., ...
+& Forstmann, B.
+U.
+(2025).
+[An expert guide to planning experimental tasks for evidence-accumulation modeling](https://doi.org/10.1177/25152459251336127).
+Advances in Methods and Practices in Psychological Science, 8(2), 25152459251336127.
+<https://doi.org/10.1177/25152459251336127>
 
@@
 ## 2025
+
+- Myers, J.
+A., Stafford, T., Koychev, I., Perneczky, R., Bandmann, O., & Vaci, N.
+(2025).
+[Loneliness, social isolation, and effects on cognitive decline in patients with dementia: A retrospective cohort study using natural language processing](https://doi.org/10.1002/dad2.70149).
+Alzheimer's & Dementia: Diagnosis, Assessment & Disease Monitoring, 17(3), e70149.
+<https://doi.org/10.1002/dad2.70149>
 

### 2025-09-02 done.qmd
update

@@
 ## 2025
+
+2020 - 2025 I was [Research Practice Lead](done/2025rpl.html) for the University of Sheffield
 
@@
 
-2021 onwards: member, University of Sheffield Open Research Advsory Group, "providing strategic leadership in the ongoing development, promotion and implementation of the policies and practices supporting the University’s
-commitment to Open Research"
+2021 onwards: member, University of Sheffield Open Research Advsory Group, "providing strategic leadership in the ongoing development, promotion and implementation of the policies and practices supporting the University’s commitment to Open Research"
 
@@
 
-2012-06-06: [Fundamentals of learning: the exploration-exploitation trade-off](done/2012-06-12.html)
+2012-06-06: [Fundamentals of learning: the exploration-exploitation trade-off](done/2012-06-06.html)
 
-2012-06-04: [New paper: A novel task for the investigation of action acquisition](done/2012-06-12.html)
+2012-06-04: [New paper: A novel task for the investigation of action acquisition](done/2012-06-04.html)
 

### 2025-09-02 done/2025rpl.qmd
update

---
title: "2020 - 2025 Univerisy Research Practice Lead"
format: html
---

From 2020-2025 I held the role of Research Practice Lead at the University of Sheffield. This was a University level, cross-faculty, leadership role. The mission was to raise the quality of our research, by supporing researcher engagement with those practices, processes and platforms which make research more reliable, more scalable and more transparent. A large part of this was understanding and advocating for open research practices, as they manifested across different disciplines - from medicine to history.

In this work I was the University representative on the [UK Reproducibility Network](https://www.ukrn.org/)./ As 'Institutional Lead' I worked on the UKRN's [Open Research Training Programme](https://www.ukrn.org/open-research-programme/), which used a train-the-trainer model to reach thousands of researchers and train them in skills to use Open Research Practices. This was a huge multi-discipline, multi-institution, multi-year project and I learnt a lot being involved from application to the completion of the last trainings.

At the University I was supported by the the Open Research Working Group and the various committees I sat on which discussed University policy, such as the Vice President for Research's Research Strategy Group, the Research Culture Steering Board, and the Open Research Advisory Group, which both included the Faculty Directors of Research and representatives for the Library and IT Services. All of which is to say that I spent a lot of time learning about University management and policy, and appreciating how much colleagues across the departments and services of the University contributed to it running as it did. I particularly recommend all academics to speak to their librarians more.

Activities I initiated or led on during my time as Research Practice Lead
- Led development and adoption of the [University of Sheffield statement on Open Research](https://www.sheffield.ac.uk/openresearch/university-statement-open-research)
- Initiated the [Editors and Publishers Network](https://sheffield.ac.uk/openresearch/home/editors-and-publishers-network)
- Submitted evidence to the Science, Innovation and Technology Committee report on [Reproducibility and research integrity](https://publications.parliament.uk/pa/cm5803/cmselect/cmsctech/101/summary.html). Written evidence:[Commercial involvement in academic publishing is key to research reliability and should face greater public scrutiny](https://osf.io/preprints/metaarxiv/rjmvh)
- Organised networking events, journal clubs, drop-in sessions and workshops on open research, reproducibility and metascience
- Toured Departments from archaeology to civil engineering to speak on 'research improvement' and Open Research practices and policy
- Helped develop and became co-chair of the new University Office for [Open Research and Scholarship](https://www.sheffield.ac.uk/openresearch/home/office-open-research-and-scholarship)

### 2025-09-07 papers.qmd
update

@@
 ## Metaresearch
+
+- Butters, A., Marshall, M.
+B., Pinfield, S., Stafford, T., Bondarenko, A., Neubauer, B., Nuske, R., Schwidlinski, P., & Denecke, H.
+(2025).
+[Applicants as Reviewers: Evaluating the Risks, Benefits, and Potential of Distributed Peer Review for Grant Funding Allocations](https://doi.org/10.6084/m9.figshare.29994841.v2) (RoRI Working Paper No.
+17).
+https://doi.org/10.6084/m9.figshare.29994841.v2
 
@@
 O., Brady, D., & Stafford, T.
-(2023, June 27).
+(in press).
 [The Ideological Turing Test: a behavioural measure of open-mindedness and perspective-taking](https://psyarxiv.com/2e9wn).
+*Cognitive Science*.
 https://doi.org/10.31234/osf.io/2e9wn
@@
 
-- Boag, R.
-J., Innes, R.
-J., Stevenson, N., Bahg, G., Busemeyer, J.
-R., Cox, G.
-E., … Forstmann, B.
-(2024, July 2).
-[An expert guide to planning experimental tasks for evidence accumulation modelling](https://osf.io/preprints/psyarxiv/snqgp).
-
--   Brand, C.
-O., Brady, D., & Stafford, T.
-(2023, June 27).
-[The Ideological Turing Test: a behavioural measure of open-mindedness and perspective-taking](https://psyarxiv.com/2e9wn).
-https://doi.org/10.31234/osf.io/2e9wn
-
 -   Karadzhov, G., Stafford, T., and Vlachos, A.
@@
 ## 2025
+
+- Boag, R.
+J., Innes, R.
+J., Stevenson, N., Bahg, G., Busemeyer, J.
+R., Cox, G.
+E., ...
+& Forstmann, B.
+U.
+(2025).
+[An expert guide to planning experimental tasks for evidence-accumulation modeling](https://doi.org/10.1177/25152459251336127).
+Advances in Methods and Practices in Psychological Science, 8(2), 25152459251336127.
+<https://doi.org/10.1177/25152459251336127>
 
@@
 Royal Society Open Science, 9(10), 220366.
+<https://doi.org/10.1098/rsos.220366>
 

### 2025-09-09 talks.qmd
update

@@
 
-- June 4. ["Do we truly understand those we disagree with, and how could we test this?
-The Ideological Turing test"](https://docs.google.com/presentation/d/19QBDb20G9QWzebz7sgbxi80xDxisy_LDCaQGvHIcQxU/edit?usp=sharing), Evolution and Social Cognition lab,	Institut Jean Nicod, Paris.
+- 6th October: [ARMA Research Evaluation SIG Drop-In Session: Randomisation in funding allocation](https://arma.ac.uk/product/arma-research-evaluation-sig-drop-in-session-randomisation-in-funding-allocation/)
 
-- Panel on Distributed Peer Review, International Conference on the Science of Science ([ICSSI](https://icssi.org/)), June 16 - 18, Copenhagen.
+# Past talks
+
+## 2025
 
 - Evaluating Distributed Peer Review at the Volkswagen Foundation. Metascience 2025, June 30 - 2 July, London.
+
+- [The Metascience Lab](https://docs.google.com/presentation/d/1hcrkLVRyFl2zAhXffWldhXhNFYqkRLJj/edit?usp=sharing&ouid=109750001665912327637&rtpof=true&sd=true), days 1, 2 & 3 at Metascience 2025, June 30 - 2 July, London.
 
@@
 
-# Past talks
+- Panel on Distributed Peer Review, International Conference on the Science of Science ([ICSSI](https://icssi.org/)), June 16 - 18, Copenhagen.
 
-## 2025
+- June 4. ["Do we truly understand those we disagree with, and how could we test this?
+The Ideological Turing test"](https://docs.google.com/presentation/d/19QBDb20G9QWzebz7sgbxi80xDxisy_LDCaQGvHIcQxU/edit?usp=sharing), Evolution and Social Cognition lab,	Institut Jean Nicod, Paris.
 

### 2025-09-12 papers.qmd
update

@@
 (2025).
-[Applicants as Reviewers: Evaluating the Risks, Benefits, and Potential of Distributed Peer Review for Grant Funding Allocations](https://doi.org/10.6084/m9.figshare.29994841.v2) (RoRI Working Paper No.
+[Applicants as Reviewers: Evaluating the Risks, Benefits, and Potential of Distributed Peer Review for Grant Funding Allocations](https://doi.org/10.6084/m9.figshare.29994841) (RoRI Working Paper No.
 17).
-https://doi.org/10.6084/m9.figshare.29994841.v2
+https://doi.org/10.6084/m9.figshare.29994841
 

### 2025-09-19 done.qmd
update

@@
 ## 2025
+
+September 2025: [Our working paper on Distributed Peer Review published](https://doi.org/10.6084/m9.figshare.29994841).
+Media: [LSE Impact Blog](https://blogs.lse.ac.uk/impactofsocialsciences/2025/09/18/distributed-peer-review-how-the-wisdom-of-the-crowd-can-allocate-grant-funding/), [Science|Business](https://sciencebusiness.net/news/r-d-funding/assessment/distributed-peer-review-cuts-funding-decision-time-trials-show-there-are-risks), [Research Professional News](https://www.researchprofessionalnews.com/rr-news-europe-universities-2025-8-radical-method-cuts-time-on-peer-review-by-60-trial-finds/), [LaborJournal](https://www.laborjournal.de/editorials/3323.php), [Table](https://table.media/research/analyse/distributed-peer-review-welche-probleme-das-verfahren-loest) and [my newsletter](https://tomstafford.substack.com/p/distributed-peer-review)
 
@@
 Research on Research Institute.
-<https://doi.org/10.6084/m9.figshare.29270534.v1>
+<https://doi.org/10.6084/m9.figshare.29270534.v2>
 

### 2025-09-25 papers.qmd
update

@@
 International Journal of Methods in Psychiatric Research, e1997.
-<https://doi.org/10.1002/mpr.1997> [[preprint](https://psyarxiv.com/sakn9)]
+<https://doi.org/10.1002/mpr.1997> [[preprint](https://psyarxiv.com/sakn9), [Data/code](https://osf.io/sd6f5/)]
 
@@
 Current Directions in Psychological Science, 31(1), 49-55.
-<https://doi.org/10.1177/09637214211057841> [[web/mobile version](https://journals.sagepub.com/doi/full/10.1177/09637214211057841)]
+<https://doi.org/10.1177/09637214211057841> [[web/mobile version](https://journals.sagepub.com/doi/full/10.1177/09637214211057841), [Code](https://osf.io/fvm8s/files/osfstorage)]
 
@@
 *Cognitive Science*.
-https://doi.org/10.31234/osf.io/2e9wn
+[Preprint](https://doi.org/10.31234/osf.io/2e9wn), [Data/Code](https://doi.org/10.5281/zenodo.16872578).
 
@@
 
--   Stafford, T. (2018). [Female chess players outperform expectations when playing men](http://journals.sagepub.com/doi/10.1177/0956797617736887). Psychological Science, 29(3), 429-436. (Preprint).
+-   Stafford, T.
+(2018).
+[Female chess players outperform expectations when playing men](http://journals.sagepub.com/doi/10.1177/0956797617736887).
+Psychological Science, 29(3), 429-436.
+https://doi.org/10.1177/095679761773688 [Preprint](https://osf.io/preprints/psyarxiv/bpy3t), [Code/Data](https://osf.io/aeksv).
 

### 2025-09-30 talks.qmd
update

@@
 
-- 6th October: [ARMA Research Evaluation SIG Drop-In Session: Randomisation in funding allocation](https://arma.ac.uk/product/arma-research-evaluation-sig-drop-in-session-randomisation-in-funding-allocation/)
+- 6th October: [ARMA Research Evaluation SIG Drop-In Session: Randomisation in funding allocation](https://arma.ac.uk/product/arma-research-evaluation-sig-drop-in-session-randomisation-in-funding-allocation/) - [my slides](https://docs.google.com/presentation/d/1nCiQ4NKBKfN1mz4yv_E4TBDEwM4hz_ob/edit?usp=sharing&ouid=102850735399031809686&rtpof=true&sd=true), as [PDF](docs/ARMA2025-10-06_TomStafford.pdf)
 

### 2025-10-14 papers.qmd
update

@@
 Behavior Research Methods, 56(4), 3578-3588.
-[[preprint](https://psyarxiv.com/prfu2/)]
+[[preprint](https://psyarxiv.com/prfu2/)],[code/data](https://osf.io/utnx2/files/osfstorage)]
 
@@
 (in press).
-[The Ideological Turing Test: a behavioural measure of open-mindedness and perspective-taking](https://psyarxiv.com/2e9wn).
+[The Ideological Turing Test: a behavioural measure of open-mindedness and perspective-taking](https://doi.org/10.1111/cogs.70126).
 *Cognitive Science*.
@@
 ## In press, and under review
+
+- Arjmandi-Lari, Z., Mantzarlis, A., Stafford, T. (2025). [Threats to the sustainability of Community Notes on X](https://arxiv.org/abs/2510.00650). arXiv preprint arXiv:2510.00650
 

### 2025-12-08 talks.qmd
update

@@
 
-- 6th October: [ARMA Research Evaluation SIG Drop-In Session: Randomisation in funding allocation](https://arma.ac.uk/product/arma-research-evaluation-sig-drop-in-session-randomisation-in-funding-allocation/) - [my slides](https://docs.google.com/presentation/d/1nCiQ4NKBKfN1mz4yv_E4TBDEwM4hz_ob/edit?usp=sharing&ouid=102850735399031809686&rtpof=true&sd=true), as [PDF](docs/ARMA2025-10-06_TomStafford.pdf)
+- 22nd January: **Funder experimentation with AI**, [Ensuring Value in Research EViR](https://evir.org/)
+
+  - Topic: There are many opportunities in research funding to use AI, such as improving applicant experience, reviewer selection, evaluation processes and feedback.
+In this talk I will introduce the Research on Research Institute's work on AI, covering our project on responsible use of AI by research funders (GRAIL) and our workshops on how to develop evaluation experiments on the use of AI in research funding (AFIRE).
+I will share experiences of research funders with evaluating AI use, and suggest principles for making progress in this area.
+<https://researchonresearch.org/project/a-f-i-r-e/>
+
+- 30th January: **The metacience of peer review**, as part of "[Does AI threaten research integrity?](https://www.ticketsource.co.uk/whats-on/room-2-62/eleanor-rathbone-building/does-ai-threaten-research-integrity/e-jopdkk)" at University of Liverpool
+
+  - Abstract:  Peer review is central to the lives of researchers - it determines if our papers get accented and if our funding proposals are successful.
+Metascience - also known as the science of science, or research on research - takes peer review as an object of study in its own right, and asks what we have learnt about how peer review works and how it might be improved.
+I'll discuss how we worked with a research funder to evaluate a trial of Distributed Peer Review  (a system where applicants for a funding call review each others' applications), and talk about the topics in the psychology of expertise, judgement and decision making can be given new relevance in the study of peer review.
+
+- 12 February: **Understanding the reasons for vaccine hesitancy** at [NHS England digital Prevention Services](https://www.digital-prevention-services.nhs.uk), Thoughtful Thursday, 1pm, Canary Wharf
 
@@
 ## 2025
+
+- 16th October [Distributed Peer Review] for SSHRC seminar on funding experiments [slides](https://docs.google.com/presentation/d/1xtzvkFIc7KEm6JyQU5tyc7p2l0iS6DtV/edit?usp=sharing&ouid=102850735399031809686&rtpof=true&sd=true), [as PDF](docs/sshrc2025-10-16.pdf)
+
+- 6th October: [ARMA Research Evaluation SIG Drop-In Session: Randomisation in funding allocation](https://arma.ac.uk/product/arma-research-evaluation-sig-drop-in-session-randomisation-in-funding-allocation/) - [my slides](https://docs.google.com/presentation/d/1nCiQ4NKBKfN1mz4yv_E4TBDEwM4hz_ob/edit?usp=sharing&ouid=102850735399031809686&rtpof=true&sd=true), as [PDF](docs/ARMA2025-10-06_TomStafford.pdf)
 

### 2025-12-12 papers.qmd
update

@@
 --------------------
+
+## Decision making & reasoning
+
+- Stafford, T., Zhu, J., & Dommett, K. (2024, December 31). Quantifying belief in the rationality of others: the Faith in Reason scale. Working Paper. <https://doi.org/10.31234/osf.io/umwxj>
+
+-   Stafford, T., Pirrone, A., Croucher, M., and Krystalli, A.
+(2020).
+[Quantifying the benefits of using decision models with response time and accuracy data](https://link.springer.com/article/10.3758/s13428-020-01372-w).
+Behaviour Research Methods, 52, 2142--2155.
+[doi.org/10.3758/s13428-020-01372-w](https://doi.org/10.3758/s13428-020-01372-w) (pre-print, [web/mobile version](https://idiolect.org.uk/papers/stafford2020/))
+
+- Boag, R.
+J., Innes, R.
+J., Stevenson, N., Bahg, G., Busemeyer, J.
+R., Cox, G.
+E., ...
+& Forstmann, B.
+U.
+(2025).
+[An expert guide to planning experimental tasks for evidence-accumulation modeling](https://doi.org/10.1177/25152459251336127).
+Advances in Methods and Practices in Psychological Science, 8(2), 25152459251336127.
+<https://doi.org/10.1177/25152459251336127>
+
+-   Brand, C.
+O., Brady, D., & Stafford, T.
+(in press).
+[The Ideological Turing Test: a behavioural measure of open-mindedness and perspective-taking](https://doi.org/10.1111/cogs.70126).
+*Cognitive Science*.
+[Preprint](https://doi.org/10.31234/osf.io/2e9wn), [Data/Code](https://doi.org/10.5281/zenodo.16872578).
+
+-   Karadzhov, G., Stafford, T., and Vlachos, A.
+(2023).
+[DeliData: A dataset for deliberation in multi-party problem solving](https://dl.acm.org/doi/10.1145/3610056).
+Proceedings of the ACM on Human-Computer Interaction, CSCW.
+<https://doi.org/10.1145/3610056> [[arXiv](https://arxiv.org/abs/2108.05271)]
+
+-   Karadzhov, G., Stafford, T., and Vlachos, A.
+(2022).
+[What makes you change your mind?
+An empirical investigation in online group decision-making conversations](https://www.delibot.xyz/publications/).
+arXiv preprint [arXiv:2207.12035](https://arxiv.org/abs/2207.12035)
+
+    -   -   See also: [delibot.xyz](https://www.delibot.xyz/)
+
+-   De Kock, C., Stafford, T., & Vlachos, A.
+(2022).
+[How to disagree well: Investigating the dispute tactics used on Wikipedia](https://arxiv.org/abs/2212.08353).
+In Y.
+Goldberg, Z.
+Kozareva, & Y.
+Zhang (Eds.), Proceedings of the 2022 Conference on Empirical Methods in Natural Language Processing (pp.
+3824–3837).
+Association for Computational Linguistics.
+https://doi.org/10.18653/v1/2022.emnlp-main.252
 
@@
 Retrieved from osf.io/preprints/psyarxiv/b2hm7
-
-## Decision making & reasoning
-
-- Stafford, T., Zhu, J., & Dommett, K. (2024, December 31). Quantifying belief in the rationality of others: the Faith in Reason scale. Working Paper. <https://doi.org/10.31234/osf.io/umwxj>
-
--   Stafford, T., Pirrone, A., Croucher, M., and Krystalli, A.
-(2020).
-[Quantifying the benefits of using decision models with response time and accuracy data](https://link.springer.com/article/10.3758/s13428-020-01372-w).
-Behaviour Research Methods, 52, 2142--2155.
-[doi.org/10.3758/s13428-020-01372-w](https://doi.org/10.3758/s13428-020-01372-w) (pre-print, [web/mobile version](https://idiolect.org.uk/papers/stafford2020/))
-
-- Boag, R.
-J., Innes, R.
-J., Stevenson, N., Bahg, G., Busemeyer, J.
-R., Cox, G.
-E., ...
-& Forstmann, B.
-U.
-(2025).
-[An expert guide to planning experimental tasks for evidence-accumulation modeling](https://doi.org/10.1177/25152459251336127).
-Advances in Methods and Practices in Psychological Science, 8(2), 25152459251336127.
-<https://doi.org/10.1177/25152459251336127>
-
--   Brand, C.
-O., Brady, D., & Stafford, T.
-(in press).
-[The Ideological Turing Test: a behavioural measure of open-mindedness and perspective-taking](https://doi.org/10.1111/cogs.70126).
-*Cognitive Science*.
-[Preprint](https://doi.org/10.31234/osf.io/2e9wn), [Data/Code](https://doi.org/10.5281/zenodo.16872578).
-
--   Karadzhov, G., Stafford, T., and Vlachos, A.
-(2023).
-[DeliData: A dataset for deliberation in multi-party problem solving](https://dl.acm.org/doi/10.1145/3610056).
-Proceedings of the ACM on Human-Computer Interaction, CSCW.
-<https://doi.org/10.1145/3610056> [[arXiv](https://arxiv.org/abs/2108.05271)]
-
--   Karadzhov, G., Stafford, T., and Vlachos, A.
-(2022).
-[What makes you change your mind?
-An empirical investigation in online group decision-making conversations](https://www.delibot.xyz/publications/).
-arXiv preprint [arXiv:2207.12035](https://arxiv.org/abs/2207.12035)
-
-    -   -   See also: [delibot.xyz](https://www.delibot.xyz/)
-
--   De Kock, C., Stafford, T., & Vlachos, A.
-(2022).
-[How to disagree well: Investigating the dispute tactics used on Wikipedia](https://arxiv.org/abs/2212.08353).
-In Y.
-Goldberg, Z.
-Kozareva, & Y.
-Zhang (Eds.), Proceedings of the 2022 Conference on Empirical Methods in Natural Language Processing (pp.
-3824–3837).
-Association for Computational Linguistics.
-https://doi.org/10.18653/v1/2022.emnlp-main.252
 
@@
 (2014).
-[Tracing the trajectory of skill learning with a very large sample of online game players](http://pss.sagepub.com/content/25/2/511).
+[Tracing the trajectory of skill learning with a very large sample of online game players](https://doi.org/10.1177/0956797613511466).
 Psychological Science, 25(2) 511--518.
-See also: [Data and analysis code](https://github.com/tomstafford/axongame).
+<https://doi.org/10.1177/0956797613511466> See also: [Data and analysis code](https://github.com/tomstafford/axongame).
 
